### 2019-06-17 manuscript/draftcssa19.tex
test-commit_RV

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
%\usepackage{graphics}
%\usepackage{curves}
%\usepackage{tikz}
%\usetikzlibrary{backgrounds}
%\usetikzlibrary{snakes} \documentclass{report}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amsfonts}
%\usepackage{graphics}
%\usepackage{curves}
%\usepackage{tikz}
%\usetikzlibrary{backgrounds}
%\usetikzlibrary{snakes}
%\usepackage{setspace}
%\doublespacing
%\usepackage{lscape}
%\usepackage{booktabs}
%\usepackage{longtable}
\usepackage{hyperref}
\usepackage{url}
\usepackage{color}

\author{SPECSIG Group}
\title{Wealth dynamics in the presence of network structure primitive institutions}
\bibliographystyle{plain} 
\begin{document}

\maketitle
\section{Introduction}
\end{document}

### 2019-06-17 src/net/sim.jl
Switch R Gini calcs from ineq to DescTools.

@@ -1,5 +1,5 @@
 using RCall
-@rlibrary ineq
+@rlibrary DescTools
 using Gadfly
 using LightGraphs
 using GraphPlot, Compose
@@ -232,7 +232,10 @@ function specnet(;additional_params...)
                 push!(wealthArray,ag.a.sugar_level)
             end
         end
-        cGini=ineq(wealthArray, type="Gini")
+        # The R function Gini() from DescTools returns a vector of three values
+        #   if conf.level is not NA: (1) the estimate, (2) the lower bound of
+        #   the CI, and (3) the upper bound.
+        cGini=Gini(wealthArray; Symbol("conf.level")=>.95)[1]
 
         gIndex=convert(Float16,cGini)
         push!(ginis,gIndex)

### 2019-06-17 src/net/sim.jl
Add Gini CI's to iter_results.

@@ -122,7 +122,8 @@ function specnet(;additional_params...)
     # will be set to a lower number at that time.
     local total_iters = params[:max_iters]
 
-    local ginis=[]
+    # Each row will have three values: the low CI, the value, and the high CI.
+    local ginis=Array{Float16}(undef,params[:max_iters],3)
     local stages=[]
     local nums_agents=[]
 
@@ -224,7 +225,6 @@ function specnet(;additional_params...)
             end
         end
 
-        #adding current gini index to ginis array
         wealthArray=[]
         empty!(wealthArray)
         for ag in keys(AN)
@@ -235,10 +235,8 @@ function specnet(;additional_params...)
         # The R function Gini() from DescTools returns a vector of three values
         #   if conf.level is not NA: (1) the estimate, (2) the lower bound of
         #   the CI, and (3) the upper bound.
-        cGini=Gini(wealthArray; Symbol("conf.level")=>.95)[1]
-
-        gIndex=convert(Float16,cGini)
-        push!(ginis,gIndex)
+        rGini=Gini(wealthArray; Symbol("conf.level")=>.95)
+        ginis[iter,:] = [ convert(Float16,r) for r in rGini ]
 
     end   # End main simulation for loop
 
@@ -250,8 +248,10 @@ function specnet(;additional_params...)
         proto_id = [ ag.a.proto_id for ag in keys(AN) ]
     )
     iter_results = DataFrame(
-        iter = 1:length(ginis),
-        gini = ginis,
+        iter = 1:length(stages),
+        gini_lowCI = ginis[1:length(stages),2],
+        gini = ginis[1:length(stages),1],
+        gini_highCI = ginis[1:length(stages),3],
         stage = stages,
         num_agents = nums_agents
     )

### 2019-06-17 src/net/sim.jl
Add error bars to single-sim Gini plot.

@@ -415,6 +415,11 @@ function plot_gini_livingfrac_over_time(iter_results, callouts)
             color=:stage,
         ),
         layer(
+            x=:iter, y=:gini, ymin=:gini_lowCI, ymax=:gini_highCI,
+            Geom.line, Geom.point, Geom.errorbar,
+            Theme(default_color=colorant"black")
+        ),
+        layer(
             x=:iter, y=:num_agents,
             Geom.line,
             Theme(default_color=colorant"black")

### 2019-06-20 src/net/param_sweep.jl
Save param sweep results.

@@ -181,18 +181,20 @@ function param_sweeper(graph_name; additional_params...)
     draw(PNG("$(tempdir())/$(graph_name)ParameterSweepPlot.png"), plotLG)
     draw(PNG("$(tempdir())/$(graph_name)_wealth_heatmap.png"), wealth_heatmap)
 
+    return [ agent_line_df, trial_line_df, plot_df ]
 end
 
 #runs a sweep for a given parameter once for each graph type,
 #saving the dataframes and plots to multiple files
 
 if graph_sweep
+    sweep_results = Dict()
     graphs=["erdos_renyi","scale_free","small_world","complete","empty"]
     println("sweeping for graph type")
     for graph in graphs
         params[:whichGraph]=graph
-        param_sweeper(string(graph))
+        sweep_results[graph] = param_sweeper(string(graph))
     end
 else
-    param_sweeper(params[:whichGraph])
+    sweep_results = param_sweeper(params[:whichGraph])
 end

### 2019-06-20 src/net/param_sweep.jl
Return single-sim results as dict.

@@ -65,7 +65,7 @@ function param_sweeper(graph_name; additional_params...)
 
             # Actually run the simulation!
             results=specnet()
-            agent_results = results[1]
+            agent_results = results[:agent_results]
 
             #finding the breakdown of graph components and pushing that to component data frame
             component_vertices=connected_components(graph)

### 2019-06-20 src/net/sim.jl

@@ -279,7 +279,8 @@ function specnet(;additional_params...)
     end
     println("\n...ending SPECnet.")
 
-    return [sort(agent_results, :agent), iter_results]
+    return Dict(:agent_results => sort(agent_results, :agent),
+        :iter_results => iter_results)
 end
 
 

### 2019-06-20 src/net/param_sweep.jl
Encapsulate "graph" in sim.jl.

@@ -66,22 +66,15 @@ function param_sweeper(graph_name; additional_params...)
             # Actually run the simulation!
             results=specnet()
             agent_results = results[:agent_results]
+            overall_results = results[:overall_results]
 
-            #finding the breakdown of graph components and pushing that to component data frame
-            component_vertices=connected_components(graph)
-            if nv(graph) == 0
-                global num_comps=0
-                global largest_comp=0
-            else
-                global num_comps=length(component_vertices)
-                global largest_comp=findmax(length.(component_vertices))[1][1]
-            end
-            push!(comp_df,(largest_comp,num_comps))
+            push!(comp_df,
+                (overall_results[:size_largest_comp],
+                 overall_results[:num_comps]))
 
             insertcols!(agent_results, 1, param_to_sweep => repeat(counter:counter,nrow(agent_results)))
             insertcols!(agent_results, 2, :seed => repeat(params[:random_seed]:params[:random_seed],nrow(agent_results)))
             insertcols!(agent_results, 3, :simulation_tag => repeat((i*num_values+j):(i*num_values+j),nrow(agent_results)))
-
 
             agent_line_df=[agent_line_df;agent_results]
 
@@ -181,7 +174,9 @@ function param_sweeper(graph_name; additional_params...)
     draw(PNG("$(tempdir())/$(graph_name)ParameterSweepPlot.png"), plotLG)
     draw(PNG("$(tempdir())/$(graph_name)_wealth_heatmap.png"), wealth_heatmap)
 
-    return [ agent_line_df, trial_line_df, plot_df ]
+    return Dict(:agent_line_df => agent_line_df,
+        :trial_line_df => trial_line_df,
+        :plot_df => plot_df)
 end
 
 #runs a sweep for a given parameter once for each graph type,
@@ -189,11 +184,11 @@ end
 
 if graph_sweep
     sweep_results = Dict()
-    graphs=["erdos_renyi","scale_free","small_world","complete","empty"]
+    graph_types=["erdos_renyi","scale_free","small_world","complete","empty"]
     println("sweeping for graph type")
-    for graph in graphs
-        params[:whichGraph]=graph
-        sweep_results[graph] = param_sweeper(string(graph))
+    for graph_type in graph_types
+        params[:whichGraph]=graph_type
+        sweep_results[graph_type] = param_sweeper(graph_type)
     end
 else
     sweep_results = param_sweeper(params[:whichGraph])

### 2019-06-20 src/net/sim.jl

@@ -264,6 +264,13 @@ function specnet(;additional_params...)
         stage = stages,
         num_agents = nums_agents
     )
+    component_vertices=connected_components(graph)
+    overall_results = Dict(
+        :size_largest_comp => nv(graph) == 0 ? 0 : 
+            findmax(length.(component_vertices))[1][1],
+        :num_comps => nv(graph) == 0 ? 0 : 
+            length(component_vertices)
+    )
 
     if params[:make_sim_plots]
         plot_gini_livingfrac_over_time(iter_results,
@@ -280,7 +287,8 @@ function specnet(;additional_params...)
     println("\n...ending SPECnet.")
 
     return Dict(:agent_results => sort(agent_results, :agent),
-        :iter_results => iter_results)
+        :iter_results => iter_results,
+        :overall_results => overall_results)
 end
 
 

### 2019-06-20 src/net/param_sweep.jl
Reorg param sweep plotting.

@@ -146,8 +146,8 @@ function param_sweeper(graph_name; additional_params...)
     trial_line_df=hcat(trial_line_df,comp_df)
     CSV.write("$(tempdir())/$(graph_name)_simulation_results.csv",trial_line_df)
 
-    #drawing plot
-    println("Creating $(param_to_sweep) plot...")
+    #drawing plots
+    println("Creating $(param_to_sweep) Gini plot...")
     plotLG=plot(plot_df,
         layer(
             x=param_to_sweep, y=:gini_lowCI,
@@ -170,8 +170,10 @@ function param_sweeper(graph_name; additional_params...)
             Theme(default_color=colorant"lightblue")
         ),
         Guide.xlabel(string(param_to_sweep)), Guide.ylabel("Gini Index"))
-    wealth_heatmap=plot(x=agent_line_df.sugar,y=agent_line_df[param_to_sweep],Geom.histogram2d,Guide.ylabel(string(param_to_sweep)), Guide.xlabel("Agent Wealth"))
     draw(PNG("$(tempdir())/$(graph_name)ParameterSweepPlot.png"), plotLG)
+
+    println("Creating $(param_to_sweep) agent heatmap...")
+    wealth_heatmap=plot(x=agent_line_df.sugar,y=agent_line_df[param_to_sweep],Geom.histogram2d,Guide.ylabel(string(param_to_sweep)), Guide.xlabel("Agent Wealth"))
     draw(PNG("$(tempdir())/$(graph_name)_wealth_heatmap.png"), wealth_heatmap)
 
     return Dict(:agent_line_df => agent_line_df,

### 2019-06-20 src/net/param_sweep.jl
Add sim_tag to trial_line_df.

@@ -37,15 +37,17 @@ function param_sweeper(graph_name; additional_params...)
         agent=String[],
         sugar=Float64[],
         proto_id=Int[],
-        simulation_tag=Int[]
+        sim_tag=Int[]
     )
-    names!(agent_line_df,[param_to_sweep,:seed,:agent,:sugar,:proto_id, :simulation_tag])
+    names!(agent_line_df,[param_to_sweep,:seed,:agent,:sugar,:proto_id,:sim_tag])
 
     global trial_line_df=DataFrame(
         replace_this=Float64[],
         seed=Int[],
-        gini=Float64[])
-    names!(trial_line_df,[param_to_sweep,:seed,:gini])
+        gini=Float64[],
+        sim_tag=Int[]
+    )
+    names!(trial_line_df,[param_to_sweep,:seed,:gini,:sim_tag])
 
     params[:make_anims] = false  # We would never want this true for a sweep
     params[:make_sim_plots] = false  # We would never want this true for a sweep
@@ -74,7 +76,7 @@ function param_sweeper(graph_name; additional_params...)
 
             insertcols!(agent_results, 1, param_to_sweep => repeat(counter:counter,nrow(agent_results)))
             insertcols!(agent_results, 2, :seed => repeat(params[:random_seed]:params[:random_seed],nrow(agent_results)))
-            insertcols!(agent_results, 3, :simulation_tag => repeat((i*num_values+j):(i*num_values+j),nrow(agent_results)))
+            insertcols!(agent_results, 3, :sim_tag => repeat((i*num_values+j):(i*num_values+j),nrow(agent_results)))
 
             agent_line_df=[agent_line_df;agent_results]
 
@@ -84,7 +86,7 @@ function param_sweeper(graph_name; additional_params...)
         params[:random_seed]=original_seed
         counter += (end_value-start_value)/num_values
     end
-    simulation_tag=0
+    sim_tag=0
     rm("$(tempdir())/$(graph_name)_agent_results.csv", force=true)
     rm("$(tempdir())/$(graph_name)_simulation_results.csv", force=true)
     rm("$(tempdir())/$(graph_name)ParameterSweepPlot.png", force=true)
@@ -114,20 +116,29 @@ function param_sweeper(graph_name; additional_params...)
     counter=start_value
     #weak solution to acccessing seed value, should be reworked
     mark_seed_value=original_seed
+
     for j = 1:num_values
+
         curr_param_value_ginis = []
[…]

### 2019-06-20 src/net/param_sweep.jl
Rework df column renaming.

@@ -39,7 +39,8 @@ function param_sweeper(graph_name; additional_params...)
         proto_id=Int[],
         sim_tag=Int[]
     )
-    names!(agent_line_df,[param_to_sweep,:seed,:agent,:sugar,:proto_id,:sim_tag])
+    names!(agent_line_df,
+        prepend!(names(agent_line_df)[2:end], [param_to_sweep]))
 
     global trial_line_df=DataFrame(
         replace_this=Float64[],
@@ -47,7 +48,8 @@ function param_sweeper(graph_name; additional_params...)
         gini=Float64[],
         sim_tag=Int[]
     )
-    names!(trial_line_df,[param_to_sweep,:seed,:gini,:sim_tag])
+    names!(trial_line_df,
+        prepend!(names(trial_line_df)[2:end], [param_to_sweep]))
 
     params[:make_anims] = false  # We would never want this true for a sweep
     params[:make_sim_plots] = false  # We would never want this true for a sweep
@@ -107,7 +109,7 @@ function param_sweeper(graph_name; additional_params...)
         gini_lowCI=Float64[],
         gini_highCI=Float64[],
     )
-    names!(plot_df,[param_to_sweep,:gini,:gini_lowCI,:gini_highCI])
+    names!(plot_df, prepend!(names(plot_df)[2:end], [param_to_sweep]))
 
 
     #change values of this dataframe to create other plots

### 2019-06-20 src/net/param_sweep.jl
Make "number of components" an integer.

@@ -19,7 +19,7 @@ graph_sweep=false    #run the sweep once for each graph type
 original_seed=params[:random_seed]
 
 components=[[],[]]
-global comp_df=DataFrame(size_largest_comp=Int[],num_comps=Float64[])
+global comp_df=DataFrame(size_largest_comp=Int[],num_comps=Int[])
 
 
 function param_sweeper(graph_name; additional_params...)

### 2019-06-20 src/net/param_sweep.jl
conflict res

@@ -4,6 +4,7 @@ using RCall
 @rlibrary DescTools
 using DataFrames
 using CSV
+using Bootstrap
 include("sim.jl")
 include("setup_params.jl")
 
@@ -105,7 +106,13 @@ function param_sweeper(graph_name; additional_params...)
 
     #dataframe containing only values to be plotted
 
-    plot_df=DataFrame(gini=Float64[],param_to_sweep=Float64[])
+    plot_df=DataFrame(
+        replace_this=Float64[],
+        gini=Float64[],
+        gini_lowCI=Float64[],
+        gini_highCI=Float64[],
+    )
+    names!(plot_df,[param_to_sweep,:gini,:gini_lowCI,:gini_highCI])
 
 
     #change values of this dataframe to create other plots
@@ -115,25 +122,29 @@ function param_sweeper(graph_name; additional_params...)
     #weak solution to acccessing seed value, should be reworked
     mark_seed_value=original_seed
     for j = 1:num_values
-        total_gini=0
+        curr_param_value_ginis = []
         for i=1:trials_per_value
             simulation_tag=(j*num_values+i)
-            # The R function Gini() from DescTools returns a vector of three
-            #   values if conf.level is not NA: (1) the estimate, (2) the lower
-            #   bound of the CI, and (3) the upper bound.
-            current_sim_gini=convert(Float64,
-                Gini(agent_line_df[agent_line_df.simulation_tag.==simulation_tag,:sugar];
-                    Symbol("conf.level")=>.95)[1])
-            #adding to total gini to be averaged for plot (plot_df)
-            total_gini+=current_sim_gini
+            # When not given a conf.level parameter, the R function Gini() from
+            #   DescTools returns a single value: the Gini coefficient. We're
+            #   not using DescTools bootstrapping to estimate the CI here,
+            #   because we want a CI from the set of Gini coefficients from our
+            #   trials_per_value runs, not the CI of a single run.
+            current_sim_gini = convert(Float64, Gini(
+                agent_line_df[agent_line_df.simulation_tag.==simulation_tag,:sugar]))
+            push!(curr_param_value_ginis, current_sim_gini)
             #adding the gini sim results to the df
             push!(trial_line_df,(counter,mark_seed_value,current_sim_gini))
             #averaging and pushing data for wealth histogram
             mark_seed_value+=1
[…]

### 2019-06-20 src/net/setup_params.jl

@@ -23,6 +23,12 @@ params = Dict{Symbol,Any}(
                                     #   > wealth than this to form a proto
     :make_anims => false,           # create animations of results?
     :make_sim_plots => true,        # create plots (for individual simulations)?
+    :num_boot_samples => 1000,      # for single sims, the number of bootstrap
+                                    #   samples used in computing CI for single
+                                    #   Gini
+                                    # for param sweeps, the number of bootstrap
+                                    #   samples used in computing CI for all
+                                    #   Ginis in runs with same parameters
     :animation_delay => 20,         # milliseconds between animation frames
     :random_seed => 1234,           # random number generator starting seed
 
@@ -33,7 +39,7 @@ params = Dict{Symbol,Any}(
                                     #   - "complete"
                                     #   - "empty"
 
-    :λ => 2,                        # ER: expected number if edges per node
+    :λ => 2.0,                        # ER: expected number if edges per node
 
     :SF_edges => 40,                # SF: number of edges
     :SF_degree => 2,                # SF: exponent of expected power law degree

### 2019-06-20 manuscript/draftcssa19.tex
with bib

@@
 
-\author{SPECSIG Group}
-\title{Wealth dynamics in the presence of network structure primitive institutions}
+\author{ABMSPECSIG Group}
+\title{Wealth dynamics in the presence of network structure and primitive cooperation}
 \bibliographystyle{plain} 
@@
 \maketitle
+\begin{abstract}
+We study wealth accumulation dynamics in a population of heterogeneously mixed agents with a capacity for a certain primitive form of cooperation enabled by static network structures.
+Despite their simplicity, the stochastic dynamics generate inequalities in wealth reminiscent of real world social systems even in a fully mixed population.
+A simple form of cooperation is introduced and is shown to enhance the viability of agents By embedding such dynamics in a network, the impact of social structures on the origins and persistence of inequality can be teased out easily.
+The models developed here complement traditional modeling approaches based on grid worlds.
+
+\end{abstract}
 \section{Introduction}
+
+~\cite{ch1as_hdbk,hedstrom2011oxford,martin_lee}
+
+~\cite{ch2as_hdbk,ch11as_hdbk,granovetter2005,hedstrom2018}
+
+\section{Model}
+~\cite{redner2001guide}
+
+\section{Analysis}
+
+\section{Conclusion and Future Work}
+%what kinds of real world systems are we talking about?
+\bibliography{ref_cssa19}
 \end{document}

### 2019-06-20 src/net/setup_params.jl
Float Conversion

@@ -8,7 +8,7 @@ params = Dict{Symbol,Any}(
     :starvation_period => 10,       # the number of iterations to starve all agents
                                     #   after the simulation has reached stage 3
                                     #   (all live non-isolate agents in protos)
-    :openness => 0.0,               # 0 <=> openness <=> 1
+    :openness => float(0.0),               # 0 <=> openness <=> 1
                                     #   (0: always choose from neighbor,
                                     #    1: always choose from entire city)
     :init_sg_lvl => 100,            # each agent starts with wealth
@@ -39,12 +39,12 @@ params = Dict{Symbol,Any}(
                                     #   - "complete"
                                     #   - "empty"
 
-    :λ => 2.0,                        # ER: expected number if edges per node
+    :λ => float(1),                        # ER: expected number if edges per node
 
     :SF_edges => 40,                # SF: number of edges
     :SF_degree => 2,                # SF: exponent of expected power law degree
                                     #   distribution
 
-    :β => 0.2,                      # SW: prob. of rewiring
+    :β => float(0.2),                      # SW: prob. of rewiring
     :k => 2,                        # SW: degree of nodes
 )

### 2019-06-21 src/net/param_sweep.jl
Component Plots Fix #62

@@ -9,17 +9,17 @@ include("sim.jl")
 include("setup_params.jl")
 
 
-param_to_sweep=:λ    #parameter to iterate over *any parameter*
+param_to_sweep=:salary   #parameter to iterate over *any parameter*
                      #for graph sweep param_to_sweep should not be exclusive to one graph type e.g. SF_prob
-start_value=0.0      #value to begin sweep
-end_value=2          #value to end sweep
+start_value=10      #value to begin sweep
+end_value=200         #value to end sweep
 num_values=50        #number of distinct values to run
 trials_per_value=4   #for each distinct value, number of independent sims to run
 graph_sweep=false    #run the sweep once for each graph type
 original_seed=params[:random_seed]
 
 components=[[],[]]
-global comp_df=DataFrame(size_largest_comp=Int[],num_comps=Int[])
+global comp_df=DataFrame(size_largest_comp=Int[],num_comps=Int[],sim_tag=Int[])
 
 
 function param_sweeper(graph_name; additional_params...)
@@ -74,7 +74,8 @@ function param_sweeper(graph_name; additional_params...)
 
             push!(comp_df,
                 (overall_results[:size_largest_comp],
-                 overall_results[:num_comps]))
+                 overall_results[:num_comps],
+				 (i*num_values+j)))
 
             insertcols!(agent_results, 1, param_to_sweep => repeat(counter:counter,nrow(agent_results)))
             insertcols!(agent_results, 2, :seed => repeat(params[:random_seed]:params[:random_seed],nrow(agent_results)))
@@ -91,8 +92,11 @@ function param_sweeper(graph_name; additional_params...)
     sim_tag=0
     rm("$(tempdir())/$(graph_name)_agent_results.csv", force=true)
     rm("$(tempdir())/$(graph_name)_simulation_results.csv", force=true)
-    rm("$(tempdir())/$(graph_name)ParameterSweepPlot.png", force=true)
+    rm("$(tempdir())/$(graph_name)GiniSweepPlot.png", force=true)
     rm("$(tempdir())/$(graph_name)_wealth_heatmap.png", force=true)
+    rm("$(tempdir())/$(graph_name)Component&GiniSweepPlots.png", force=true)
+    rm("$(tempdir())/$(graph_name)ComponentSweepPlot.png", force=true)
+
 
     #this file contains all info with one line per agent in a given run of siml.jl
[…]

### 2019-06-21 src/net/param_sweep.jl
Remove "&" from filename. Fix indentation.

@@ -75,7 +75,7 @@ function param_sweeper(graph_name; additional_params...)
             push!(comp_df,
                 (overall_results[:size_largest_comp],
                  overall_results[:num_comps],
-				 (i*num_values+j)))
+                 (i*num_values+j)))
 
             insertcols!(agent_results, 1, param_to_sweep => repeat(counter:counter,nrow(agent_results)))
             insertcols!(agent_results, 2, :seed => repeat(params[:random_seed]:params[:random_seed],nrow(agent_results)))
@@ -94,7 +94,7 @@ function param_sweeper(graph_name; additional_params...)
     rm("$(tempdir())/$(graph_name)_simulation_results.csv", force=true)
     rm("$(tempdir())/$(graph_name)GiniSweepPlot.png", force=true)
     rm("$(tempdir())/$(graph_name)_wealth_heatmap.png", force=true)
-    rm("$(tempdir())/$(graph_name)Component&GiniSweepPlots.png", force=true)
+    rm("$(tempdir())/$(graph_name)Component_GiniSweepPlots.png", force=true)
     rm("$(tempdir())/$(graph_name)ComponentSweepPlot.png", force=true)
 
 
@@ -112,13 +112,13 @@ function param_sweeper(graph_name; additional_params...)
         gini=Float64[],
         gini_lowCI=Float64[],
         gini_highCI=Float64[],
-		number_components=Float64[],
-		number_components_lowCI=Float64[],
+        number_components=Float64[],
+        number_components_lowCI=Float64[],
         number_components_highCI=Float64[],
-		size_largest_component=Float64[],
-		size_largest_component_lowCI=Float64[],
+        size_largest_component=Float64[],
+        size_largest_component_lowCI=Float64[],
         size_largest_component_highCI=Float64[],
-	)
+    )
     names!(plot_df, prepend!(names(plot_df)[2:end], [param_to_sweep]))
 
 
@@ -147,7 +147,7 @@ function param_sweeper(graph_name; additional_params...)
                 agent_line_df[agent_line_df.sim_tag.==sim_tag,:sugar]))
             push!(curr_param_value_ginis, current_sim_gini)
             push!(curr_param_value_sizes,comp_df[comp_df[:sim_tag].==sim_tag,:size_largest_comp])
-			push!(curr_param_value_components,comp_df[comp_df[:sim_tag].==sim_tag,:num_comps])
[…]

### 2019-06-21 src/net/param_sweep.jl
Fix critical Gini bootstrap error. (Thanks Will!!)

@@ -158,7 +158,7 @@ function param_sweeper(graph_name; additional_params...)
         mark_seed_value=original_seed
 
         # Compute the average Gini, with CI, for this set of param values.
-        bs = bootstrap(x->Gini(x), curr_param_value_ginis,
+        bs = bootstrap(mean, curr_param_value_ginis,
             BasicSampling(params[:num_boot_samples]))
         ciGinis = confint(bs, BasicConfInt(.95))[1]
 

### 2019-06-21 src/net/param_sweep.jl
Force white background (not transparent) on plots.

@@ -208,6 +208,7 @@ function param_sweeper(graph_name; additional_params...)
             Geom.ribbon,
             Theme(default_color=colorant"lightblue")
         ),
+        Theme(background_color=colorant"white"),
         Guide.xlabel(string(param_to_sweep)), Guide.ylabel("Gini Index"))
 
     plotComponents=plot(plot_df,
@@ -251,13 +252,24 @@ function param_sweeper(graph_name; additional_params...)
             Geom.ribbon,
             Theme(default_color=colorant"pink",key_position=:top)
         ),
-        Guide.xlabel(string(param_to_sweep)),Guide.ylabel(nothing), Guide.manual_color_key("Legend", ["Agents in Largest Component", "Number of Components"], ["red", "green"]),style(key_position=:bottom))
+        Theme(background_color=colorant"white"),
+        Guide.xlabel(string(param_to_sweep)), Guide.ylabel(nothing),
+        Guide.manual_color_key("Legend",
+            ["Agents in Largest Component", "Number of Components"],
+            ["red", "green"]),
+        style(background_color=colorant"white",key_position=:bottom))
+
     compGiniPlot=vstack(plotLG,plotComponents)
+
     draw(PNG("$(tempdir())/$(graph_name)GiniSweepPlot.png"), plotLG)
     draw(PNG("$(tempdir())/$(graph_name)Component_GiniSweepPlots.png"), compGiniPlot)
     draw(PNG("$(tempdir())/$(graph_name)ComponentSweepPlot.png"), plotComponents)
     println("Creating $(param_to_sweep) agent heatmap...")
-    wealth_heatmap=plot(x=agent_line_df.sugar,y=agent_line_df[param_to_sweep],Geom.histogram2d,Guide.ylabel(string(param_to_sweep)), Guide.xlabel("Agent Wealth"))
+    wealth_heatmap=plot(x=agent_line_df.sugar,y=agent_line_df[param_to_sweep],
+        Geom.histogram2d,
+        Theme(background_color=colorant"white"),
+        Guide.ylabel(string(param_to_sweep)),
+        Guide.xlabel("Agent Wealth"))
     draw(PNG("$(tempdir())/$(graph_name)_wealth_heatmap.png"), wealth_heatmap)
 
     return Dict(:agent_line_df => agent_line_df,

### 2019-06-21 src/net/sim.jl

@@ -401,16 +401,19 @@ function plot_final_wealth_hist(sim_state::SimState)
 	final_wealthp = plot(
         x=final_wealths,
         Geom.histogram(density=true, bincount=20),
+        Theme(background_color=colorant"white"),
         Guide.xlabel("Agent Wealth"),
         Guide.ylabel("Density of agents"))
     final_proto_wealthp = plot(
         x=final_proto_wealths,
         Geom.histogram(density=true, bincount=20),
+        Theme(background_color=colorant"white"),
         Guide.xlabel("Proto Wealth"),
         Guide.ylabel("Density of protos"))
     final_proto_wealth_alivep = plot(
         x=final_proto_wealths_alive,
         Geom.histogram(density=true, bincount=20),
+        Theme(background_color=colorant"white"),
         Guide.xlabel("Proto Wealth"),
         Guide.ylabel("Density of protos"))		
     draw(PNG("$(tempdir())/final_agent_wealth_histogram.png"),final_wealthp)
@@ -453,6 +456,7 @@ function plot_gini_livingfrac_over_time(iter_results, callouts)
             Theme(default_color=colorant"black")
         ),
         Guide.xlabel("Iteration"), Guide.ylabel("Gini / fraction living"),
+        Theme(background_color=colorant"white"),
         Scale.color_discrete_manual("blue","green","red",
             levels=["1","2","3"]),
         Guide.title(join([ "$(c)=$(params[c])\n" for c in callouts ])))
@@ -508,7 +512,9 @@ function plot_iteration_graphs(iter)
             # Hard to know what to set the max value to.
             Scale.x_continuous(minvalue=0,
                 maxvalue=params[:init_sg_lvl]*
-                    params[:max_iters]/10)
+                    params[:max_iters]/10),
+
+        Theme(background_color=colorant"white"),
     )
 
     draw(PNG("$(tempdir())/wealth$(lpad(string(iter),3,'0')).png"),

### 2019-06-21 src/net/param_sweep.jl
Align x axes on stacked plot.

@@ -252,10 +252,11 @@ function param_sweeper(graph_name; additional_params...)
             Geom.ribbon,
             Theme(default_color=colorant"pink",key_position=:top)
         ),
-        Theme(background_color=colorant"white"),
-        Guide.xlabel(string(param_to_sweep)), Guide.ylabel(nothing),
+        Guide.xlabel(string(param_to_sweep)),
+        Guide.ylabel("Components", orientation=:vertical),
+        Guide.xticks(ticks=:auto, label=true, orientation=:horizontal),
         Guide.manual_color_key("Legend",
-            ["Agents in Largest Component", "Number of Components"],
+            ["Agents in Largest Component      .", "Number of Components"],
             ["red", "green"]),
         style(background_color=colorant"white",key_position=:bottom))
 

### 2019-06-21 src/net/param_sweep.jl
Increase height on stacked figure.

@@ -263,7 +263,8 @@ function param_sweeper(graph_name; additional_params...)
     compGiniPlot=vstack(plotLG,plotComponents)
 
     draw(PNG("$(tempdir())/$(graph_name)GiniSweepPlot.png"), plotLG)
-    draw(PNG("$(tempdir())/$(graph_name)Component_GiniSweepPlots.png"), compGiniPlot)
+    draw(PNG("$(tempdir())/$(graph_name)Component_GiniSweepPlots.png",
+        4inch, 6inch), compGiniPlot)
     draw(PNG("$(tempdir())/$(graph_name)ComponentSweepPlot.png"), plotComponents)
     println("Creating $(param_to_sweep) agent heatmap...")
     wealth_heatmap=plot(x=agent_line_df.sugar,y=agent_line_df[param_to_sweep],

### 2019-06-21 src/net/param_sweep.jl
Refactor data frame labeling.

@@ -34,10 +34,10 @@ function param_sweeper(graph_name; additional_params...)
     global agent_line_df = DataFrame(
         replace_this=Float64[],
         seed=Int[],
+        sim_tag=Int[],
         agent=String[],
         sugar=Float64[],
         proto_id=Int[],
-        sim_tag=Int[]
     )
     names!(agent_line_df,
         prepend!(names(agent_line_df)[2:end], [param_to_sweep]))
@@ -45,11 +45,21 @@ function param_sweeper(graph_name; additional_params...)
     global trial_line_df=DataFrame(
         replace_this=Float64[],
         seed=Int[],
+        sim_tag=Int[],
         gini=Float64[],
-        sim_tag=Int[]
     )
     names!(trial_line_df,
         prepend!(names(trial_line_df)[2:end], [param_to_sweep]))
+
+    global iter_line_df=DataFrame(
+        replace_this=Float64[],
+        seed=Int[],
+        sim_tag=Int[],
+        iter=Int[],
+        stage=Int[],
+    )
+    names!(iter_line_df,
+        prepend!(names(iter_line_df)[2:end], [param_to_sweep]))
 
     params[:make_anims] = false  # We would never want this true for a sweep
     params[:make_sim_plots] = false  # We would never want this true for a sweep
@@ -70,6 +80,7 @@ function param_sweeper(graph_name; additional_params...)
             # Actually run the simulation!
             results=specnet()
             agent_results = results[:agent_results]
+            iter_results = results[:iter_results]
             overall_results = results[:overall_results]
 
             push!(comp_df,
@@ -77,11 +88,12 @@ function param_sweeper(graph_name; additional_params...)
                  overall_results[:num_comps],
                  (i*num_values+j)))
 
-            insertcols!(agent_results, 1, param_to_sweep => repeat(counter:counter,nrow(agent_results)))
-            insertcols!(agent_results, 2, :seed => repeat(params[:random_seed]:params[:random_seed],nrow(agent_results)))
-            insertcols!(agent_results, 3, :sim_tag => repeat((i*num_values+j):(i*num_values+j),nrow(agent_results)))
+            add_sim_info!(agent_results, param_counter, counter, i*num_values+j)
+            iter_results = iter_results[[:iter,:stage]]  # only need these for now
+            add_sim_info!(iter_results, param_counter, counter, i*num_values+j)
 
             agent_line_df=[agent_line_df;agent_results]
[…]

### 2019-06-22 src/net/param_sweep.jl
Plot of proto properties.

@@ -19,7 +19,7 @@ graph_sweep=false    #run the sweep once for each graph type
 original_seed=params[:random_seed]
 
 components=[[],[]]
-global comp_df=DataFrame(size_largest_comp=Int[],num_comps=Int[],sim_tag=Int[])
+global social_connectivity_df=DataFrame(size_largest_comp=Int[],num_comps=Int[],average_proto_size=Float64[], num_protos=Int[],sim_tag=Int[])
 
 
 function param_sweeper(graph_name; additional_params...)
@@ -83,9 +83,12 @@ function param_sweeper(graph_name; additional_params...)
             iter_results = results[:iter_results]
             overall_results = results[:overall_results]
 
-            push!(comp_df,
+            push!(social_connectivity_df,
                 (overall_results[:size_largest_comp],
                  overall_results[:num_comps],
+				 overall_results[:average_proto_size],
+	             overall_results[:num_protos],
+
                  (i*num_values+j)))
 
             add_sim_info!(agent_results, param_counter, counter, i*num_values+j)
@@ -108,7 +111,7 @@ function param_sweeper(graph_name; additional_params...)
     rm("$(tempdir())/$(graph_name)_wealth_heatmap.png", force=true)
     rm("$(tempdir())/$(graph_name)Component_GiniSweepPlots.png", force=true)
     rm("$(tempdir())/$(graph_name)ComponentSweepPlot.png", force=true)
-
+    rm("$(tempdir())/$(graph_name)ProtoPropertiesSweep.png", force=true)
 
     #this file contains all info with one line per agent in a given run of siml.jl
     CSV.write("$(tempdir())/$(graph_name)_agent_results.csv",agent_line_df)
@@ -136,6 +139,12 @@ function param_sweeper(graph_name; additional_params...)
         time_to_stage3=Float64[],
         time_to_stage3_lowCI=Float64[],
         time_to_stage3_highCI=Float64[],
+		average_proto_size=Float64[],
+        average_proto_size_lowCI=Float64[],
+        average_proto_size_highCI=Float64[],
+		num_protos=Float64[],
+        num_protos_lowCI=Float64[],
+        num_protos_highCI=Float64[]
     )
     names!(plot_df, prepend!(names(plot_df)[2:end], [param_to_sweep]))
 
@@ -152,6 +161,8 @@ function param_sweeper(graph_name; additional_params...)
         curr_param_value_ginis = []
         curr_param_value_sizes = []
[…]

### 2019-06-22 src/net/sim.jl

@@ -265,12 +265,20 @@ function specnet(;additional_params...)
         num_agents = nums_agents
     )
     component_vertices=connected_components(graph)
+    total_proto_size=0
+	for p in arr_protos
+	    total_proto_size+=length(p.arr_member_ids)
+	end
+	proto_average_size=total_proto_size/length(arr_protos)
+	
     overall_results = Dict(
         :size_largest_comp => nv(graph) == 0 ? 0 : 
             findmax(length.(component_vertices))[1][1],
         :num_comps => nv(graph) == 0 ? 0 : 
-            length(component_vertices)
-    )
+            length(component_vertices),
+        :average_proto_size=>proto_average_size,
+        :num_protos=>length(arr_protos)		
+   )
 
     if params[:make_sim_plots]
         plot_gini_livingfrac_over_time(iter_results,
@@ -580,4 +588,3 @@ function all_parameters_legit(additional_params)
     end
     return true
 end
-

### 2019-06-22 src/net/param_sweep.jl
Update param_sweep.jl

@@ -200,10 +200,10 @@ function param_sweeper(graph_name; additional_params...)
         #Compute the average size of the largest component, with a CI for current params
         bs = bootstrap(mean, curr_param_value_sizes, BasicSampling(params[:num_boot_samples]))
         ciSizes = confint(bs, BasicConfInt(.95))[1]
-        #Compute the average proto size, with a CI for current params
+        #CI for average proto size for current params
         bs = bootstrap(mean, curr_param_value_proto_size, BasicSampling(params[:num_boot_samples]))
         ciProtoSizes = confint(bs, BasicConfInt(.95))[1]
-		#Compute the average size of the largest component, with a CI for current params
+        #CI for number of protos for current params
         bs = bootstrap(mean, curr_param_value_num_protos, BasicSampling(params[:num_boot_samples]))
         ciNumProtos = confint(bs, BasicConfInt(.95))[1]
         #Compute the average number of components, with a CI for current params

### 2019-06-23 src/net/param_sweep.jl
Make colors and legends consistent.

@@ -359,14 +359,14 @@ function param_sweeper(graph_name; additional_params...)
         Guide.ylabel("Time to reach stage", orientation=:vertical),
         Guide.xticks(ticks=:auto, label=true, orientation=:horizontal),
         Guide.manual_color_key("Legend",
-            ["Stage 2", "Stage 3"],
+            ["Stage 2      .", "Stage 3"],
             ["blue", "red"]),
         style(background_color=colorant"white",key_position=:bottom))
     plotProtos=plot(plot_df,
         layer(
             x=param_to_sweep, y=:num_protos_lowCI,
             Geom.line,
-            Theme(default_color=colorant"lightgreen")
+            Theme(default_color=colorant"lightgray")
         ),
         layer(
             x=param_to_sweep, y=:num_protos,
@@ -376,17 +376,17 @@ function param_sweeper(graph_name; additional_params...)
         layer(
             x=param_to_sweep, y=:num_protos_highCI,
             Geom.line,
-            Theme(default_color=colorant"lightgreen")
+            Theme(default_color=colorant"lightgray")
         ),
         layer(
             x=param_to_sweep, ymin=:num_protos_lowCI, ymax=:num_protos_highCI,
             Geom.ribbon,
-            Theme(default_color=colorant"green",key_position=:top)
+            Theme(default_color=colorant"lightgreen",key_position=:top)
         ),
         layer(
             x=param_to_sweep, y=:average_proto_size_lowCI,
             Geom.line,
-            Theme(default_color=colorant"orange")
+            Theme(default_color=colorant"lightgray")
         ),
         layer(
             x=param_to_sweep, y=:average_proto_size,
@@ -396,18 +396,18 @@ function param_sweeper(graph_name; additional_params...)
         layer(
             x=param_to_sweep, y=:average_proto_size_highCI,
             Geom.line,
-            Theme(default_color=colorant"orange")
+            Theme(default_color=colorant"lightgray")
         ),
         layer(
             x=param_to_sweep, ymin=:average_proto_size_lowCI, ymax=:average_proto_size_highCI,
             Geom.ribbon,
-            Theme(default_color=colorant"darkorange",key_position=:top)
+            Theme(default_color=colorant"orange",key_position=:top)
         ),
         Guide.xlabel(string(param_to_sweep)),
         Guide.ylabel("Protos", orientation=:vertical),
         Guide.xticks(ticks=:auto, label=true, orientation=:horizontal),
[…]

### 2019-06-23 src/net/setup_params.jl
(Fix whitespace errors.)

@@ -8,7 +8,7 @@ params = Dict{Symbol,Any}(
     :starvation_period => 10,       # the number of iterations to starve all agents
                                     #   after the simulation has reached stage 3
                                     #   (all live non-isolate agents in protos)
-    :openness => float(0.0),               # 0 <=> openness <=> 1
+    :openness => float(0.0),        # 0 <=> openness <=> 1
                                     #   (0: always choose from neighbor,
                                     #    1: always choose from entire city)
     :init_sg_lvl => 100,            # each agent starts with wealth
@@ -39,12 +39,12 @@ params = Dict{Symbol,Any}(
                                     #   - "complete"
                                     #   - "empty"
 
-    :λ => float(1),                        # ER: expected number if edges per node
+    :λ => float(1),                 # ER: expected number if edges per node
 
     :SF_edges => 40,                # SF: number of edges
     :SF_degree => 2,                # SF: exponent of expected power law degree
                                     #   distribution
 
-    :β => float(0.2),                      # SW: prob. of rewiring
+    :β => float(0.2),               # SW: prob. of rewiring
     :k => 2,                        # SW: degree of nodes
 )

### 2019-06-23 src/net/param_sweep.jl
Refactor param sweep plotting.

@@ -235,199 +235,29 @@ function param_sweeper(graph_name; additional_params...)
 
     CSV.write("$(tempdir())/$(graph_name)_simulation_results.csv",trial_line_df)
 
-    #drawing plots
-    println("Creating $(param_to_sweep) Gini plot...")
-    plotLG=plot(plot_df,
-        layer(
-            x=param_to_sweep, y=:gini_lowCI,
-            Geom.line,
-            Theme(default_color=colorant"lightgray")
-        ),
-        layer(
-            x=param_to_sweep, y=:gini,
-            Geom.line,
-            Theme(default_color=colorant"navy", line_width=.5mm)
-        ),
-        layer(
-            x=param_to_sweep, y=:gini_highCI,
-            Geom.line,
-            Theme(default_color=colorant"lightgray")
-        ),
-        layer(
-            x=param_to_sweep, ymin=:gini_lowCI, ymax=:gini_highCI,
-            Geom.ribbon,
-            Theme(default_color=colorant"lightblue")
-        ),
-        Theme(background_color=colorant"white"),
-        Guide.xlabel(string(param_to_sweep)), Guide.ylabel("Gini Index"))
-		
+    ginip = draw_plot(plot_df, param_to_sweep, Dict("gini"=>"navy"), "Gini")
+    compp = draw_plot(plot_df, param_to_sweep,
+        Dict("number_components"=>"green", "size_largest_component" => "red"),
+        "Components")
+    protop = draw_plot(plot_df, param_to_sweep,
+        Dict("num_protos"=>"green", "average_proto_size" => "brown"),
+        "Components")
 
-    println("Creating $(param_to_sweep) components plot...")
-    plotComponents=plot(plot_df,
-        layer(
-            x=param_to_sweep, y=:number_components_lowCI,
-            Geom.line,
-            Theme(default_color=colorant"lightgray")
-        ),
-        layer(
-            x=param_to_sweep, y=:number_components,
-            Geom.line,
-            Theme(default_color=colorant"green", line_width=.5mm)
-        ),
-        layer(
-            x=param_to_sweep, y=:number_components_highCI,
-            Geom.line,
-            Theme(default_color=colorant"lightgray")
-        ),
-        layer(
-            x=param_to_sweep, ymin=:number_components_lowCI, ymax=:number_components_highCI,
-            Geom.ribbon,
[…]

### 2019-06-23 src/net/param_sweep.jl
(Fix bad plot title.)

@@ -241,7 +241,7 @@ function param_sweeper(graph_name; additional_params...)
         "Components")
     protop = draw_plot(plot_df, param_to_sweep,
         Dict("num_protos"=>"green", "average_proto_size" => "brown"),
-        "Components")
+        "Protos")
 
     # zeros are meaningless in time-to-stage plots
     to_stage_df = plot_df[plot_df[:time_to_stage3] .> 0, :]

### 2019-06-23 src/net/sim.jl
Add warning for early sim termination.

@@ -249,6 +249,11 @@ function specnet(;additional_params...)
 
     end   # End main simulation for loop
 
+    terminated_early = false
+    if total_iters == params[:max_iters]
+        pri("\n*WARNING* sim terminated early at iteration $(total_iters)!\n")
+        terminated_early = true
+    end
 
     # Collect results in DataFrame.
     agent_results = DataFrame(
@@ -276,8 +281,9 @@ function specnet(;additional_params...)
             findmax(length.(component_vertices))[1][1],
         :num_comps => nv(graph) == 0 ? 0 : 
             length(component_vertices),
-        :average_proto_size=>proto_average_size,
-        :num_protos=>length(arr_protos)		
+        :average_proto_size => proto_average_size,
+        :num_protos => length(arr_protos),
+        :terminated_early => terminated_early,
    )
 
     if params[:make_sim_plots]

### 2019-06-23 src/net/param_sweep.jl
Simulation tag fix. Thanks Stephen!

@@ -89,11 +89,11 @@ function param_sweeper(graph_name; additional_params...)
 				 overall_results[:average_proto_size],
 	             overall_results[:num_protos],
 
-                 (i*num_values+j)))
+                 (i*trials_per_value+j)))
 
-            add_sim_info!(agent_results, param_counter, counter, i*num_values+j)
+            add_sim_info!(agent_results, param_counter, counter, i*trials_per_value+j)
             iter_results = iter_results[[:iter,:stage]]  # only need these for now
-            add_sim_info!(iter_results, param_counter, counter, i*num_values+j)
+            add_sim_info!(iter_results, param_counter, counter, i*trials_per_value+j)
 
             agent_line_df=[agent_line_df;agent_results]
             iter_line_df=[iter_line_df;iter_results]
@@ -167,7 +167,7 @@ function param_sweeper(graph_name; additional_params...)
         curr_param_value_p3s=[]
         for i=1:trials_per_value
 
-            sim_tag=(j*num_values+i)
+            sim_tag=(j*trials_per_value+i)
 
             # When not given a conf.level parameter, the R function Gini() from
             #   DescTools returns a single value: the Gini coefficient. We're

### 2019-06-23 src/net/param_sweep.jl
Plot # agents in proto. Shorten some var names.

@@ -19,7 +19,13 @@ graph_sweep=false    #run the sweep once for each graph type
 original_seed=params[:random_seed]
 
 components=[[],[]]
-global social_connectivity_df=DataFrame(size_largest_comp=Int[],num_comps=Int[],average_proto_size=Float64[], num_protos=Int[],sim_tag=Int[])
+global social_connectivity_df=DataFrame(
+    size_largest_comp=Int[],
+    num_comps=Int[],
+    average_proto_size=Float64[],
+    num_protos=Int[],
+    num_agents_in_proto=Int[],
+    sim_tag=Int[])
 
 
 function param_sweeper(graph_name; additional_params...)
@@ -88,6 +94,7 @@ function param_sweeper(graph_name; additional_params...)
                  overall_results[:num_comps],
 				 overall_results[:average_proto_size],
 	             overall_results[:num_protos],
+	             overall_results[:num_agents_in_proto],
 
                  (i*num_values+j)))
 
@@ -144,7 +151,10 @@ function param_sweeper(graph_name; additional_params...)
         average_proto_size_highCI=Float64[],
 		num_protos=Float64[],
         num_protos_lowCI=Float64[],
-        num_protos_highCI=Float64[]
+        num_protos_highCI=Float64[],
+		num_agents_in_proto=Float64[],
+        num_agents_in_proto_lowCI=Float64[],
+        num_agents_in_proto_highCI=Float64[],
     )
     names!(plot_df, prepend!(names(plot_df)[2:end], [param_to_sweep]))
 
@@ -158,13 +168,15 @@ function param_sweeper(graph_name; additional_params...)
 
     for j = 1:num_values
 
-        curr_param_value_ginis = []
-        curr_param_value_sizes = []
-        curr_param_value_components = []
-		curr_param_value_proto_size=[]
-		curr_param_value_num_protos=[]
-        curr_param_value_p2s=[]
-        curr_param_value_p3s=[]
+        # "curr" means "for all trials of the CURRent parameter value."
+        curr_ginis = []
+        curr_sizes = []
+        curr_components = []
+		curr_proto_size=[]
+		curr_num_protos=[]
+		curr_num_agents_in_proto=[]
+        curr_s2s=[]
+        curr_s3s=[]
         for i=1:trials_per_value
 
             sim_tag=(j*num_values+i)
@@ -176,13 +188,14 @@ function param_sweeper(graph_name; additional_params...)
[…]

### 2019-06-23 src/net/sim.jl

@@ -275,6 +275,7 @@ function specnet(;additional_params...)
 	    total_proto_size+=length(p.arr_member_ids)
 	end
 	proto_average_size=total_proto_size/length(arr_protos)
+    num_agents_in_proto = sum([ ag.a.proto_id ≠ -1 for ag ∈  keys(AN) ])
 	
     overall_results = Dict(
         :size_largest_comp => nv(graph) == 0 ? 0 : 
@@ -284,6 +285,7 @@ function specnet(;additional_params...)
         :average_proto_size => proto_average_size,
         :num_protos => length(arr_protos),
         :terminated_early => terminated_early,
+        :num_agents_in_proto => num_agents_in_proto,
    )
 
     if params[:make_sim_plots]

### 2019-06-23 src/net/param_sweep.jl
Return pre- and post-starvation results.

@@ -88,6 +88,7 @@ function param_sweeper(graph_name; additional_params...)
             agent_results = results[:agent_results]
             iter_results = results[:iter_results]
             overall_results = results[:overall_results]
+            starvation_results = results[:starvation_results]
 
             push!(social_connectivity_df,
                 (overall_results[:size_largest_comp],

### 2019-06-23 src/net/sim.jl

@@ -127,6 +127,7 @@ function specnet(;additional_params...)
     local stages=[]
     local nums_agents=[]
 
+    local overall_results
     for iter in 1:params[:max_iters]
 
         global graph, locs_x, locs_y
@@ -143,6 +144,8 @@ function specnet(;additional_params...)
         if iter % 10 == 0 println(iter) end
 
         if stages[end] == 3
+            # Collect stats on the model right before the starvation period.
+            overall_results = collect_stats(SimState(graph, AN, arr_protos))
             starvation_timer += 1
             if starvation_timer == params[:starvation_period]
                 total_iters = iter - 1
@@ -269,24 +272,13 @@ function specnet(;additional_params...)
         stage = stages,
         num_agents = nums_agents
     )
-    component_vertices=connected_components(graph)
-    total_proto_size=0
-	for p in arr_protos
-	    total_proto_size+=length(p.arr_member_ids)
-	end
-	proto_average_size=total_proto_size/length(arr_protos)
-    num_agents_in_proto = sum([ ag.a.proto_id ≠ -1 for ag ∈  keys(AN) ])
 	
-    overall_results = Dict(
-        :size_largest_comp => nv(graph) == 0 ? 0 : 
-            findmax(length.(component_vertices))[1][1],
-        :num_comps => nv(graph) == 0 ? 0 : 
-            length(component_vertices),
-        :average_proto_size => proto_average_size,
-        :num_protos => length(arr_protos),
-        :terminated_early => terminated_early,
-        :num_agents_in_proto => num_agents_in_proto,
-   )
+    # Collect stats on the model after the starvation period.
+    starvation_results = collect_stats(SimState(graph, AN, arr_protos))
+    if !isdefined(Main, :overall_results)
+        # Not totally sure what to do in this WARNING case.
+        overall_results = starvation_results
+    end
 
     if params[:make_sim_plots]
         plot_gini_livingfrac_over_time(iter_results,
@@ -304,7 +296,9 @@ function specnet(;additional_params...)
 
     return Dict(:agent_results => sort(agent_results, :agent),
         :iter_results => iter_results,
-        :overall_results => overall_results)
+        :overall_results => overall_results,
+        :starvation_results => starvation_results,
+        :terminated_early => terminated_early)
 end
 
 
@@ -583,6 +577,21 @@ function get_stage(sim_state::SimState)
         end
[…]

### 2019-06-23 src/net/param_sweep.jl
(Fix indentation.)

@@ -93,9 +93,9 @@ function param_sweeper(graph_name; additional_params...)
             push!(social_connectivity_df,
                 (overall_results[:size_largest_comp],
                  overall_results[:num_comps],
-				 overall_results[:average_proto_size],
-	             overall_results[:num_protos],
-	             overall_results[:num_agents_in_proto],
+                 overall_results[:average_proto_size],
+                 overall_results[:num_protos],
+                 overall_results[:num_agents_in_proto],
 
                  (i*trials_per_value+j)))
 
@@ -147,13 +147,13 @@ function param_sweeper(graph_name; additional_params...)
         time_to_stage3=Float64[],
         time_to_stage3_lowCI=Float64[],
         time_to_stage3_highCI=Float64[],
-		average_proto_size=Float64[],
+        average_proto_size=Float64[],
         average_proto_size_lowCI=Float64[],
         average_proto_size_highCI=Float64[],
-		num_protos=Float64[],
+        num_protos=Float64[],
         num_protos_lowCI=Float64[],
         num_protos_highCI=Float64[],
-		num_agents_in_proto=Float64[],
+        num_agents_in_proto=Float64[],
         num_agents_in_proto_lowCI=Float64[],
         num_agents_in_proto_highCI=Float64[],
     )
@@ -173,9 +173,9 @@ function param_sweeper(graph_name; additional_params...)
         curr_ginis = []
         curr_sizes = []
         curr_components = []
-		curr_proto_size=[]
-		curr_num_protos=[]
-		curr_num_agents_in_proto=[]
+        curr_proto_size=[]
+        curr_num_protos=[]
+        curr_num_agents_in_proto=[]
         curr_s2s=[]
         curr_s3s=[]
         for i=1:trials_per_value
@@ -240,9 +240,9 @@ function param_sweeper(graph_name; additional_params...)
                                 ciSizes[1], ciSizes[2], ciSizes[3],
                                 s2Times[1], s2Times[2], s2Times[3],
                                 s3Times[1], s3Times[2], s3Times[3],
-								ciProtoSizes[1], ciProtoSizes[2], ciProtoSizes[3],
-								ciNumProtos[1], ciNumProtos[2], ciNumProtos[3],
-								ciNumAginP[1], ciNumAginP[2], ciNumAginP[3],
+                                ciProtoSizes[1], ciProtoSizes[2], ciProtoSizes[3],
[…]

### 2019-06-23 src/net/param_sweep.jl
Store values, not arrays. (?)

@@ -190,12 +190,12 @@ function param_sweeper(graph_name; additional_params...)
             current_sim_gini = convert(Float64, Gini(
                 agent_line_df[agent_line_df.sim_tag.==sim_tag,:sugar]))
             push!(curr_ginis, current_sim_gini)
-            push!(curr_sizes,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:size_largest_comp])
-            push!(curr_components,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:num_comps])
-            push!(curr_proto_size,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:average_proto_size])
-			push!(curr_num_protos,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:num_protos])
-			push!(curr_num_agents_in_proto,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:num_agents_in_proto])
-			push!(curr_s2s,first_iter_of_stage(iter_line_df, 2, sim_tag))
+            push!(curr_sizes,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:size_largest_comp][1])
+            push!(curr_components,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:num_comps][1])
+            push!(curr_proto_size,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:average_proto_size][1])
+            push!(curr_num_protos,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:num_protos][1])
+            push!(curr_num_agents_in_proto,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:num_agents_in_proto][1])
+            push!(curr_s2s,first_iter_of_stage(iter_line_df, 2, sim_tag))
             push!(curr_s3s,first_iter_of_stage(iter_line_df, 3, sim_tag))
             #adding results to the df
             push!(trial_line_df,(counter,mark_seed_value,sim_tag,
@@ -370,7 +370,7 @@ lighter_shade_of = Dict(
     "brown" => "orange",
 )
 
-		
+
 #runs a sweep for a given parameter once for each graph type,
 #saving the dataframes and plots to multiple files
 

### 2019-06-23 src/net/param_sweep.jl
Don't compute Gini of all NaNs.

@@ -207,9 +207,14 @@ function param_sweeper(graph_name; additional_params...)
         mark_seed_value=original_seed
 
         # Compute the average Gini, with CI, for this set of param values.
-        bs = bootstrap(mean, curr_ginis,
-            BasicSampling(params[:num_boot_samples]))
-        ciGinis = confint(bs, BasicConfInt(.95))[1]
+        if all([isnan(g) for g in curr_ginis])
+            # TODO: getting around a numerical error for now
+            ciGinis = [.5,.5,.5]
+        else
+            bs = bootstrap(mean, curr_ginis,
+                BasicSampling(params[:num_boot_samples]))
+            ciGinis = confint(bs, BasicConfInt(.95))[1]
+        end
 
         #Compute the average size of the largest component, with a CI for current params
         bs = bootstrap(mean, curr_sizes, BasicSampling(params[:num_boot_samples]))

### 2019-06-23 src/net/param_sweep.jl
Add # living agents to param sweep plot.

@@ -25,6 +25,8 @@ global social_connectivity_df=DataFrame(
     average_proto_size=Float64[],
     num_protos=Int[],
     num_agents_in_proto=Int[],
+    num_living_agents_pre=Float64[],
+    num_living_agents_post=Float64[],
     sim_tag=Int[])
 
 
@@ -96,6 +98,8 @@ function param_sweeper(graph_name; additional_params...)
                  overall_results[:average_proto_size],
                  overall_results[:num_protos],
                  overall_results[:num_agents_in_proto],
+                 overall_results[:num_living_agents],     # shouldn't be here
+                 starvation_results[:num_living_agents],  # shouldn't be here
 
                  (i*trials_per_value+j)))
 
@@ -156,6 +160,12 @@ function param_sweeper(graph_name; additional_params...)
         num_agents_in_proto=Float64[],
         num_agents_in_proto_lowCI=Float64[],
         num_agents_in_proto_highCI=Float64[],
+        num_living_agents_pre=Float64[],
+        num_living_agents_pre_lowCI=Float64[],
+        num_living_agents_pre_highCI=Float64[],
+        num_living_agents_post=Float64[],
+        num_living_agents_post_lowCI=Float64[],
+        num_living_agents_post_highCI=Float64[],
     )
     names!(plot_df, prepend!(names(plot_df)[2:end], [param_to_sweep]))
 
@@ -178,6 +188,8 @@ function param_sweeper(graph_name; additional_params...)
         curr_num_agents_in_proto=[]
         curr_s2s=[]
         curr_s3s=[]
+        curr_num_living_agents_pre=[]
+        curr_num_living_agents_post=[]
         for i=1:trials_per_value
 
             sim_tag=(j*trials_per_value+i)
@@ -197,6 +209,8 @@ function param_sweeper(graph_name; additional_params...)
             push!(curr_num_agents_in_proto,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:num_agents_in_proto][1])
             push!(curr_s2s,first_iter_of_stage(iter_line_df, 2, sim_tag))
             push!(curr_s3s,first_iter_of_stage(iter_line_df, 3, sim_tag))
+            push!(curr_num_living_agents_pre,social_connectivity_df[social_connectivity_df[:sim_tag].==sim_tag,:num_living_agents_pre][1])
[…]

### 2019-06-23 src/net/sim.jl

@@ -127,7 +127,7 @@ function specnet(;additional_params...)
     local stages=[]
     local nums_agents=[]
 
-    local overall_results
+    global overall_results
     for iter in 1:params[:max_iters]
 
         global graph, locs_x, locs_y
@@ -144,8 +144,10 @@ function specnet(;additional_params...)
         if iter % 10 == 0 println(iter) end
 
         if stages[end] == 3
-            # Collect stats on the model right before the starvation period.
-            overall_results = collect_stats(SimState(graph, AN, arr_protos))
+            if starvation_timer == 0
+                # Collect stats on the model right before the starvation period.
+                overall_results = collect_stats(SimState(graph, AN, arr_protos))
+            end
             starvation_timer += 1
             if starvation_timer == params[:starvation_period]
                 total_iters = iter - 1
@@ -277,7 +279,7 @@ function specnet(;additional_params...)
     starvation_results = collect_stats(SimState(graph, AN, arr_protos))
     if !isdefined(Main, :overall_results)
         # Not totally sure what to do in this WARNING case.
-        overall_results = starvation_results
+        overall_results = copy(starvation_results)
     end
 
     if params[:make_sim_plots]
@@ -591,6 +593,7 @@ function collect_stats(s::SimState)
         :average_proto_size => proto_average_size,
         :num_protos => length(s.arr_protos),
         :num_agents_in_proto => num_agents_in_proto,
+        :num_living_agents => length([ a for a ∈  keys(s.AN) if a.a.alive ]),
    )
 end
 

### 2019-06-24 src/net/sim.jl
Kill dead protos Fix #65

@@ -79,6 +79,7 @@ function specnet(;additional_params...)
     # The initial social network.
     global graph = choose_graph()
 
+    arr_dead_protos=[]
 
     suglvl_distrib = DiscreteUniform(1, params[:init_sg_lvl])
     white_noise_distrib = Normal(0, params[:white_noise_intensity])
@@ -95,7 +96,7 @@ function specnet(;additional_params...)
     ## the following is a hack; see comment in ../scape/run-simulation.jl
     arr_protos = [Proto(-1, -1, false, ["-"], [Transaction(-1, -1, "", "-")])]
 
-
+ 
     # (Erase old images.)
     save_dir = pwd()
     cd("$(tempdir())")
@@ -237,6 +238,9 @@ function specnet(;additional_params...)
                 push!(wealthArray,ag.a.sugar_level)
             end
         end
+		
+		kill_proto(SimState(graph, AN, arr_protos))
+		
         # The R function Gini() from DescTools returns a vector of three values
         #   if conf.level is not NA: (1) the estimate, (2) the lower bound of
         #   the CI, and (3) the upper bound.
@@ -309,6 +313,25 @@ end
 # Mark the agent "dead" whose agent number is passed. This involves
 # surgically removing it from the graph, adjusting the agent-to-node mappings,
 # and deleting it from the list of last-frame's plot coordinates.
+
+function kill_proto(sim_state::SimState)
+	index=length(sim_state.arr_protos)
+	while index>0
+        if(sim_state.arr_protos[index].balance<=0)
+            for id in sim_state.arr_protos[index].arr_member_ids
+                for ag in keys(AN)
+                    if ag.a.agent_id==id
+                        ag.a.proto_id=-1
+                    end
+                end
+            end
+        push!(arr_dead_protos,sim_state.arr_protos[index])
+		deleteat!(sim_state.arr_protos,index)
+		end
+        index-=1    
+	end
+end	
+		    
 function kill_agent(dying_agent)
     global graph, AN, locs_x, locs_y
     dying_node = AN[dying_agent]

### 2019-06-24 src/net/setup_params.jl
Kill dead protos Fix #65

@@ -15,10 +15,10 @@ params = Dict{Symbol,Any}(
                                     #   ~U(1, init_sg_lvl)
     :metabolic_rate => 5,           # each iteration, each agent consumes exactly
                                     #   this much sugar
-    :salary => 10,                  # each iteration, each agent receives exactly
+    :salary => 10,                   # each iteration, each agent receives exactly
                                     #   this much sugar
-    :white_noise_intensity => 1,    # each iteration, an agent receives (or loses)
-                                    #   ~N(0, white_noise_intensity) extra sugar
+    :white_noise_intensity =>       # each iteration, an agent receives (or loses)
+        float(1.0),                 #   ~N(0, white_noise_intensity) extra sugar
     :proto_threshold => 50,         # each agent in an encounter must have
                                     #   > wealth than this to form a proto
     :make_anims => false,           # create animations of results?

### 2019-06-25 manuscript/draftcssa19.tex
notes added
more outlines
intro

@@
 \section{Introduction}
+In recent years, concerns and debates surrounding wealth inequality and socioeconomic mobility have been one of the few unifying issues dominating the extremely polarized public spheres of the Global North.
+While economic and political inquality used to be discussed in not so mainstream heterodox economics circles, the contentious discussions on the topic since the publication of Piketty's book suggests a lack of consensus about very basic foundational questions like the origins and persistence of economic inequality.
+Not surprisingly, traditional theories and tools of macro and micro economics are now being diagnosed for its limitations.
+Simultaneously, insights from related disciplines along with novel scientific inquiry models not usually associated with traditional econometrics are being taken more seriously.
+The current work shares this spirit by integrating substantive ideas from anthropology, economic sociology and urban sociology and using modelling approaches from computational social science and analytical sociology to understand the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
+
+%The current plan is start with economics economic sociology and wealth dynamic models.
+The former is discussed in Jackson's review, the latter in rvenkat's CSSA18 paper.
+Then we move on to how wealth dynamics and inequality questions matter also to other fields like anthropology and sociology.
+Wealh dynamics in such situations can also be addressed using economic models and is the focus of our manuscript.
+
+%The general idea is to discuss how/why social networks matter wealth accumulation dynamics.
+We have references from anthropology.
+We have references in economic sociology(jackson).Sampson's work and Venkatesh's work can be used when talking about urban poverty and urban sociology.
+Discuss how in economics, wealth accumulation dynamics are mostly discussed at the macroeconomic level.
+In this sense, this work (and the work presented last year) are novel in this regard.
+
+%% Sampson's work seem to be crucial for making the claim that social structures and neighborhood effects are important determinants of economic outcomes.
+
+% Wealth accumulation models all start from fancy macroeconomic models and may not be well suited for studying wealth accumulation processes under poverty where high level of stochasticity seem to matter.
+
+%While we are interested in more sophisticated models, we are more interested in extracting the effects of social network structure in simple models of cooperative wealth accumulation.
+The proto-institution is definetely borrowed from SriMil.
+In order to study more elaborate and economically rigorous wealth dynamics, we need to be able sort of the effects of network structure in simple stylized network models.
+The work on ER models is expected to be first of our analysis.
+Eventually, we plan to get to more realistic wealth accumulation models of interest to economists but for now this is all we have.
+
+\cite{power2018cooperation,power2018}
+
+\cite{koster2019,koster2014,koster2015,bogerhoff2015}
+
+\cite{smith2019,nolin2012}
 
@@
 
+%In Katz's book, the differing life histories of individuals in Hamilton, Canada suggest that luck played a role in deterministic life outcomes.
+Katz argues that social mobility makes sense only in the context of social structure
+
+%Katz's chapter 2.
+His main argument there is that the structure of inequality rpresent in Hamilton, Canada is representative of inequality present in all other north american cities of that era.
+The persistence of inequality can be see in the persistence of four kinds of social structures.
+1) occupational structure, 2) division of wealth and proportion of the wealthy, 3) social and demographic identity of different economic ranks, and 4) distance between people of different socio-economic ranks or social stratification.
+He talks about peristence of networks of wealth and power.
+Points out strong interconnection between property, political power and social status.
+Argues that economic stratification and its crystallization leads to crystallization of social and other subjective stratifications.
+
 \section{Model}
 ~\cite{redner2001guide}
+%Use chapter 3 of redner's book here. 
+%Also, the network model presented here seem to be one of a kind.
+Typicall dynamcics on networks are deterministic in nature.
+The models discussed here is different from deterministic dynamic processes and epidemic processes, and diffusion type processes (percolation processes).
+The models are stochastic dynamic systems on networks.
+Such social processes are studied using Stochastic Actor Oriented Models (SOAM) Snidjers.
+ALso use Kolacyzk and Csardi's discussion as reference.
+Social influence models.....
+and others) This is not directly about influence but more about cooperation.
+Need to find a nice way of talking about this.
+
+%In the model section, we motivate our current specnet model as attempts to capture specific aspects of historical sociology and urban sociology of Katz and Samson respectively.
 
@@
 \section{Conclusion and Future Work}
-%what kinds of real world systems are we talking about?
+%what kinds of real world systems are we talking about?This section should write itself. Just a brief discussion of phase 2+ and integration with spescape should suffice 
+%I am actually confused about whether such a purely preliminary work can say antyhing about the real world.
+Do we really want to say anything at all about the real world.
+What can ER graphs say about the real world?
+
+%We conclude by discussing features of social processes and mechanisms argued for by both Sampson and Katz that are currently not present in the model but important and part of the vision for where our model is headed.
+
+%We also include the goal of seamlessly going from a model with no geography to a model with geography.
+
 \bibliography{ref_cssa19}

### 2019-06-25 src/net/sim.jl
Don't die computing bootstrap for all-NaN Ginis.

@@ -248,9 +248,13 @@ function specnet(;additional_params...)
         #   (which use bootstrapping, and are therefore time-consuming) to get
         #   all three. Otherwise, just get (1).
         if params[:make_sim_plots]
-            rGini=Gini(wealthArray; Symbol("conf.level")=>.95,
-                :R=>params[:num_boot_samples])
-            ginis[iter,:] = [ convert(Float16,r) for r in rGini ]
+            if length(wealthArray) > 0
+                rGini=Gini(wealthArray; Symbol("conf.level")=>.95,
+                    :R=>params[:num_boot_samples])
+                ginis[iter,:] = [ convert(Float16,r) for r in rGini ]
+            else
+                ginis[iter,:] = [ NaN, NaN, NaN ]
+            end
         else
             rGini=Gini(wealthArray)
             ginis[iter,1] = convert(Float16,rGini)
@@ -465,6 +469,13 @@ end
 # The callouts parameter should be a list of symbols which should appear in the
 # title's plot.
 function plot_gini_livingfrac_over_time(iter_results, callouts)
+
+    # Remove rows with NaNs.
+    for col in names(iter_results)
+        iter_results[col] = map(x->isnan(x) ? missing : x, iter_results[col])
+    end
+    iter_results = iter_results[completecases(iter_results),:]
+
     stage_names = Dict(1=>"1", 2=>"2", 3=>"3")
     iter_results.stage = [ stage_names[s] for s in iter_results.stage ]
     iter_results.num_agents /= maximum(iter_results.num_agents)

### 2019-06-25 src/net/sim.jl
Fix sugar-level-of-dying-agents bug.

@@ -212,7 +212,7 @@ function specnet(;additional_params...)
                 if ag.a.sugar_level < 0 && ag.a.alive ]
         for dying_agent in dying_agents
             try
-                in_the_hole = ag.a.sugar_level
+                in_the_hole = dying_agent.a.sugar_level
                 withdraw_from_proto!(dying_agent, arr_protos, iter)
                 prd("Agent $(dying_agent) got some money! " *
                     "(had $(in_the_hole), " *
@@ -222,7 +222,7 @@ function specnet(;additional_params...)
             catch exc
                 if isa(exc, NotEnoughSugarException)
                     prd("Agent $(dying_agent) died!! " *
-                        "(needed -$(dying_agent.a.sugar_level), only had " *
+                        "(needed $(-dying_agent.a.sugar_level), only had " *
                         "$(arr_protos[dying_agent.a.proto_id].balance) in proto)")
                 else
                     prd("Agent $(dying_agent) died!! (no proto)")

### 2019-06-25 manuscript/draftcssa19.tex
minor

@@
 The current work shares this spirit by integrating substantive ideas from anthropology, economic sociology and urban sociology and using modelling approaches from computational social science and analytical sociology to understand the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
+
+The current work originated in our attempts to incorporate and tease out the effects of social structures in simple models of wealth dynamics in the presence of environmental stochasticity, and a simple form of resource pooling.
+These models were inspired by our search for analogs of grid world agent based models of Srikanth and Milton \footnote{Include proper citation of SriMil here} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
+While interaction or mixing of agent population is achieved through foraging in the original model, the model presented here achieves this by partially mixing the agents via a static network structure.
+
+The original model drew its inspiration from historical sociology, in Katz's influential study of middle of 19th century Hamilton, Canada.
+Retaining this original motivation, we draw additional inspiration from economic sociology, in the work of Grannovetter; urban sociology, in the work of Sampson and others; and in anthropology, in the work on cooperation in small to medium scale societies.
 

### 2019-06-25 src/net/sim.jl
Rework dying-protos handling.

@@ -193,7 +193,7 @@ function specnet(;additional_params...)
 
         #Makes the agents deposit any excess sugar into their proto
         for ag in keys(AN)
-            if ag.a.proto_id ≠ -1
+            try
                 current = fetch_specific_proto_obj(arr_protos, ag.a.proto_id)
                 if ag.a.sugar_level > params[:proto_threshold]
                     deposit_amt = ag.a.sugar_level - params[:proto_threshold]
@@ -204,6 +204,9 @@ function specnet(;additional_params...)
                     current.balance += deposit_amt
                     push!(current.ledger_transactions, transaction)
                 end
+            catch DomainError
+                # This agent's proto has died because some other agent
+                # exhausted it. Never mind.
             end
         end
 
@@ -212,32 +215,33 @@ function specnet(;additional_params...)
                 if ag.a.sugar_level < 0 && ag.a.alive ]
         for dying_agent in dying_agents
             try
-                in_the_hole = dying_agent.a.sugar_level
-                withdraw_from_proto!(dying_agent, arr_protos, iter)
-                prd("Agent $(dying_agent) got some money! " *
-                    "(had $(in_the_hole), " *
-                    "now has $(dying_agent.a.sugar_level), " *
-                    "proto still has " *
-                    "$(arr_protos[dying_agent.a.proto_id].balance))")
+                if dying_agent.a.proto_id == -1
+                    prd("Agent $(dying_agent) died!! " *
+                        "(needed $(-dying_agent.a.sugar_level), " *
+                        "and had no proto).")
+                else
+                    in_the_hole = dying_agent.a.sugar_level
+                    withdraw_from_proto!(dying_agent, arr_protos, iter)
+                    prd("Agent $(dying_agent) got some money! " *
+                        "(had $(in_the_hole), " *
+                        "now has $(dying_agent.a.sugar_level), " *
+                        "proto still has " *
+                        "$(fetch_specific_proto_obj(arr_protos,dying_agent.a.proto_id).balance).)")
+                end
             catch exc
                 if isa(exc, NotEnoughSugarException)
                     prd("Agent $(dying_agent) died!! " *
-                        "(needed $(-dying_agent.a.sugar_level), only had " *
-                        "$(arr_protos[dying_agent.a.proto_id].balance) in proto)")
+                        "(needed $(-dying_agent.a.sugar_level) " *
[…]

### 2019-06-25 src/star/Protos.jl

@@ -8,7 +8,7 @@ mutable struct Transaction
     transaction_amount::Float64
     period::Int32
     type::String ## deposit or withdrawal or closure
-    agent_id::String    
+    agent_id::String
 end
 
 mutable struct Proto
@@ -27,8 +27,12 @@ function fetch_specific_proto_obj(arr_protos, proto_id)
     Return a proto object from the given array of proto objects
     that has the given proto id.
     """
-    return [probj for probj in arr_protos 
-            if probj.proto_id == proto_id][1] 
+    matching_protos = [probj for probj in arr_protos
+        if probj.proto_id == proto_id]
+    if length(matching_protos) ≠ 1
+        throw(DomainError(proto_id))
+    end
+    return matching_protos[1]
 end
 
 function form_possible_protos!(arr_agents, agent_environment, arr_protos,
@@ -40,23 +44,23 @@ function form_possible_protos!(arr_agents, agent_environment, arr_protos,
     (a) none of the focal agent's neighbors are part of a proto
     (b) one of the focal agent's neighbors is part of a proto
     (c) two or more of the focal agent's neighbors are part of a proto.
-    
+
     In the case of (a), a randomly chosen neighbor and the focal agent join to
     form a proto.
     In the case of (b), the focal agent joins the proto of the neighbor.
-    In the case of (c), the focal agent joins the proto of a 
+    In the case of (c), the focal agent joins the proto of a
     randomly-chosen neighbor.
-    
+
     Modifies focal and neighbor agents' proto_id field, if proto-
     formation or joining occurs.
-    Reduces the focal agent and neighbor agents' sugarlevels by an amount 
+    Reduces the focal agent and neighbor agents' sugarlevels by an amount
     = sugarlevel - params[:threshold].
 
     Modifies the array of protos by adding, as needed, new proto struct.
-    
+
     Returns an array of Proto structures to the caller.
     """
-    
+
     threshold = params[:proto_threshold]
     start_proto_id = begin
         if length(arr_protos) == 1 && arr_protos[1].proto_id == -1
@@ -84,18 +88,18 @@ function form_possible_protos!(arr_agents, agent_environment, arr_protos,
                     agobj.a.proto_id = next_proto_id
                     deposit_amt = agobj.a.sugar_level - threshold
                     transaction1 = Transaction(deposit_amt,
-                                               timeperiod, "deposit", 
+                                               timeperiod, "deposit",
                                                agobj.a.agent_id)
                     agobj.a.sugar_level -= deposit_amt
 
[…]

### 2019-06-25 src/net/sim.jl
Kill protos (make agent proto_id -2). Don't add to proto -1's balance.

@@ -219,6 +219,12 @@ function specnet(;additional_params...)
                     prd("Agent $(dying_agent) died!! " *
                         "(needed $(-dying_agent.a.sugar_level), " *
                         "and had no proto).")
+                    kill_agent(dying_agent)
+                elseif dying_agent.a.proto_id == -2
+                    prd("Agent $(dying_agent) died!! " *
+                        "(needed $(-dying_agent.a.sugar_level), " *
+                        "but proto has already been exhausted. (1)")
+                    kill_agent(dying_agent)
                 else
                     in_the_hole = dying_agent.a.sugar_level
                     withdraw_from_proto!(dying_agent, arr_protos, iter)
@@ -234,9 +240,13 @@ function specnet(;additional_params...)
                         "(needed $(-dying_agent.a.sugar_level) " *
                         "and proto only had " *
                         "$(fetch_specific_proto_obj(arr_protos,dying_agent.a.proto_id).balance).)")
+                elseif isa(exc, DomainError)
+                    prd("Agent $(dying_agent) died!! " *
+                        "(needed $(-dying_agent.a.sugar_level), " *
+                        "but proto has already been exhausted. (2)")
                 else
                     prd("    SHOULD NEVER GET HERE")
-                    quit()
+                    error(1)
                 end
                 kill_agent(dying_agent)
             end
@@ -328,11 +338,12 @@ function kill_sugarless_protos(sim_state::SimState, arr_dead_protos)
     while index>0
         if(sim_state.arr_protos[index].proto_id ≠ -1 &&
                 sim_state.arr_protos[index].balance<=0)
-            pri("Killing proto $(sim_state.arr_protos[index].proto_id)")
+            prd("Killing proto $(sim_state.arr_protos[index].proto_id)")
             for id in sim_state.arr_protos[index].arr_member_ids
                 for ag in keys(AN)
                     if ag.a.agent_id==id
-                        ag.a.proto_id=-1
+                        ag.a.proto_id=-2    # new value, indicating "was once
+                                            #   in a proto, but no longer."
                     end
                 end
             end

### 2019-06-25 src/star/Protos.jl

@@ -29,7 +29,7 @@ function fetch_specific_proto_obj(arr_protos, proto_id)
     """
     matching_protos = [probj for probj in arr_protos
         if probj.proto_id == proto_id]
-    if length(matching_protos) ≠ 1
+    if proto_id == -1  ||  length(matching_protos) ≠ 1
         throw(DomainError(proto_id))
     end
     return matching_protos[1]

### 2019-06-26 manuscript/draftcssa19.tex
Add note: sim code description in Model section.
two more paragraphs

--- 2019-06-25 manuscript/draftcssa19.tex
@@
 In recent years, concerns and debates surrounding wealth inequality and socioeconomic mobility have been one of the few unifying issues dominating the extremely polarized public spheres of the Global North.
-While economic and political inquality used to be discussed in not so mainstream heterodox economics circles, the contentious discussions on the topic since the publication of Piketty's book suggests a lack of consensus about very basic foundational questions like the origins and persistence of economic inequality.
+While economic and political inequality used to be discussed in not so mainstream heterodox economics circles, the contentious discussions on the topic within mainstream economics since the publication of Piketty's book~\cite{piketty2017capital} suggests a lack of consensus about very basic foundational questions like the origins and persistence of economic inequality.
 Not surprisingly, traditional theories and tools of macro and micro economics are now being diagnosed for its limitations.
 Simultaneously, insights from related disciplines along with novel scientific inquiry models not usually associated with traditional econometrics are being taken more seriously.
-The current work shares this spirit by integrating substantive ideas from anthropology, economic sociology and urban sociology and using modelling approaches from computational social science and analytical sociology to understand the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
+The work presented here shares this spirit by integrating substantive ideas from anthropology, economic sociology~\cite{granovetter2017society} and urban sociology~\cite{sampson2012great} and using modeling approaches from computational social science~\cite{hedstrom2018} and analytical sociology~\cite{hedstrom2011oxford} to understand the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
+
+The current work originated in our attempts to incorporate and tease out the effects of social structures in simple models of wealth dynamics in the presence of environmental stochasticity, and a simple form of resource pooling.
+These models were inspired by our search for analogs of grid world agent based models of Srikanth and Milton \footnote{Include proper citation of SriMil here} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
+The original model uses foraging to mix the population and create opportunities for interaction, and when certain conditions are met allow resource sharing.
+The model presented achieves this by partially mixing the agents by postulating a static network structure.
+
+The original model drew its inspiration from historical sociology, in Katz's influential study of middle of 19th century Hamilton, Canada~\cite{katz2013people}.
+Retaining this original motivation, we draw additional inspiration from economic sociology, in the work of Granovetter~\cite{granovetter2005}; urban sociology, in the work of Sampson~\cite{sampson2002} and others; and in anthropology, in the work on cooperation in small to medium scale societies~\cite{avner1994,white2011kinship}.
+The geographic and economic scale of the systems, the nature of social actors and time period of interest are all very different from the ones used to develop macroeconomic representative agent models~\cite{benhabib2018}, making the similarity between macroeconomic wealth dynamics models and our models not comparable without further justification.
+Elaborating on the interplay of conceptual and methodological ideas among these disciplines is beyond the scope of this article.
+Instead, we anchor this work on economic sociology and revisit the insights from the above disciplines in the article's concluding section.
+
+The important role played by social structures or non-economic structures in determining economic outcomes of individuals in a society is not in doubt~\cite{granovetter2005,jackson_rev2017}.
+Still, in the absence of a unifying foundation for sociology and economics, the full impact of this two-way interpenetration of economic and social structures is demonstrated only on a case by case basis.
+The language of social and economic networks affords a first principle integration by simplifying the non-trivial concept of social and economic structure~\cite{martin_lee} to only dyadic relations.
+
+As mentioned earlier, macroeconomic models are ill-suited to the study of collective phenomena at intermediate level.
+Hence, alternative explanations of aggregate phenomena that match the expressivity of economic models are required.
+Analytical sociology~\cite{ch1as_hdbk}, with its emphasis of explanation of collective emergent phenomena using mathematically formulated social mechanisms~\cite{ch2as_hdbk,ch11as_hdbk} anchored at the individual level, is an ideal candidate for this purpose.
+
+Models used in scientific inquiry serve a specific purpose.
+In this work, the goal is to construct simple toy models that reproduce non-trivial wealth inequality distributions in the presence and absence of primitive forms of cooperation, clearly delineating the role of network structure in generating wealth inequality.
+We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models with no detailed empirical grounding, but with the potential to generate realistic looking inequality distributions.
+In doing so, we aspire to shed light on the \textit{true} social and economic mechanisms underlying the genesis and persistence of economic inequality.
+
+%Briefly explain the model here and then move on to the next section. .
 
@@
 %While we are interested in more sophisticated models, we are more interested in extracting the effects of social network structure in simple models of cooperative wealth accumulation.
-The proto-institution is definetely borrowed from SriMil.
+The proto-institution is definitely borrowed from SriMil.
 In order to study more elaborate and economically rigorous wealth dynamics, we need to be able sort of the effects of network structure in simple stylized network models.
@@
 Eventually, we plan to get to more realistic wealth accumulation models of interest to economists but for now this is all we have.
-
-\cite{power2018cooperation,power2018}
-
-\cite{koster2019,koster2014,koster2015,bogerhoff2015}
-
-\cite{smith2019,nolin2012}
-
-~\cite{ch1as_hdbk,hedstrom2011oxford,martin_lee}
-
-~\cite{ch2as_hdbk,ch11as_hdbk,granovetter2005,hedstrom2018}
 
@@
 %Katz's chapter 2.
-His main argument there is that the structure of inequality rpresent in Hamilton, Canada is representative of inequality present in all other north american cities of that era.
+His main argument there is that the structure of inequality represent in Hamilton, Canada is representative of inequality present in all other north American cities of that era.
 The persistence of inequality can be see in the persistence of four kinds of social structures.
 1) occupational structure, 2) division of wealth and proportion of the wealthy, 3) social and demographic identity of different economic ranks, and 4) distance between people of different socio-economic ranks or social stratification.
-He talks about peristence of networks of wealth and power.
+He talks about persistence of networks of wealth and power.
 Points out strong interconnection between property, political power and social status.
@@
 %Also, the network model presented here seem to be one of a kind.
-Typicall dynamcics on networks are deterministic in nature.
+Typically dynam ics on networks are deterministic in nature.
 The models discussed here is different from deterministic dynamic processes and epidemic processes, and diffusion type processes (percolation processes).
@@
 %In the model section, we motivate our current specnet model as attempts to capture specific aspects of historical sociology and urban sociology of Katz and Samson respectively.
+
+%Stephen thinks that a subsection of the Model section should be about the
+%simulation code. It won't be long; just enough to explain how the mathematical
+%model just described is represented and executed in Julia, including some
+%answers to non-obvious questions that arise when considering implementation.
 
@@
 
+% I am moving the discussion of connections to anthropology to this section
+
+\cite{power2018cooperation,power2018}
+
+\cite{koster2019,koster2014,koster2015,bogerhoff2015}
+
+\cite{smith2019,nolin2012}
+
 \bibliography{ref_cssa19}

### 2019-06-26 src/net/param_sweep.jl
Allow custom line styles in plots.

@@ -283,11 +283,12 @@ function param_sweeper(graph_name; additional_params...)
 
     CSV.write("$(tempdir())/$(graph_name)_simulation_results.csv",trial_line_df)
 
-    ginip = draw_plot(plot_df, param_to_sweep, Dict("gini"=>"navy"), "Gini")
+    ginip = draw_plot(plot_df, param_to_sweep, Dict("gini"=>"navy"),
+        y_label="Gini")
 
     compp = draw_plot(plot_df, param_to_sweep,
         Dict("number_components"=>"green", "size_largest_component" => "red"),
-        "Components")
+        y_label="Components")
 
     protop = draw_plot(plot_df, param_to_sweep,
         Dict(
@@ -295,14 +296,15 @@ function param_sweeper(graph_name; additional_params...)
             "average_proto_size" => "brown",
             "num_agents_in_proto" => "red",
         ),
-        "Protos",
-        [Guide.annotation(compose(context(), Compose.text(0, params[:N], "N=$(params[:N])", hleft, vtop))),
+        y_label="Protos",
+        extra=[Guide.annotation(compose(context(), Compose.text(0, params[:N], "N=$(params[:N])", hleft, vtop))),
          layer(yintercept=[params[:N]], Geom.hline(style=:dot, color=colorant"navy"))[1]])
 
     numlivingp = draw_plot(plot_df, param_to_sweep,
-        Dict("num_living_agents_pre"=>"green", "num_living_agents_post" => "red"),
-        "Number of living agents",
-        [Guide.annotation(compose(context(), Compose.text(0, params[:N], "N=$(params[:N])", hleft, vtop))),
+        Dict("num_living_agents_pre"=>"green",
+            "num_living_agents_post" => "red"),
+        y_label="Number of living agents",
+        extra=[Guide.annotation(compose(context(), Compose.text(0, params[:N], "N=$(params[:N])", hleft, vtop))),
          Coord.Cartesian(ymin=0, ymax=params[:N]),
          layer(yintercept=[params[:N]], Geom.hline(style=:dot, color=colorant"navy"))[1]])
 
@@ -310,7 +312,7 @@ function param_sweeper(graph_name; additional_params...)
     to_stage_df = plot_df[plot_df[:time_to_stage3] .> 0, :]
     ttsp = draw_plot(to_stage_df, param_to_sweep,
         Dict("time_to_stage2"=>"blue", "time_to_stage3" => "red"),
-        "Time to reach stage")
[…]

### 2019-06-26 src/net/param_sweep.jl
Plot number of protos pre- and post-starvation.

@@ -23,10 +23,11 @@ global social_connectivity_df=DataFrame(
     size_largest_comp=Int[],
     num_comps=Int[],
     average_proto_size=Float64[],
-    num_protos=Int[],
     num_agents_in_proto=Int[],
     num_living_agents_pre=Float64[],
     num_living_agents_post=Float64[],
+    num_protos_pre=Float64[],
+    num_protos_post=Float64[],
     sim_tag=Int[])
 
 
@@ -96,10 +97,11 @@ function param_sweeper(graph_name; additional_params...)
                 (overall_results[:size_largest_comp],
                  overall_results[:num_comps],
                  overall_results[:average_proto_size],
-                 overall_results[:num_protos],
                  overall_results[:num_agents_in_proto],
                  overall_results[:num_living_agents],     # shouldn't be here
                  starvation_results[:num_living_agents],  # shouldn't be here
+                 overall_results[:num_protos],     # shouldn't be here
+                 starvation_results[:num_protos],  # shouldn't be here
 
                  (i*trials_per_value+j)))
 
@@ -154,9 +156,6 @@ function param_sweeper(graph_name; additional_params...)
         average_proto_size=Float64[],
         average_proto_size_lowCI=Float64[],
         average_proto_size_highCI=Float64[],
-        num_protos=Float64[],
-        num_protos_lowCI=Float64[],
-        num_protos_highCI=Float64[],
         num_agents_in_proto=Float64[],
         num_agents_in_proto_lowCI=Float64[],
         num_agents_in_proto_highCI=Float64[],
@@ -166,6 +165,12 @@ function param_sweeper(graph_name; additional_params...)
         num_living_agents_post=Float64[],
         num_living_agents_post_lowCI=Float64[],
         num_living_agents_post_highCI=Float64[],
+        num_protos_pre=Float64[],
+        num_protos_pre_lowCI=Float64[],
+        num_protos_pre_highCI=Float64[],
+        num_protos_post=Float64[],
+        num_protos_post_lowCI=Float64[],
+        num_protos_post_highCI=Float64[],
     )
     names!(plot_df, prepend!(names(plot_df)[2:end], [param_to_sweep]))
 
@@ -184,12 +189,13 @@ function param_sweeper(graph_name; additional_params...)
         curr_sizes = []
         curr_components = []
[…]

### 2019-06-26 src/net/sim.jl
Properly, permanently detect end of stage 1.

@@ -621,10 +621,13 @@ end
 #   S1: No agent has yet created a proto.
 #   S2: Agents are creating and joining protos.
 #   S3: All agents are either (a) graph isolates, (b) dead, or (c) in a proto.
+global left_stage_1 = false
 function get_stage(sim_state::SimState)
-    if length(sim_state.arr_protos) == 1   # See arr_protos hack
+    if length(sim_state.arr_protos) == 1  &&  # See arr_protos hack
+            !left_stage_1
         return 1
     else
+        global left_stage_1 = true
         for agent in keys(AN)
             if length(neighbors(graph,AN[agent])) > 0  &&
                     agent.a.alive  &&

### 2019-06-26 src/net/sim.jl
Plot num living agents & protos on same plot.

@@ -127,6 +127,7 @@ function specnet(;additional_params...)
     local ginis=Array{Float16}(undef,params[:max_iters],3)
     local stages=[]
     local nums_agents=[]
+    local nums_protos=[]
 
     global overall_results
     for iter in 1:params[:max_iters]
@@ -158,6 +159,7 @@ function specnet(;additional_params...)
         end
 
         push!(nums_agents, length([ a for a ∈  keys(AN) if a.a.alive ]))
+        push!(nums_protos, length(arr_protos))
 
         if params[:make_anims]
             if locs_x == nothing
@@ -296,7 +298,8 @@ function specnet(;additional_params...)
         gini = ginis[1:length(stages),1],
         gini_highCI = ginis[1:length(stages),3],
         stage = stages,
-        num_agents = nums_agents
+        num_agents = nums_agents,
+        num_protos = nums_protos,
     )
 
     # Collect stats on the model after the starvation period.
@@ -478,7 +481,7 @@ function plot_final_wealth_hist(sim_state::SimState)
         Guide.ylabel("Density of protos"))
     draw(PNG("$(tempdir())/final_agent_wealth_histogram.png"),final_wealthp)
     draw(PNG("$(tempdir())/final_proto_wealth_histogram_alive.png"),final_proto_wealth_alivep)
-    draw(PNG("$(tempdir())/final_proto_wealth_histogram.png"),final_proto_wealthp)
+    #draw(PNG("$(tempdir())/final_proto_wealth_histogram.png"),final_proto_wealthp)
 
 end
 
@@ -496,6 +499,8 @@ function plot_gini_livingfrac_over_time(iter_results, callouts)
     stage_names = Dict(1=>"1", 2=>"2", 3=>"3")
     iter_results.stage = [ stage_names[s] for s in iter_results.stage ]
     iter_results.num_agents /= maximum(iter_results.num_agents)
+    iter_results.num_protos /= maximum(iter_results.num_protos)
+
     giniPlot=plot(iter_results,
         layer(
             x=:iter, y=:gini_lowCI,
@@ -517,17 +522,36 @@ function plot_gini_livingfrac_over_time(iter_results, callouts)
             Geom.ribbon,
             Theme(default_color=colorant"lightblue")
         ),
-        layer(
-            x=:iter, y=:num_agents,
-            Geom.line,
-            Theme(default_color=colorant"black")
-        ),
[…]

### 2019-06-26 src/net/param_sweep.jl
(Keep "N=n" annotation on plot.)

@@ -323,7 +323,7 @@ function param_sweeper(graph_name; additional_params...)
             "num_protos_pre" => :dot,
             "num_protos_post" => :dot),
         y_label="Number of living agents/protos",
-        extra=[Guide.annotation(compose(context(), Compose.text(0, params[:N], "N=$(params[:N])", hleft, vtop))),
+        extra=[Guide.annotation(compose(context(), Compose.text(minimum(plot_df[param_to_sweep]), params[:N], "N=$(params[:N])", hleft, vtop))),
          Coord.Cartesian(ymin=0, ymax=params[:N]),
          layer(yintercept=[params[:N]], Geom.hline(style=:dot, color=colorant"navy"))[1]])
 

### 2019-06-26 src/net/param_sweep.jl
(Turn legends back on for param sweep plots.)

@@ -316,8 +316,8 @@ function param_sweeper(graph_name; additional_params...)
     numlivingp = draw_plot(plot_df, param_to_sweep,
         Dict("num_living_agents_pre" => "green",
             "num_living_agents_post" => "red",
-            "num_protos_pre" => "green",
-            "num_protos_post" => "red"),
+            "num_protos_pre" => "blue",
+            "num_protos_post" => "orange"),
         Dict("num_living_agents_pre"=> :solid,
             "num_living_agents_post" => :solid,
             "num_protos_pre" => :dot,
@@ -414,9 +414,9 @@ function draw_plot(plot_df, param_to_sweep, vars_colors=Dict{String,String},
     if length(vars_colors) > 1
         vars = collect(keys(vars_colors))
         vars[1:end-1] = [ v*"   ." for v in vars[1:end-1] ]
-# TODO: add legend that combines both color and linestyle, where appropriate.
-#        push!(p, Guide.manual_color_key(nothing,
-#            vars, collect(values(vars_colors))))
+        # TODO: add legend that combines both color and linestyle, where appropriate.
+        push!(p, Guide.manual_color_key(nothing,
+            vars, collect(values(vars_colors))))
     end
     [ push!(p, e) for e in extra ]
 
@@ -426,9 +426,12 @@ end
 lighter_shade_of = Dict(
     "navy" => "lightblue",
     "blue" => "lightblue",
+    "orange" => "pink",
     "red" => "pink",
     "green" => "lightgreen",
     "brown" => "orange",
+    "black" => "grey",
+    "grey" => "lightgrey",
 )
 
 # Keep only columns we will use for this plot, and remove rows with missing

### 2019-06-26 src/net/param_sweep.jl
Sort legend labels more sensibly.

@@ -412,11 +412,11 @@ function draw_plot(plot_df, param_to_sweep, vars_colors=Dict{String,String},
         style(background_color=colorant"white",key_position=:bottom)
     )
     if length(vars_colors) > 1
-        vars = collect(keys(vars_colors))
+        vars = sort(collect(keys(vars_colors)))
+        colors = [ vars_colors[x] for x in vars ]
         vars[1:end-1] = [ v*"   ." for v in vars[1:end-1] ]
         # TODO: add legend that combines both color and linestyle, where appropriate.
-        push!(p, Guide.manual_color_key(nothing,
-            vars, collect(values(vars_colors))))
+        push!(p, Guide.manual_color_key(nothing, vars, colors))
     end
     [ push!(p, e) for e in extra ]
 

### 2019-06-26 src/net/sim.jl
NAN error when length(arr_protos)=0

@@ -94,7 +94,7 @@ function specnet(;additional_params...)
             =>k for k in 1:params[:N])
 
     ## the following is a hack; see comment in ../scape/run-simulation.jl
-    arr_protos = [Proto(-1, -1, false, ["-"], [Transaction(-1, -1, "", "-")])]
+    arr_protos = []
 
 
     # (Erase old images.)
@@ -666,7 +666,11 @@ end
 function collect_stats(s::SimState)
     total_proto_sz = sum([ length(p.arr_member_ids) for p ∈  s.arr_protos ])
     component_vertices = connected_components(s.graph)
-    proto_average_size=total_proto_sz/length(s.arr_protos)
+    if length(s.arr_protos) ==0
+	    proto_average_size=0
+    else
+	    proto_average_size=total_proto_sz/length(s.arr_protos)
+	end
     num_agents_in_proto = sum([ ag.a.proto_id ≠ -1 for ag ∈  keys(AN) ])
     return Dict(:size_largest_comp => nv(s.graph) == 0 ? 0 :
             findmax(length.(component_vertices))[1][1],

### 2019-06-26 manuscript/draftcssa19.tex
SD's review of RV's section 1 draft.

@@
 While economic and political inequality used to be discussed in not so mainstream heterodox economics circles, the contentious discussions on the topic within mainstream economics since the publication of Piketty's book~\cite{piketty2017capital} suggests a lack of consensus about very basic foundational questions like the origins and persistence of economic inequality.
-Not surprisingly, traditional theories and tools of macro and micro economics are now being diagnosed for its limitations.
-Simultaneously, insights from related disciplines along with novel scientific inquiry models not usually associated with traditional econometrics are being taken more seriously.
+Not surprisingly, traditional theories and tools of macro and micro economics are now being diagnosed for their limitations.
+Simultaneously, insights from related disciplines, along with novel scientific inquiry models not usually associated with traditional econometrics, are being taken more seriously.
 The work presented here shares this spirit by integrating substantive ideas from anthropology, economic sociology~\cite{granovetter2017society} and urban sociology~\cite{sampson2012great} and using modeling approaches from computational social science~\cite{hedstrom2018} and analytical sociology~\cite{hedstrom2011oxford} to understand the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
+% SD: citation for "anthropology," the first element of the last sentence's list? Grief and/or White?
 
 The current work originated in our attempts to incorporate and tease out the effects of social structures in simple models of wealth dynamics in the presence of environmental stochasticity, and a simple form of resource pooling.
-These models were inspired by our search for analogs of grid world agent based models of Srikanth and Milton \footnote{Include proper citation of SriMil here} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
-The original model uses foraging to mix the population and create opportunities for interaction, and when certain conditions are met allow resource sharing.
-The model presented achieves this by partially mixing the agents by postulating a static network structure.
+These models were inspired by our search for analogs of the grid world agent-based models (ABMs) of Friesen and Mudigonda \footnote{Include proper citation of SriMil here} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
+The original model used foraging to mix the population and create opportunities for interaction, and, when certain conditions were met, allowed resource sharing.
+Our model achieves agent interaction by postulating a static network structure which partially mixes the agents.
 
@@
 Elaborating on the interplay of conceptual and methodological ideas among these disciplines is beyond the scope of this article.
-Instead, we anchor this work on economic sociology and revisit the insights from the above disciplines in the article's concluding section.
+Instead, we anchor this work in economic sociology and revisit the insights from the above disciplines in the article's concluding section.
 
 The important role played by social structures or non-economic structures in determining economic outcomes of individuals in a society is not in doubt~\cite{granovetter2005,jackson_rev2017}.
-Still, in the absence of a unifying foundation for sociology and economics, the full impact of this two-way interpenetration of economic and social structures is demonstrated only on a case by case basis.
+Still, in the absence of a unifying foundation for sociology and economics, the full impact of this two-way interpenetration of economic and social structures is demonstrated only on a case-by-case basis.
 The language of social and economic networks affords a first principle integration by simplifying the non-trivial concept of social and economic structure~\cite{martin_lee} to only dyadic relations.
 
-As mentioned earlier, macroeconomic models are ill-suited to the study of collective phenomena at intermediate level.
-Hence, alternative explanations of aggregate phenomena that match the expressivity of economic models are required.
-Analytical sociology~\cite{ch1as_hdbk}, with its emphasis of explanation of collective emergent phenomena using mathematically formulated social mechanisms~\cite{ch2as_hdbk,ch11as_hdbk} anchored at the individual level, is an ideal candidate for this purpose.
+As mentioned earlier, macroeconomic models are ill-suited to the study of collective phenomena at an intermediate level.
+Hence, alternative explanations of aggregate phenomena that match the expressiveness of economic models are required.
+Analytical sociology~\cite{ch1as_hdbk}, with its emphasis on explanation of collective emergent phenomena using mathematically formulated social mechanisms~\cite{ch2as_hdbk,ch11as_hdbk} anchored at the individual level, is an ideal candidate for this purpose.
 
@@
 In this work, the goal is to construct simple toy models that reproduce non-trivial wealth inequality distributions in the presence and absence of primitive forms of cooperation, clearly delineating the role of network structure in generating wealth inequality.
-We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models with no detailed empirical grounding, but with the potential to generate realistic looking inequality distributions.
+We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models, with no detailed empirical grounding, but with the potential to generate realistic looking inequality distributions.
 In doing so, we aspire to shed light on the \textit{true} social and economic mechanisms underlying the genesis and persistence of economic inequality.

### 2019-06-27 manuscript/draftcssa19.tex
section 1 completed

@@
 The current work originated in our attempts to incorporate and tease out the effects of social structures in simple models of wealth dynamics in the presence of environmental stochasticity, and a simple form of resource pooling.
-These models were inspired by our search for analogs of the grid world agent-based models (ABMs) of Friesen and Mudigonda \footnote{Include proper citation of SriMil here} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
+These models were inspired by our search for analogs of the grid world agent-based models (ABMs) of Friesen and Mudigonda~\cite{srimil} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
 The original model used foraging to mix the population and create opportunities for interaction, and, when certain conditions were met, allowed resource sharing.
@@
 
-Models used in scientific inquiry serve a specific purpose.
-In this work, the goal is to construct simple toy models that reproduce non-trivial wealth inequality distributions in the presence and absence of primitive forms of cooperation, clearly delineating the role of network structure in generating wealth inequality.
+Models constructed here, like those used in scientific inquiry in general, serve a specific purpose.
+In this work, we construct simple toy models to reproduce certain aspects of non-trivial wealth inequality distributions in the presence and absence of primitive forms of cooperation, clearly delineating the role of network structure in generating wealth inequality.
 We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models, with no detailed empirical grounding, but with the potential to generate realistic looking inequality distributions.
@@
 
-%Briefly explain the model here and then move on to the next section. .
+%What is the scientific question of interest to us? 
+%How features of models of structure and dyanmics intera
 
-%The current plan is start with economics economic sociology and wealth dynamic models.
-The former is discussed in Jackson's review, the latter in rvenkat's CSSA18 paper.
-Then we move on to how wealth dynamics and inequality questions matter also to other fields like anthropology and sociology.
-Wealh dynamics in such situations can also be addressed using economic models and is the focus of our manuscript.
+The phenomenon under scrutiny is the emergence and evolution of economic inequality in societies with non-trivial social structures.
+The model we use to answer questions surrounding this phenomena must possess a dynamic model of wealth accumulation, a model of social structure; and a suitably useful measure of inequality.
+The dynamics are modeled as Brownian noise driven linear dynamical systems, here constant growth rate; the structure is modeled by networks, here random graphs; the measure of inequality used is Gini coefficients.
+Although both the dynamical system and the network model are quiet well understood, the precise interplay of structure and dynamics produces interesting emergent wealth distributions.
+To the best of our knowledge, this specific combination of network structure and social dynamics has not been discussed in the computational social science or mathematical sociology literature and consider this the primary contribution of this work.
+
+Apart from enabling interactions between social actors, social structures like institutions also shape the form of cooperation and coordination mechanisms.
+The institutions can take the form of economic institutions, like banks and cooperatives; or the form of norms, like resource sharing practices in societies.
+The original SriMil model~\cite{srimil}consists of simple resource pooling arrangement where aggregates of agents pool their excess wealth in a common institution called protoinstitutions, agreeing to provide this saved resource to individual agents in times of need.
+The model of resource pooling used in this work is identical to the SriMil model.
+
+While the analysis to be presented in later sections focus only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-Renyi network models, space constraints prevent us from repeating the analysis on other standard \textit{textbook} networks like scale free and small world networks.
+We also address more empirically grounded models in the concluding section of this paper.
+
+In the next section, we discuss the mathematical formulation of the model.
+In section 3, we present the analysis of our simulation experiments, summarize key findings and discuss why we chose \texttt{julia} programming language~\cite{Julia-2017} for our implementation.
+In section 4, we discuss the limitations of our simple models, extensions to dynamics and networks more expressive than the ones presented here, and planned future work.
 
@@
 \section{Model}
-~\cite{redner2001guide}
+~\cite{redner2001guide} ~\cite{rv}
 %Use chapter 3 of redner's book here. 

### 2019-06-27 manuscript/draftcssa19.tex
Reword macroeconomics models.

--- 2019-06-26 manuscript/draftcssa19.tex
@@
 Retaining this original motivation, we draw additional inspiration from economic sociology, in the work of Granovetter~\cite{granovetter2005}; urban sociology, in the work of Sampson~\cite{sampson2002} and others; and in anthropology, in the work on cooperation in small to medium scale societies~\cite{avner1994,white2011kinship}.
-The geographic and economic scale of the systems, the nature of social actors and time period of interest are all very different from the ones used to develop macroeconomic representative agent models~\cite{benhabib2018}, making the similarity between macroeconomic wealth dynamics models and our models not comparable without further justification.
+The geographic and economic scale of the systems, the nature of social actors and time period of interest are all very different from the ones used to develop models of representative agents in macroeconomics~\cite{benhabib2018}, making the similarity between macroeconomic wealth dynamics models and our models not comparable without further justification.
 Elaborating on the interplay of conceptual and methodological ideas among these disciplines is beyond the scope of this article.

### 2019-06-27 src/net/param_sweep.jl
Add "critical" print level.

@@ -36,8 +36,8 @@ function param_sweeper(graph_name; additional_params...)
     @assert all_parameters_legit(additional_params)
     merge!(params, Dict(additional_params))
 
-    println("Starting sweep..")
-    print("Sweeping for: $(param_to_sweep)")
+    prc("Starting sweep...\n")
+    prc("Sweeping for: $(param_to_sweep)")
     counter=start_value
 
     global agent_line_df = DataFrame(
@@ -373,7 +373,7 @@ function draw_plot(plot_df, param_to_sweep, vars_colors=Dict{String,String},
         vars_linestyles=Dict{String,Symbol}();
         y_label=nothing, extra=[], plot_CIs=true)
 
-    prd("Drawing: $(vars_colors)")
+    prd("Drawing: $(vars_colors)\n")
     plot_df = consolidate(plot_df, param_to_sweep, vars_colors, plot_CIs)
     layers = Layer[]
     for (var, color) in vars_colors
@@ -459,7 +459,7 @@ end
 if graph_sweep
     sweep_results = Dict()
     graph_types=["erdos_renyi","scale_free","small_world","complete","empty"]
-    println("sweeping for graph type")
+    prc("sweeping for graph type")
     for graph_type in graph_types
         params[:whichGraph]=graph_type
         sweep_results[graph_type] = param_sweeper(graph_type)

### 2019-06-27 src/net/sim.jl

@@ -32,9 +32,9 @@ function specnet(;additional_params...)
     @assert all_parameters_legit(additional_params)
     merge!(params, Dict(additional_params))
 
-    pri("SPECnet simulation parameters:")
+    pri("SPECnet simulation parameters:\n")
     for param in sort(collect(keys(params)), by=x->lowercase(string(x)))
-        pri("   $(param) = $(params[param])")
+        pri("   $(param) = $(params[param])\n")
     end
 
     global locs_x, locs_y
@@ -73,7 +73,7 @@ function specnet(;additional_params...)
     # them ruthlessly in sync.)
 
 
-    println("Run SPECnet...")
+    pri("Run SPECnet...\n")
 
 
     # The initial social network.
@@ -111,7 +111,7 @@ function specnet(;additional_params...)
     locs_x, locs_y = nothing, nothing
 
 
-    println("Iterations:")
+    pri("Iterations:\n")
 
 
     # The number of stage 3 iterations run so far.
@@ -137,13 +137,13 @@ function specnet(;additional_params...)
         push!(stages, get_stage(SimState(graph, AN, arr_protos)))
         @assert stages[end] ∈  [1,2,3]
         if stages[end] == 1
-            print("-")
+            pri("-")
         elseif stages[end] == 2
-            print("+")
+            pri("+")
         elseif stages[end] == 3
-            print("#")
+            pri("#")
         end
-        if iter % 10 == 0 println(iter) end
+        if iter % 10 == 0 pri(iter) end
 
         if stages[end] == 3
             if starvation_timer == 0
@@ -220,12 +220,12 @@ function specnet(;additional_params...)
                 if dying_agent.a.proto_id == -1
                     prd("Agent $(dying_agent) died!! " *
                         "(needed $(-dying_agent.a.sugar_level), " *
-                        "and had no proto).")
+                        "and had no proto).\n")
                     kill_agent(dying_agent)
                 elseif dying_agent.a.proto_id == -2
                     prd("Agent $(dying_agent) died!! " *
                         "(needed $(-dying_agent.a.sugar_level), " *
-                        "but proto has already been exhausted. (1)")
+                        "but proto has already been exhausted. (1)\n")
                     kill_agent(dying_agent)
                 else
                     in_the_hole = dying_agent.a.sugar_level
@@ -234,20 +234,20 @@ function specnet(;additional_params...)
                         "(had $(in_the_hole), " *
                         "now has $(dying_agent.a.sugar_level), " *
[…]

### 2019-06-27 src/net/perf_comp.jl
Add perf_comp.jl (perform comparison).

@@ -1,0 +1,129 @@
+#!/usr/bin/env julia
+# perf_comp.jl (perform comparison)
+# Unlike param_sweep.jl, which sweeps through a range of parameter values, this
+#  script runs the sim multiple times for a small set of different settings, and
+#  produces comparison statistics and plots.
+
+using Revise
+using RCall
+@rlibrary DescTools
+using DataFrames
+using CSV
+using Bootstrap
+include("sim.jl")
+include("setup_params.jl")
+
+
+num_trials=40
+original_seed=params[:random_seed]
+
+settings_sets = [
+    Dict(:label => "empty", :whichGraph => "empty"),
+    Dict(:label => "λ=0", :whichGraph => "erdos_renyi", :λ => 0.0),
+#   Dict(:label => "λ=¼", :whichGraph => "erdos_renyi", :λ => 0.25),
+    Dict(:label => "λ=½", :whichGraph => "erdos_renyi", :λ => 0.5),
+#   Dict(:label => "λ=¾", :whichGraph => "erdos_renyi", :λ => 0.75),
+    Dict(:label => "λ=1", :whichGraph => "erdos_renyi", :λ => 1.0),
+#   Dict(:label => "λ=1¼", :whichGraph => "erdos_renyi", :λ => 1.25),
+    Dict(:label => "λ=1½", :whichGraph => "erdos_renyi", :λ => 1.5),
+#   Dict(:label => "λ=1¾", :whichGraph => "erdos_renyi", :λ => 1.75),
+    Dict(:label => "λ=2", :whichGraph => "erdos_renyi", :λ => 2.0),
+    Dict(:label => "λ=3", :whichGraph => "erdos_renyi", :λ => 3.0),
+    Dict(:label => "λ=4", :whichGraph => "erdos_renyi", :λ => 4.0),
+    Dict(:label => "λ=5", :whichGraph => "erdos_renyi", :λ => 5.0),
+    Dict(:label => "λ=6", :whichGraph => "erdos_renyi", :λ => 6.0),
+    Dict(:label => "complete", :whichGraph => "complete"),
+]
+
+function perform_comparison(settings_sets)
+
+    prc("Starting comparison...\n")
+
+    trials_df = DataFrame(
+        label=String[],
+        seed=Int[],
+        gini_pre=Float64[],
+        gini_post=Float64[],
+        num_comps=Float64[],
+        avg_proto_size_pre=Float64[],
+        avg_proto_size_post=Float64[],
[…]

### 2019-06-27 src/net/sim.jl

@@ -674,6 +674,8 @@ function collect_stats(s::SimState)
     num_agents_in_proto = sum([ ag.a.proto_id ≠ -1 for ag ∈  keys(AN) ])
     return Dict(:size_largest_comp => nv(s.graph) == 0 ? 0 :
             findmax(length.(component_vertices))[1][1],
+        :gini => Gini([ ag.a.sugar_level
+                            for ag ∈  keys(AN) if ag.a.sugar_level ≥ 0 ]),
         :num_comps => nv(s.graph) == 0 ? 0 :
             length(component_vertices),
         :average_proto_size => proto_average_size,
@@ -684,7 +686,8 @@ function collect_stats(s::SimState)
 end
 
 function all_parameters_legit(additional_params)
-    if !all([ word in keys(params) for word in keys(additional_params) ])
+    if !all([ word in union([:label], keys(params))
+                                        for word in keys(additional_params) ])
         for word in keys(additional_params)
             if word ∉  keys(params)
                 prc("No such SPECnet parameter \"$(word)\".\n")

### 2019-06-28 manuscript/analysis.tex
Break out analysis section to separate file.

% (Separate analysis.tex file, so all images are in a separate file.)

\subsection{None-to-None Network}

\subsection{All-to-All Network}

\subsection{Erd\H{o}s-R\'{e}nyi Model}

\subsection{Integrating our findings from the previous subsections}

### 2019-06-28 manuscript/draftcssa19.tex
Break out analysis section to separate file.

@@
 
-While the analysis to be presented in later sections focus only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-Renyi network models, space constraints prevent us from repeating the analysis on other standard \textit{textbook} networks like scale free and small world networks.
+While the analysis to be presented in later sections focus only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-R\'{e}nyi network models, space constraints prevent us from repeating the analysis on other standard \textit{textbook} networks like scale free and small world networks.
 We also address more empirically grounded models in the concluding section of this paper.
@@
 \section{Analysis}
+\include{analysis}
 

### 2019-06-28 src/net/sim.jl
Make ER param calculation slightly more precise.

@@ -421,7 +421,7 @@ end
 
 function choose_graph()
     if params[:whichGraph]=="erdos_renyi"
-        ER_prob=params[:λ]/params[:N]
+        ER_prob=params[:λ]/(params[:N]-1)
         graph = LightGraphs.SimpleGraphs.erdos_renyi(
             params[:N], ER_prob)
 

### 2019-06-28 src/net/sim.jl
Fix a few plotting bugs in edge cases.

@@ -267,9 +267,15 @@ function specnet(;additional_params...)
                             for ag in keys(AN) if ag.a.sugar_level ≥ 0 ]
         if params[:make_sim_plots]
             if length(wealthArray) > 1
-                rGini=Gini(wealthArray; Symbol("conf.level")=>.95,
-                    :R=>params[:num_boot_samples])
-                ginis[iter,:] = [ convert(Float16,r) for r in rGini ]
+                if all_the_same(wealthArray)
+                    # All wealths are the same. In this case, the Gini
+                    #   coefficient itself is 0, and a CI cannot be calculated.
+                    ginis[iter,:] = [ 0.0, 0.0, 0.0 ]
+                else
+                    rGini=Gini(wealthArray; Symbol("conf.level")=>.95,
+                        :R=>params[:num_boot_samples])
+                    ginis[iter,:] = [ convert(Float16,r) for r in rGini ]
+                end
             else
                 ginis[iter,:] = [ NaN, NaN, NaN ]
             end
@@ -481,7 +487,7 @@ function plot_final_wealth_hist(sim_state::SimState)
         Guide.ylabel("Density of protos"))
     draw(PNG("$(tempdir())/final_agent_wealth_histogram.png"),final_wealthp)
     draw(PNG("$(tempdir())/final_proto_wealth_histogram_alive.png"),final_proto_wealth_alivep)
-    #draw(PNG("$(tempdir())/final_proto_wealth_histogram.png"),final_proto_wealthp)
+    draw(PNG("$(tempdir())/final_proto_wealth_histogram.png"),final_proto_wealthp)
 
 end
 
@@ -582,34 +588,39 @@ function plot_iteration_graphs(iter)
         graphp)
 
     # Plot wealth histogram for this iteration.
-    in_proto_wealths=[]
-    not_in_proto_wealths=[]
+    in_proto_wealths=Float64[]
+    not_in_proto_wealths=Float64[]
     [  in_proto(ag) ?
             push!(in_proto_wealths,ag.a.sugar_level) :
             push!(not_in_proto_wealths,ag.a.sugar_level)
         for ag in keys(AN) ]
 
-    wealthp = plot(
-        layer(x=in_proto_wealths,
+    wealthp_layers = Layer[]
+    if length(in_proto_wealths) > 1
+        push!(wealthp_layers, layer(x=in_proto_wealths,
             Geom.histogram(density=true, bincount=20),
[…]

### 2019-06-28 src/net/param_sweep.jl
Deletion of proto member_ids. Proto plot reimplemented

@@ -9,12 +9,12 @@ include("sim.jl")
 include("setup_params.jl")
 
 
-param_to_sweep=:salary   #parameter to iterate over *any parameter*
+param_to_sweep=:λ   #parameter to iterate over *any parameter*
                      #for graph sweep param_to_sweep should not be exclusive to one graph type e.g. SF_prob
-start_value=10      #value to begin sweep
-end_value=200         #value to end sweep
-num_values=50        #number of distinct values to run
-trials_per_value=4   #for each distinct value, number of independent sims to run
+start_value=0.0     #value to begin sweep
+end_value=6         #value to end sweep
+num_values=30        #number of distinct values to run
+trials_per_value=14   #for each distinct value, number of independent sims to run
 graph_sweep=false    #run the sweep once for each graph type
 original_seed=params[:random_seed]
 
@@ -22,7 +22,8 @@ components=[[],[]]
 global social_connectivity_df=DataFrame(
     size_largest_comp=Int[],
     num_comps=Int[],
-    average_proto_size=Float64[],
+    average_proto_size_pre=Float64[],
+	average_proto_size_post=Float64[],
     num_agents_in_proto=Int[],
     num_living_agents_pre=Float64[],
     num_living_agents_post=Float64[],
@@ -97,6 +98,7 @@ function param_sweeper(graph_name; additional_params...)
                 (overall_results[:size_largest_comp],
                  overall_results[:num_comps],
                  overall_results[:average_proto_size],
+				 starvation_results[:average_proto_size],
                  overall_results[:num_agents_in_proto],
                  overall_results[:num_living_agents],     # shouldn't be here
                  starvation_results[:num_living_agents],  # shouldn't be here
@@ -153,9 +155,12 @@ function param_sweeper(graph_name; additional_params...)
         time_to_stage3=Float64[],
         time_to_stage3_lowCI=Float64[],
         time_to_stage3_highCI=Float64[],
-        average_proto_size=Float64[],
-        average_proto_size_lowCI=Float64[],
-        average_proto_size_highCI=Float64[],
+        average_proto_size_pre=Float64[],
+        average_proto_size_pre_lowCI=Float64[],
+        average_proto_size_pre_highCI=Float64[],
[…]

### 2019-06-28 src/net/setup_params.jl

@@ -5,7 +5,7 @@ params = Dict{Symbol,Any}(
     :max_iters => 50,               # maximum number of iterations the simulation
                                     #   runs before termination (will terminate
                                     #   earlier if stopping condition reached)
-    :starvation_period => 10,       # the number of iterations to starve all agents
+    :starvation_period => 20,       # the number of iterations to starve all agents
                                     #   after the simulation has reached stage 3
                                     #   (all live non-isolate agents in protos)
     :openness => float(0.0),        # 0 <=> openness <=> 1
@@ -15,13 +15,13 @@ params = Dict{Symbol,Any}(
                                     #   ~U(1, init_sg_lvl)
     :metabolic_rate => 5,           # each iteration, each agent consumes exactly
                                     #   this much sugar
-    :salary => 10,                   # each iteration, each agent receives exactly
+    :salary => 20,                   # each iteration, each agent receives exactly
                                     #   this much sugar
     :white_noise_intensity =>       # each iteration, an agent receives (or loses)
         float(1.0),                 #   ~N(0, white_noise_intensity) extra sugar
     :proto_threshold => 50,         # each agent in an encounter must have
                                     #   > wealth than this to form a proto
-    :make_anims => false,           # create animations of results?
+    :make_anims => true,           # create animations of results?
     :make_sim_plots => true,        # create plots (for individual simulations)?
     :num_boot_samples => 1000,      # for single sims, the number of bootstrap
                                     #   samples used in computing CI for single
@@ -39,7 +39,7 @@ params = Dict{Symbol,Any}(
                                     #   - "complete"
                                     #   - "empty"
 
-    :λ => float(1),                 # ER: expected number if edges per node
+    :λ => float(2),                 # ER: expected number if edges per node
 
     :SF_edges => 40,                # SF: number of edges
     :SF_degree => 2,                # SF: exponent of expected power law degree

### 2019-06-28 src/net/sim.jl

@@ -27,6 +27,7 @@ end
 #     specnet()
 #     specnet(max_iters=20)
 #     specnet(max_iters=20, N=100)
+    ## the following is a hack; see comment in ../scape/run-simulation.jl
 function specnet(;additional_params...)
 
     @assert all_parameters_legit(additional_params)
@@ -93,8 +94,7 @@ function specnet(;additional_params...)
 
             =>k for k in 1:params[:N])
 
-    ## the following is a hack; see comment in ../scape/run-simulation.jl
-    arr_protos = []
+
 
 
     # (Erase old images.)
@@ -110,6 +110,7 @@ function specnet(;additional_params...)
 
     locs_x, locs_y = nothing, nothing
 
+    arr_protos = []
 
     println("Iterations:")
 
@@ -255,7 +256,7 @@ function specnet(;additional_params...)
         end
 
 
-        kill_sugarless_protos(SimState(graph, AN, arr_protos), arr_dead_protos)
+        arr_protos=kill_sugarless_protos(SimState(graph, AN, arr_protos), arr_dead_protos)
 
         # The R function Gini() from DescTools returns a vector of three values
         #   if conf.level is not NA: (1) the estimate, (2) the lower bound of
@@ -337,24 +338,25 @@ end
 #   arr_dead_protos variable and setting all its members back to a -1 ("no
 #   proto") proto_id.
 function kill_sugarless_protos(sim_state::SimState, arr_dead_protos)
-    index=length(sim_state.arr_protos)
-    while index>0
+    index=length(sim_state.arr_protos) 
+	while index>0
+	               
         if(sim_state.arr_protos[index].proto_id ≠ -1 &&
-                sim_state.arr_protos[index].balance<=0)
-            prd("Killing proto $(sim_state.arr_protos[index].proto_id)")
-            for id in sim_state.arr_protos[index].arr_member_ids
-                for ag in keys(AN)
-                    if ag.a.agent_id==id
-                        ag.a.proto_id=-2    # new value, indicating "was once
-                                            #   in a proto, but no longer."
-                    end
-                end
-            end
+            sim_state.arr_protos[index].balance==0.0)
+            println("Killing proto $(sim_state.arr_protos[index].proto_id)")
+			for ag in keys(AN) 
+			    if ag.a.proto_id == sim_state.arr_protos[index].proto_id
[…]

### 2019-07-02 src/net/param_sweep.jl
Remove graph name from plot filenames.
Move println->prd.

@@ -32,7 +32,7 @@ global social_connectivity_df=DataFrame(
     sim_tag=Int[])
 
 
-function param_sweeper(graph_name; additional_params...)
+function param_sweeper(; additional_params...)
 
     @assert all_parameters_legit(additional_params)
     merge!(params, Dict(additional_params))
@@ -121,16 +121,16 @@ function param_sweeper(graph_name; additional_params...)
         counter += (end_value-start_value)/num_values
     end
     sim_tag=0
-    rm("$(tempdir())/$(graph_name)_agent_results.csv", force=true)
-    rm("$(tempdir())/$(graph_name)_simulation_results.csv", force=true)
-    rm("$(tempdir())/$(graph_name)GiniSweepPlot.png", force=true)
-    rm("$(tempdir())/$(graph_name)_wealth_heatmap.png", force=true)
-    rm("$(tempdir())/$(graph_name)Component_GiniSweepPlots.png", force=true)
-    rm("$(tempdir())/$(graph_name)ComponentSweepPlot.png", force=true)
-    rm("$(tempdir())/$(graph_name)ProtoPropertiesSweep.png", force=true)
+    rm("$(tempdir())/agent_results.csv", force=true)
+    rm("$(tempdir())/simulation_results.csv", force=true)
+    rm("$(tempdir())/GiniSweepPlot.png", force=true)
+    rm("$(tempdir())/wealth_heatmap.png", force=true)
+    rm("$(tempdir())/Component_GiniSweepPlots.png", force=true)
+    rm("$(tempdir())/ComponentSweepPlot.png", force=true)
+    rm("$(tempdir())/ProtoPropertiesSweep.png", force=true)
 
     #this file contains all info with one line per agent in a given run of siml.jl
-    CSV.write("$(tempdir())/$(graph_name)_agent_results.csv",agent_line_df)
+    CSV.write("$(tempdir())/agent_results.csv",agent_line_df)
 
 
     #once the main dataframe is made, plots may be drawn with data from agent_line_df
@@ -313,7 +313,7 @@ function param_sweeper(graph_name; additional_params...)
     #this file contains (currently) only the resulting Gini index from each simulation
     trial_line_df=join(trial_line_df, social_connectivity_df, on = :sim_tag)
 
-    CSV.write("$(tempdir())/$(graph_name)_simulation_results.csv",trial_line_df)
+    CSV.write("$(tempdir())/simulation_results.csv",trial_line_df)
 
[…]

### 2019-07-02 src/net/sim.jl

@@ -350,7 +350,7 @@ function kill_sugarless_protos(sim_state::SimState, arr_dead_protos)
         if(sim_state.arr_protos[index].proto_id ≠ -1 &&
 
             sim_state.arr_protos[index].balance==0.0)
-            println("Killing proto $(sim_state.arr_protos[index].proto_id)")
+            prd("Killing proto $(sim_state.arr_protos[index].proto_id)")
 			for ag in keys(AN) 
 			    if ag.a.proto_id == sim_state.arr_protos[index].proto_id
 				    ag.a.proto_id=-2                     # new value, indicating "was once
@@ -359,7 +359,7 @@ function kill_sugarless_protos(sim_state::SimState, arr_dead_protos)
 			end
 
             push!(arr_dead_protos,sim_state.arr_protos[index])
-            println("proto deleted")
+            prd("proto deleted")
 			deleteat!(sim_state.arr_protos,index)
         end
         index-=1

### 2019-07-02 src/net/sim.jl
Collect life history.

@@ -94,8 +94,11 @@ function specnet(;additional_params...)
 
             =>k for k in 1:params[:N])
 
-
-
+    life_history = DataFrame(
+        iter = Int[],
+        agent = String[],
+        sugar = Float16[]
+    )
 
     # (Erase old images.)
     save_dir = pwd()
@@ -161,6 +164,9 @@ function specnet(;additional_params...)
 
         push!(nums_agents, length([ a for a ∈  keys(AN) if a.a.alive ]))
         push!(nums_protos, length(arr_protos))
+        for ag ∈  keys(AN)   # if a.a.alive ?
+            push!(life_history, (iter, ag.a.agent_id, ag.a.sugar_level))
+        end
 
         if params[:make_anims]
             if locs_x == nothing
@@ -320,6 +326,7 @@ function specnet(;additional_params...)
         plot_gini_livingfrac_over_time(iter_results,
             [:proto_threshold, :salary, :white_noise_intensity])
         plot_final_wealth_hist(SimState(graph, AN, arr_protos))
+        plot_life_history(life_history)
     end
 
     if params[:make_anims]
@@ -334,6 +341,7 @@ function specnet(;additional_params...)
         :iter_results => iter_results,
         :overall_results => overall_results,
         :starvation_results => starvation_results,
+        :life_history => life_history,
         :terminated_early => terminated_early)
 end
 
@@ -353,8 +361,8 @@ function kill_sugarless_protos(sim_state::SimState, arr_dead_protos)
             prd("Killing proto $(sim_state.arr_protos[index].proto_id)")
 			for ag in keys(AN) 
 			    if ag.a.proto_id == sim_state.arr_protos[index].proto_id
-				    ag.a.proto_id=-2                     # new value, indicating "was once
-                                                         #   in a proto, but no longer."
+				    ag.a.proto_id=-2        # new value, indicating "was once
+                                            #   in a proto, but no longer."
 				end
 			end
 
@@ -655,6 +663,10 @@ function plot_iteration_graphs(iter)
 
 end
 
+
+function plot_life_history(life_history)
+
+end
 
 # Return an integer ∈  {1,2,3} for the stage that the simulation is currently in:
 #   S1: No agent has yet created a proto.

### 2019-07-02 src/star/Protos.jl
update

@@ -15,7 +15,7 @@ mutable struct Proto
     proto_id::Int
     balance::Float64
     alive::Bool
-    arr_member_ids::Array{String, 1}
+#   arr_member_ids::Array{String, 1}
     ledger_transactions::Array{Transaction, 1}
 end
 
@@ -103,7 +103,6 @@ function form_possible_protos!(arr_agents, agent_environment, arr_protos,
                                        transaction1.transaction_amount +
                                        transaction2.transaction_amount,
                                        true,
-                                       [agobj.a.agent_id, partner_agent.a.agent_id],
                                        [transaction1, transaction2])
                     next_proto_id += 1
                     push!(arr_protos, prototn_obj)
@@ -138,7 +137,6 @@ function update_proto_statuses!(arr_protos, timeperiod)
     for proto_obj in arr_protos
         if proto_obj.balance <= 0
             proto_obj.alive = false
-            proto_obj.arr_member_ids = []
             push!(proto_obj.ledger_transactions,
                   Transaction(0, timeperiod, "closure", "-"))
         end

### 2019-07-02 src/net/sim.jl
Plot life history.

@@ -97,7 +97,7 @@ function specnet(;additional_params...)
     life_history = DataFrame(
         iter = Int[],
         agent = String[],
-        sugar = Float16[]
+        sugar_level = Float16[]
     )
 
     # (Erase old images.)
@@ -326,7 +326,7 @@ function specnet(;additional_params...)
         plot_gini_livingfrac_over_time(iter_results,
             [:proto_threshold, :salary, :white_noise_intensity])
         plot_final_wealth_hist(SimState(graph, AN, arr_protos))
-        plot_life_history(life_history)
+        plot_life_history(life_history, stages)
     end
 
     if params[:make_anims]
@@ -664,8 +664,17 @@ function plot_iteration_graphs(iter)
 end
 
 
-function plot_life_history(life_history)
-
+function plot_life_history(life_history, stages)
+    stage_starts = [findfirst(x->x==n, stages) for n ∈  [2,3]]
+    life_historyp = plot(life_history,
+        group=:agent, x=:iter, y=:sugar_level, Geom.line,
+        xintercept=stage_starts,
+        Geom.vline(style=[:dash], color=["green","red"]),
+        Guide.annotation(compose(context(),
+            Compose.text(stage_starts, fill(maximum(life_history[:sugar_level]),2),
+            [" Stage 2", " Stage 3"], fill(hleft,2), fill(vtop,2)))),
+        Theme(default_color=Colors.RGBA(0,0,0,.5), background_color=colorant"white"))
+    draw(PNG("$(tempdir())/life_history.png"), life_historyp)
 end
 
 # Return an integer ∈  {1,2,3} for the stage that the simulation is currently in:

### 2019-07-02 src/net/sim.jl
Color code life history by proto class.

@@ -97,7 +97,9 @@ function specnet(;additional_params...)
     life_history = DataFrame(
         iter = Int[],
         agent = String[],
-        sugar_level = Float16[]
+        sugar_level = Float16[],
+        proto_id = Int[],
+        num_neighbors = Int[]
     )
 
     # (Erase old images.)
@@ -165,7 +167,8 @@ function specnet(;additional_params...)
         push!(nums_agents, length([ a for a ∈  keys(AN) if a.a.alive ]))
         push!(nums_protos, length(arr_protos))
         for ag ∈  keys(AN)   # if a.a.alive ?
-            push!(life_history, (iter, ag.a.agent_id, ag.a.sugar_level))
+            push!(life_history, (iter, ag.a.agent_id, ag.a.sugar_level,
+                ag.a.proto_id, length(neighbors(graph, AN[ag]))))
         end
 
         if params[:make_anims]
@@ -666,8 +669,13 @@ end
 
 function plot_life_history(life_history, stages)
     stage_starts = [findfirst(x->x==n, stages) for n ∈  [2,3]]
+    life_history[:proto_class] = 
+        map(x->x==-1 ? "no" : (x==-2 ? "dead" : "yes"), life_history[:proto_id])
     life_historyp = plot(life_history,
         group=:agent, x=:iter, y=:sugar_level, Geom.line,
+        color=:proto_class,
+        Scale.color_discrete_manual("blue","purple","red",
+            levels=["no","yes","dead"]),
         xintercept=stage_starts,
         Geom.vline(style=[:dash], color=["green","red"]),
         Guide.annotation(compose(context(),

### 2019-07-02 src/net/sim.jl
Color code life history by isolate/neighbors.

@@ -669,13 +669,13 @@ end
 
 function plot_life_history(life_history, stages)
     stage_starts = [findfirst(x->x==n, stages) for n ∈  [2,3]]
-    life_history[:proto_class] = 
-        map(x->x==-1 ? "no" : (x==-2 ? "dead" : "yes"), life_history[:proto_id])
+    life_history[:isolate] = 
+        map(x->x==0 ? "yes" : "no", life_history[:num_neighbors])
     life_historyp = plot(life_history,
         group=:agent, x=:iter, y=:sugar_level, Geom.line,
-        color=:proto_class,
-        Scale.color_discrete_manual("blue","purple","red",
-            levels=["no","yes","dead"]),
+        color=:isolate,
+        Scale.color_discrete_manual("navy","orange",
+            levels=["no","yes"]),
         xintercept=stage_starts,
         Geom.vline(style=[:dash], color=["green","red"]),
         Guide.annotation(compose(context(),

### 2019-07-02 src/net/param_sweep.jl
Repeat sweep for N

@@ -13,10 +13,14 @@ param_to_sweep=:λ   #parameter to iterate over *any parameter*
                      #for graph sweep param_to_sweep should not be exclusive to one graph type e.g. SF_prob
 start_value=0.0     #value to begin sweep
 end_value=6         #value to end sweep
-num_values=30        #number of distinct values to run
+num_values=10        #number of distinct values to run
 trials_per_value=14   #for each distinct value, number of independent sims to run
 graph_sweep=false    #run the sweep once for each graph type
 original_seed=params[:random_seed]
+repeat_param=:N
+repeat_start_value=10
+repeat_end_value=15
+run_repeat_sweep=true
 
 components=[[],[]]
 global social_connectivity_df=DataFrame(
@@ -121,6 +125,7 @@ function param_sweeper(graph_name; additional_params...)
         counter += (end_value-start_value)/num_values
     end
     sim_tag=0
+    
     rm("$(tempdir())/$(graph_name)_agent_results.csv", force=true)
     rm("$(tempdir())/$(graph_name)_simulation_results.csv", force=true)
     rm("$(tempdir())/$(graph_name)GiniSweepPlot.png", force=true)
@@ -128,6 +133,7 @@ function param_sweeper(graph_name; additional_params...)
     rm("$(tempdir())/$(graph_name)Component_GiniSweepPlots.png", force=true)
     rm("$(tempdir())/$(graph_name)ComponentSweepPlot.png", force=true)
     rm("$(tempdir())/$(graph_name)ProtoPropertiesSweep.png", force=true)
+    rm("$(tempdir())/$(graph_name)repeat_sweep_plot.png", force=true)
 
     #this file contains all info with one line per agent in a given run of siml.jl
     CSV.write("$(tempdir())/$(graph_name)_agent_results.csv",agent_line_df)
@@ -314,7 +320,13 @@ function param_sweeper(graph_name; additional_params...)
     trial_line_df=join(trial_line_df, social_connectivity_df, on = :sim_tag)
 
     CSV.write("$(tempdir())/$(graph_name)_simulation_results.csv",trial_line_df)
-
+   
+    global repeat_sweep_layer=layer(x=plot_df[param_to_sweep],y=plot_df[:gini],Geom.line,
+	                                Theme(line_width=1mm, 
[…]

### 2019-07-03 src/net/param_sweep.jl
Whitespace and other tweaks.

@@ -126,14 +126,14 @@ function param_sweeper(; additional_params...)
     end
     sim_tag=0
 
-    rm("$(tempdir())/$(graph_name)_agent_results.csv", force=true)
-    rm("$(tempdir())/$(graph_name)_simulation_results.csv", force=true)
-    rm("$(tempdir())/$(graph_name)GiniSweepPlot.png", force=true)
-    rm("$(tempdir())/$(graph_name)_wealth_heatmap.png", force=true)
-    rm("$(tempdir())/$(graph_name)Component_GiniSweepPlots.png", force=true)
-    rm("$(tempdir())/$(graph_name)ComponentSweepPlot.png", force=true)
-    rm("$(tempdir())/$(graph_name)ProtoPropertiesSweep.png", force=true)
-    rm("$(tempdir())/$(graph_name)repeat_sweep_plot.png", force=true)
+    rm("$(tempdir())/agent_results.csv", force=true)
+    rm("$(tempdir())/simulation_results.csv", force=true)
+    rm("$(tempdir())/GiniSweepPlot.png", force=true)
+    rm("$(tempdir())/wealth_heatmap.png", force=true)
+    rm("$(tempdir())/Component_GiniSweepPlots.png", force=true)
+    rm("$(tempdir())/ComponentSweepPlot.png", force=true)
+    rm("$(tempdir())/ProtoPropertiesSweep.png", force=true)
+    rm("$(tempdir())/repeat_sweep_plot.png", force=true)
 
 
     #this file contains all info with one line per agent in a given run of siml.jl
@@ -236,8 +236,6 @@ function param_sweeper(; additional_params...)
             #adding results to the df
             push!(trial_line_df,(counter,mark_seed_value,sim_tag,
                 current_sim_gini))
-            
-            
 
             mark_seed_value+=1
         end
@@ -321,10 +319,10 @@ function param_sweeper(; additional_params...)
     trial_line_df=join(trial_line_df, social_connectivity_df, on = :sim_tag)
 
 
-    CSV.write("$(tempdir())/$(graph_name)_simulation_results.csv",trial_line_df)
-   
+    CSV.write("$(tempdir())/simulation_results.csv",trial_line_df)
+
     global repeat_sweep_layer=layer(x=plot_df[param_to_sweep],y=plot_df[:gini],Geom.line,
-	                                Theme(line_width=1mm, 
+	                                Theme(line_width=1mm,
[…]

### 2019-07-03 src/net/sim.jl
Collect and plot proto history.

@@ -102,6 +102,13 @@ function specnet(;additional_params...)
         num_neighbors = Int[]
     )
 
+    proto_history = DataFrame(
+        iter = Int[],
+        proto_id = Int[],
+        balance = Float16[],
+        num_members = Int[],
+    )
+
     # (Erase old images.)
     save_dir = pwd()
     cd("$(tempdir())")
@@ -169,6 +176,10 @@ function specnet(;additional_params...)
         for ag ∈  keys(AN)   # if a.a.alive ?
             push!(life_history, (iter, ag.a.agent_id, ag.a.sugar_level,
                 ag.a.proto_id, length(neighbors(graph, AN[ag]))))
+        end
+        for pr ∈  arr_protos
+            push!(proto_history, (iter, pr.proto_id, pr.balance, length(
+                [ ag for ag ∈  keys(AN) if ag.a.proto_id==pr.proto_id ])))
         end
 
         if params[:make_anims]
@@ -329,7 +340,7 @@ function specnet(;additional_params...)
         plot_gini_livingfrac_over_time(iter_results,
             [:proto_threshold, :salary, :white_noise_intensity])
         plot_final_wealth_hist(SimState(graph, AN, arr_protos))
-        plot_life_history(life_history, stages)
+        plot_history(life_history, proto_history, stages)
     end
 
     if params[:make_anims]
@@ -345,6 +356,7 @@ function specnet(;additional_params...)
         :overall_results => overall_results,
         :starvation_results => starvation_results,
         :life_history => life_history,
+        :proto_history => proto_history,
         :terminated_early => terminated_early)
 end
 
@@ -667,7 +679,7 @@ function plot_iteration_graphs(iter)
 end
 
 
-function plot_life_history(life_history, stages)
+function plot_history(life_history, proto_history, stages)
     stage_starts = [findfirst(x->x==n, stages) for n ∈  [2,3]]
     life_history[:isolate] = 
         map(x->x==0 ? "yes" : "no", life_history[:num_neighbors])
@@ -681,8 +693,20 @@ function plot_life_history(life_history, stages)
         Guide.annotation(compose(context(),
             Compose.text(stage_starts, fill(maximum(life_history[:sugar_level]),2),
             [" Stage 2", " Stage 3"], fill(hleft,2), fill(vtop,2)))),
-        Theme(default_color=Colors.RGBA(0,0,0,.5), background_color=colorant"white"))
[…]

### 2019-07-05 manuscript/draftcssa19.tex
Add plug for computational simulation; wordsmith.

@@
 Analytical sociology~\cite{ch1as_hdbk}, with its emphasis on explanation of collective emergent phenomena using mathematically formulated social mechanisms~\cite{ch2as_hdbk,ch11as_hdbk} anchored at the individual level, is an ideal candidate for this purpose.
+It is particularly powerful when combined with computational simulation, because when mathematically-formulated models reach even a modest level of complexity, they often become analytically intractable.
+Simulation \textit{in silico} can yield approximate results for these more complex scenarios, which supplement the exact results reached by traditional methods.
 
@@
 
+% SD: In light of recent discussions, we may want to downplay Gini and up-play the robustness of agents to exogenous shocks.
 The phenomenon under scrutiny is the emergence and evolution of economic inequality in societies with non-trivial social structures.
-The model we use to answer questions surrounding this phenomena must possess a dynamic model of wealth accumulation, a model of social structure; and a suitably useful measure of inequality.
+The model we use to answer questions surrounding this phenomenon must possess a dynamic model of wealth accumulation, a model of social structure, and a suitably useful measure of inequality.
 The dynamics are modeled as Brownian noise driven linear dynamical systems, here constant growth rate; the structure is modeled by networks, here random graphs; the measure of inequality used is Gini coefficients.
-Although both the dynamical system and the network model are quiet well understood, the precise interplay of structure and dynamics produces interesting emergent wealth distributions.
-To the best of our knowledge, this specific combination of network structure and social dynamics has not been discussed in the computational social science or mathematical sociology literature and consider this the primary contribution of this work.
+Although both the dynamical system and the network model are quite well understood, the precise interplay of structure and dynamics produces interesting emergent wealth distributions.
+To the best of our knowledge, this specific combination of network structure and social dynamics has not been discussed in the computational social science or mathematical sociology literature, and we consider this the primary contribution of this work.
 
 Apart from enabling interactions between social actors, social structures like institutions also shape the form of cooperation and coordination mechanisms.
-The institutions can take the form of economic institutions, like banks and cooperatives; or the form of norms, like resource sharing practices in societies.
-The original SriMil model~\cite{srimil}consists of simple resource pooling arrangement where aggregates of agents pool their excess wealth in a common institution called protoinstitutions, agreeing to provide this saved resource to individual agents in times of need.
+The institutions can take the form of economic institutions, like banks and cooperatives; or the form of norms, like resource-sharing practices in societies.
+The original SriMil model~\cite{srimil}consists of a simple resource pooling arrangement where aggregates of agents pool their excess wealth in a common institution called ``proto-institutions,'' agreeing to provide this saved resource to individual agents in times of need.
 The model of resource pooling used in this work is identical to the SriMil model.
 
-While the analysis to be presented in later sections focus only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-R\'{e}nyi network models, space constraints prevent us from repeating the analysis on other standard \textit{textbook} networks like scale free and small world networks.
+The analysis to be presented in later sections focuses only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-R\'{e}nyi network models; space constraints unfortunately prevent us from repeating the analysis on other standard \textit{textbook} networks like scale-free and small-world networks.
 We also address more empirically grounded models in the concluding section of this paper.
@@
 In the next section, we discuss the mathematical formulation of the model.
-In section 3, we present the analysis of our simulation experiments, summarize key findings and discuss why we chose \texttt{julia} programming language~\cite{Julia-2017} for our implementation.
+In section 3, we present the analysis of our simulation experiments, summarize key findings and discuss why we chose the \texttt{julia} programming language~\cite{Julia-2017} for our implementation.
 In section 4, we discuss the limitations of our simple models, extensions to dynamics and networks more expressive than the ones presented here, and planned future work.
@@
 \end{document}
+% this line is for Stephen's purposes only:
+% vim:textwidth=99999

### 2019-07-06 src/net/sim.jl
Fix stage computation, in light of no dummy Proto.

@@ -707,8 +707,7 @@ end
 #   S3: All agents are either (a) graph isolates, (b) dead, or (c) in a proto.
 global left_stage_1 = false
 function get_stage(sim_state::SimState)
-    if length(sim_state.arr_protos) == 1  &&  # See arr_protos hack
-            !left_stage_1
+    if length(sim_state.arr_protos) == 0  &&  !left_stage_1
         return 1
     else
         global left_stage_1 = true

### 2019-07-06 src/net/sim.jl
Pretty up history plot for publication.

@@ -666,23 +666,26 @@ end
 
 
 function plot_history(life_history, proto_history, stages)
-    stage_starts = [findfirst(x->x==n, stages) for n ∈  [2,3]]
+    stage_starts = [findfirst(x->x==n, stages) for n ∈  1:3]
     stage_starts = [isnothing(ss) ? 1 : ss for ss ∈  stage_starts]
     life_history[:isolate] =
         map(x->x==0 ? "yes" : "no", life_history[:num_neighbors])
     life_historyp = plot(life_history,
         group=:agent, x=:iter, y=:sugar_level, Geom.line,
         color=:isolate,
-        Scale.color_discrete_manual("navy","orange",
-            levels=["no","yes"]),
+        Scale.color_discrete_manual("navy","orange", levels=["no","yes"]),
         xintercept=stage_starts,
-        Geom.vline(style=[:dash], color=["green","red"]),
+        Geom.vline(style=[:dash], color=["blue","green","red"]),
+        yintercept=[params[:proto_threshold]],
+        Geom.hline(style=[:dot], color=["grey"]),
         Guide.annotation(compose(context(),
-            Compose.text(stage_starts, fill(maximum(life_history[:sugar_level]),2),
-            [" Stage 2", " Stage 3"], fill(hleft,2), fill(vtop,2)))),
-        Theme(default_color=Colors.RGBA(0,0,0,.5), background_color=colorant"white",
-            key_position=:bottom),
+            Compose.text(maximum(life_history[:iter]),
+            params[:proto_threshold], "proto threshold", hright, vbottom))),
+        Theme(default_color=Colors.RGBA(0,0,0,.5),
+            background_color=colorant"white", key_position=:bottom),
+        Coord.cartesian(xmin=1, xmax=length(stages)),
         Coord.cartesian(xmax=length(stages)),
+        Guide.xlabel(nothing, orientation=:horizontal),
         Guide.ylabel("Agent wealth", orientation=:vertical))
     to_plot = life_historyp
 
@@ -690,12 +693,19 @@ function plot_history(life_history, proto_history, stages)
         proto_historyp = plot(proto_history,
             group=:proto_id, x=:iter, y=:balance, Geom.line,
             xintercept=stage_starts,
-            Geom.vline(style=[:dash], color=["green","red"]),
-            Theme(default_color=Colors.RGBA(.5,0,.5,.5), background_color=colorant"white",
-                key_position=:bottom),
[…]

### 2019-07-06 manuscript/analysis.tex
Add section 3.1 (verification).

@@
 
-\subsection{None-to-None Network}
+First, we verify that the simulation's output matches obviously expected
+results. Then, we investigate aspects of its behavior which are not computable
+analytically in order to discover important consequences of the model.
 
-\subsection{All-to-All Network}
+\subsection{Verification}
 
-\subsection{Erd\H{o}s-R\'{e}nyi Model}
+\subsubsection{Single simulation runs}
 
-\subsection{Integrating our findings from the previous subsections}
+For a sensible range of parameter settings, the life history of a single
+simulation run follows an expected pattern. Assuming a positive growth rate
+(\textit{i.e.}, salary > metabolic rate), each agent's wealth rises unsteadily
+during stage 1, until eventually the first pair of neighboring agents who each
+reach the threshold form a proto-institution. Throughout stage 2, these agents
+contribute all wealth in excess of the threshold to that proto, and so their
+proto's balance rises unsteadily while their personal wealth remains at the
+constant threshold. Meanwhile, the other agents also reach the threshold at
+various points in time, and also form or join protos, until every non-isolate
+(that is, every node with at least one neighbor) is a member of a proto. Stage
+3 (the starvation period) then commences, with isolates drawing on a greater
+personal wealth than the non-isolates. When an isolate reaches zero wealth, it
+dies; when a non-isolate reaches zero, it draws from its (shared) proto balance
+until that too, reaches zero, and it dies.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\columnwidth]{figures/sampleLifeHistory.png}
+\caption{A single run of the simulation, with $\lambda$=2. Each of 50 nodes is
+given an initial wealth of 50 units, a regular income distributed as
+$\sim\mathcal{N}(20,5)$, a metabolic rate of 5, and a proto threshold of 65.}
+\label{fig:singleRun}
+\end{figure}
+
+This history can be seen in Figure~\ref{fig:singleRun}. The top plot depicts
+agent wealth at every iteration, and the bottom plot shows the balances of the
+protos at the same points in time. (No protos exist until stage 2, by
+definition.) Note that the isolates (orange lines) never form protos, and
+therefore begin the starvation stage with a higher personal wealth to draw
+from. We verified that changes to basic parameters have the expected effect:
+lowering the initial wealth delays the onset of stage 2; a higher $\sigma^2$
+for the income distribution makes the lines less jagged; a higher metabolic
+rate hastens extinction; \textit{etc.}
+
+% Show different levels of white noise intensity relative to growth rate
+%     (salary - metabolic rate)
+
+\subsubsection{Parameter sweeps}
+
+% Gini coefficient (pre-stage-3) decreases with λ
+
+\subsection{Findings}
+
+% Wealth histogram is steady ?
+
+% Which is better strategy: to form protos when possible, or not?

### 2019-07-08 src/net/sim.jl
Add *effective* wealth plot (counting proto share.)

@@ -98,6 +98,7 @@ function specnet(;additional_params...)
         iter = Int[],
         agent = String[],
         sugar_level = Float16[],
+        resources = Float16[],   # combined agent and proto wealth share
         proto_id = Int[],
         num_neighbors = Int[]
     )
@@ -122,7 +123,7 @@ function specnet(;additional_params...)
 
     locs_x, locs_y = nothing, nothing
 
-    arr_protos = []
+    arr_protos = Proto[]
 
     pri("Iterations:\n")
 
@@ -165,7 +166,7 @@ function specnet(;additional_params...)
                 overall_results = collect_stats(SimState(graph, AN, arr_protos))
                 agent_results = DataFrame(
                     agent = [ ag.a.agent_id for ag in keys(AN) ],
-                    sugar = [ ag.a.sugar_level for ag in keys(AN) ],
+                    sugar = [ compute_effective_wealth(arr_protos, ag) for ag in keys(AN) ],
                     proto_id = [ ag.a.proto_id for ag in keys(AN) ]
                 )
             end
@@ -182,6 +183,7 @@ function specnet(;additional_params...)
         push!(nums_protos, length(arr_protos))
         for ag ∈  keys(AN)   # if a.a.alive ?
             push!(life_history, (iter, ag.a.agent_id, ag.a.sugar_level,
+                compute_effective_wealth(arr_protos, ag), 
                 ag.a.proto_id, length(neighbors(graph, AN[ag]))))
         end
         for pr ∈  arr_protos
@@ -291,8 +293,9 @@ function specnet(;additional_params...)
         # If we're going to end up making a single-sim plot, use Gini's CI's
         #   (which use bootstrapping, and are therefore time-consuming) to get
         #   all three. Otherwise, just get (1).
-        wealthArray=[ ag.a.sugar_level
-                            for ag in keys(AN) if ag.a.sugar_level ≥ 0 ]
+        wealthArray=[ compute_effective_wealth(arr_protos, ag)
+                    for ag in keys(AN)
+                        if compute_effective_wealth(arr_protos, ag) ≥ 0 ]
         if params[:make_sim_plots]
             if length(wealthArray) > 1
                 if all_the_same(wealthArray)
@@ -490,7 +493,7 @@ function plot_final_wealth_hist(sim_state::SimState)
     final_wealths=[]
     final_proto_wealths_alive=[]
[…]

### 2019-07-08 manuscript/analysis.tex
Add effective wealth plot.

@@
 therefore begin the starvation stage with a higher personal wealth to draw
-from. We verified that changes to basic parameters have the expected effect:
+from.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\columnwidth]{figures/sampleEffectiveHistory.png}
+\caption{The same simulation run as Figure~\ref{fig:singleRun}, but this time
+depicting each agent's \textit{effective} wealth (its personal wealth plus its
+share of its proto's wealth, if any).}
+\label{fig:effectiveWealthSingleRun}
+\end{figure}
+
+Figure~\ref{fig:effectiveWealthSingleRun} shows the same information in another
+way: instead of plotting each agent's \textit{personal} wealth (as in the top
+plot of Figure~\ref{fig:singleRun}, we show its \textbf{effective wealth},
+defined as the sum of its personal wealth and its ``share'' of its proto's
+wealth (if any). After all, contributions that a proto's members make to its
+balance are available to those members in times of need; therefore, a fair
+comparison between isolates and non-isolates should take this into account.
+From the figure, it can be seen that isolates no longer have a systematic
+advantage (as they appeared to in Figure~\ref{fig:singleRun}.
+
+We verified that changes to basic parameters all have the expected effect:
 lowering the initial wealth delays the onset of stage 2; a higher $\sigma^2$

### 2019-07-08 src/net/analysis.jl
Add analysis.jl. Use *original* isolate status.

@@ -1,0 +1,20 @@
+
+using HypothesisTests
+
+# Assumption: sim.jl has been executed, and its return value saved in a
+#   variable called "r".
+
+# Perform Wilcoxon rank-sum test (a.k.a. "Mann-Whitney U Test") to confirm or
+# deny the hypothesis that isolates die sooner/later than non-isolates on
+# average.
+lh = r[:life_history]
+lifespans = by(lh, [:agent, :original_isolate], lifespan = :iter => maximum)
+
+lifespanp = plot(lifespans, x=:original_isolate, y=:lifespan, Geom.boxplot,
+    color=:original_isolate,
+    Scale.y_continuous(minvalue=0))
+draw(PNG("$(tempdir())/lifespanComparison.png"), lifespanp)
+
+ilifespans = lifespans[lifespans[:original_isolate].==true,:lifespan]
+nlifespans = lifespans[lifespans[:original_isolate].==false,:lifespan]
+srt = MannWhitneyUTest(ilifespans, nlifespans)

### 2019-07-08 src/net/sim.jl

@@ -100,7 +100,7 @@ function specnet(;additional_params...)
         sugar_level = Float16[],
         resources = Float16[],   # combined agent and proto wealth share
         proto_id = Int[],
-        num_neighbors = Int[]
+        num_neighbors = Int[],
     )
 
     proto_history = DataFrame(
@@ -143,6 +143,10 @@ function specnet(;additional_params...)
     local nums_agents=[]
     local nums_protos=[]
 
+    # Remember how many neighbors each node *originally* had.
+    local original_neighbor_count =
+        Dict(ag.a.agent_id=>length(neighbors(graph,AN[ag]))
+                                                for ag ∈  keys(AN))
     global overall_results
     global agent_results
     for iter in 1:params[:max_iters]
@@ -350,7 +354,7 @@ function specnet(;additional_params...)
         plot_gini_livingfrac_over_time(iter_results,
             [:proto_threshold, :salary, :white_noise_intensity])
         plot_final_wealth_hist(SimState(graph, AN, arr_protos))
-        plot_history(life_history, proto_history, stages)
+        plot_history(life_history, proto_history, stages, original_neighbor_count)
     end
 
     if params[:make_anims]
@@ -670,17 +674,17 @@ function plot_iteration_graphs(iter)
 end
 
 
-function plot_history(life_history, proto_history, stages)
+function plot_history(life_history, proto_history, stages, original_neighbor_count)
     stage_starts = [findfirst(x->x==n, stages) for n ∈  1:3]
     stage_starts = [isnothing(ss) ? 1 : ss for ss ∈  stage_starts]
-    life_history[:isolate] =
-        map(x->x==0 ? "yes" : "no", life_history[:num_neighbors])
 
+    life_history[:original_isolate] = 
+        [original_neighbor_count[a] == 0 for a in life_history[:agent]]
     effective_historyp = plot(life_history,
         # Plotting effective wealth, not just agent wealth
         group=:agent, x=:iter, y=:resources, Geom.line,
-        color=:isolate,
-        Scale.color_discrete_manual("navy","orange", levels=["no","yes"]),
+        color=:original_isolate,
+        Scale.color_discrete_manual("navy","orange", levels=[false, true]),
         xintercept=stage_starts,
         Geom.vline(style=[:dash], color=["blue","green","red"]),
         yintercept=[params[:proto_threshold]],
@@ -698,8 +702,8 @@ function plot_history(life_history, proto_history, stages)
[…]

### 2019-07-10 src/net/sim.jl
Plot isolates correctly. Fix #74.

@@ -142,11 +142,8 @@ function specnet(;additional_params...)
     local stages=[]
     local nums_agents=[]
     local nums_protos=[]
+    global stage3_isolates=[]
 
-    # Remember how many neighbors each node *originally* had.
-    local original_neighbor_count =
-        Dict(ag.a.agent_id=>length(neighbors(graph,AN[ag]))
-                                                for ag ∈  keys(AN))
     global overall_results
     global agent_results
     for iter in 1:params[:max_iters]
@@ -171,8 +168,15 @@ function specnet(;additional_params...)
                 agent_results = DataFrame(
                     agent = [ ag.a.agent_id for ag in keys(AN) ],
                     sugar = [ compute_effective_wealth(arr_protos, ag) for ag in keys(AN) ],
-                    proto_id = [ ag.a.proto_id for ag in keys(AN) ]
+                    proto_id = [ ag.a.proto_id for ag in keys(AN) ],
+                    nn = [ length(neighbors(graph,AN[ag])) for ag in keys(AN) ],
+                    raw = [ ag.a.sugar_level for ag in keys(AN) ],
+                  #  isol = [original_neighbor_count[ag.a.agent_id] == 0 for ag in keys(AN) ],
                 )
+
+                # Remember which neighbors were isolates when stage 3 began.
+                global stage3_isolates =
+                    Dict(ag.a.agent_id=>ag.a.proto_id<0 for ag ∈  keys(AN))
             end
             starvation_timer += 1
             if starvation_timer == params[:starvation_period]  ||
@@ -353,8 +357,8 @@ function specnet(;additional_params...)
     if params[:make_sim_plots]
         plot_gini_livingfrac_over_time(iter_results,
             [:proto_threshold, :salary, :white_noise_intensity])
-        plot_final_wealth_hist(SimState(graph, AN, arr_protos))
-        plot_history(life_history, proto_history, stages, original_neighbor_count)
+        #plot_final_wealth_hist(SimState(graph, AN, arr_protos))
+        plot_history(life_history, proto_history, stages, stage3_isolates)
     end
 
     if params[:make_anims]
@@ -674,12 +678,13 @@ function plot_iteration_graphs(iter)
 end
 
 
-function plot_history(life_history, proto_history, stages, original_neighbor_count)
+function plot_history(life_history, proto_history, stages, stage3_isolates)
     stage_starts = [findfirst(x->x==n, stages) for n ∈  1:3]
[…]

### 2019-07-10 src/net/sim.jl
Work around agent_results bug.

@@ -169,8 +169,8 @@ function specnet(;additional_params...)
                     agent = [ ag.a.agent_id for ag in keys(AN) ],
                     sugar = [ compute_effective_wealth(arr_protos, ag) for ag in keys(AN) ],
                     proto_id = [ ag.a.proto_id for ag in keys(AN) ],
-                    nn = [ length(neighbors(graph,AN[ag])) for ag in keys(AN) ],
-                    raw = [ ag.a.sugar_level for ag in keys(AN) ],
+                  #  nn = [ length(neighbors(graph,AN[ag])) for ag in keys(AN) ],
+                  #  raw = [ ag.a.sugar_level for ag in keys(AN) ],
                   #  isol = [original_neighbor_count[ag.a.agent_id] == 0 for ag in keys(AN) ],
                 )
 

### 2019-07-11 manuscript/draftcssa19.tex
Add section 3.1 (verification).
section 1 completed to reflect conclusion

@@
-\documentclass{article}
+\documentclass[sigconf]{acmart}
 \usepackage{amsmath}
@@
 Simultaneously, insights from related disciplines, along with novel scientific inquiry models not usually associated with traditional econometrics, are being taken more seriously.
-The work presented here shares this spirit by integrating substantive ideas from anthropology, economic sociology~\cite{granovetter2017society} and urban sociology~\cite{sampson2012great} and using modeling approaches from computational social science~\cite{hedstrom2018} and analytical sociology~\cite{hedstrom2011oxford} to understand the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
+The work presented here shares this spirit by integrating substantive ideas from anthropology, economic sociology~\cite{granovetter2017society} and urban sociology~\cite{sampson2012great} and using modeling approaches from computational social science~\cite{hedstrom2018}, computational economics~\cite{tesfatsion} and analytical sociology~\cite{hedstrom2011oxford} to understand the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
 % SD: citation for "anthropology," the first element of the last sentence's list? Grief and/or White?
@@
 
-%What is the scientific question of interest to us? 
-%How features of models of structure and dyanmics intera
-
 % SD: In light of recent discussions, we may want to downplay Gini and up-play the robustness of agents to exogenous shocks.
@@
 The model we use to answer questions surrounding this phenomenon must possess a dynamic model of wealth accumulation, a model of social structure, and a suitably useful measure of inequality.
-The dynamics are modeled as Brownian noise driven linear dynamical systems, here constant growth rate; the structure is modeled by networks, here random graphs; the measure of inequality used is Gini coefficients.
+The dynamics are modeled as Brownian noise driven linear dynamical systems, here constant growth rate; the structure is modeled by networks, here random graphs; the measures of inequality used are Gini coefficients, and survival time distributions of agents in response to lack of resources.
 Although both the dynamical system and the network model are quite well understood, the precise interplay of structure and dynamics produces interesting emergent wealth distributions.
-To the best of our knowledge, this specific combination of network structure and social dynamics has not been discussed in the computational social science or mathematical sociology literature, and we consider this the primary contribution of this work.
+To the best of our knowledge, this specific combination of network structure and social dynamics has not been discussed in the computational social science (CSS) or mathematical sociology literature, and we consider this the primary contribution of this work.
 
@@
 
-The analysis to be presented in later sections focuses only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-R\'{e}nyi network models; space constraints unfortunately prevent us from repeating the analysis on other standard \textit{textbook} networks like scale-free and small-world networks.
-We also address more empirically grounded models in the concluding section of this paper.
+The analysis to be presented in later sections focuses only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-R\'{e}nyi network models (ER); space constraints unfortunately prevent us from repeating the analysis on other standard \textit{textbook} networks like scale-free and small-world networks.
+We discuss empirical evidence for the role of social network structures in the concluding section of this paper, motivating the need for more expressive social network models.
 
@@
 
+Before discussing our model in greater mathematical detail, we discuss the model qualitatively, contrasting them with more familiar modeling approaches.
+The model presented here has much in common with models used in social reality inspired models in statistical physics~\cite{redner2001guide}, dynamic process models in network science~\cite{newman2018networks}, and computational social science and agent-based models~\cite{abm_review}; however, our modeling philosophy is somewhere at the interface of agent-based computational economics (ACE)~\cite{tesfatsion} and analytical sociology (AS)~\cite{ch1as_hdbk,ch2as_hdbk}.
+In ACE, we acknowledge its aspiration to develop bottom-up models of economic systems at all scales but restrain from its enthusiastic use of complex but well-calibrated detailed models of markets and agents~\cite{tesfatsion2017}.
+In AS, we assent its focus on social mechanisms in explaining social phenomena, but instead rely on simplified mechanisms with few parameters~\cite{ch11as_hdbk} with the specific goal of extracting insights from \textit{stylized} models.
+
+More specifically, from statistical physics, we borrow the dynamics: diffusion models and associated first-passage time techniques; from network science, we borrow the structural aspects: Erd\H{o}s-R\'{e}nyi network models; and from non-equlibrium statistical physics, CSS and ACE, we borrow a form of cooperation: the concept of coalescence, institution and coordination.
+
+\section{Model}
+The model of cooperative wealth accumulation constructed here is best thought of as a stochastic interacting particle system infused with economic sociological semantics.
+The particle evolves according to an one dimensional diffusion process with constant drift and is driven by a Brownian noise with boundary condition at the origin corresponding to particle absorption.
+After crossing a pre-determined threshold in state space.
+
+In this section, we introduce the model used for our simulation study.
+
+~\cite{redner2001guide} ~\cite{rv}  ~\cite{wilhite} ~\cite{arthur}
+
+\subsection{Implementation}
+%Stephen thinks that a subsection of the Model section should be about the
+%simulation code. It won't be long; just enough to explain how the mathematical
+%model just described is represented and executed in Julia, including some
+%answers to non-obvious questions that arise when considering implementation.
+
+\section{Analysis}
+%\input{analysis}
+
+\section{Conclusion and Future Work}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%Things that could be discussed here but is redundant if we are running out of words 
 %The general idea is to discuss how/why social networks matter wealth accumulation dynamics.
@@
 
-\section{Model}
-~\cite{redner2001guide} ~\cite{rv}
-%Use chapter 3 of redner's book here. 
-%Also, the network model presented here seem to be one of a kind.
-Typically dynam ics on networks are deterministic in nature.
-The models discussed here is different from deterministic dynamic processes and epidemic processes, and diffusion type processes (percolation processes).
-The models are stochastic dynamic systems on networks.
-Such social processes are studied using Stochastic Actor Oriented Models (SOAM) Snidjers.
-ALso use Kolacyzk and Csardi's discussion as reference.
-Social influence models.....
-and others) This is not directly about influence but more about cooperation.
-Need to find a nice way of talking about this.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% This one is really important and top priority for use as a zoomed out conclusion 
+%what kinds of real world systems are we talking about?This section should write itself. Just a brief discussion of phase 2+ and integration with spescape should suffice 
+%%%% ERGM, SBM and LNM are good next steps 
+%%%%% Use anthropology references to motivate more expressive models 
+\cite{power2018cooperation,power2018}
 
-%In the model section, we motivate our current specnet model as attempts to capture specific aspects of historical sociology and urban sociology of Katz and Samson respectively.
+\cite{koster2019,koster2014,koster2015,bogerhoff2015}
 
-%Stephen thinks that a subsection of the Model section should be about the
-%simulation code. It won't be long; just enough to explain how the mathematical
-%model just described is represented and executed in Julia, including some
-%answers to non-obvious questions that arise when considering implementation.
+\cite{smith2019,nolin2012}
 
-\section{Analysis}
-\include{analysis}
+%%%%
 
-\section{Conclusion and Future Work}
-%what kinds of real world systems are we talking about?This section should write itself. Just a brief discussion of phase 2+ and integration with spescape should suffice 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %I am actually confused about whether such a purely preliminary work can say antyhing about the real world.
@@
 
-\cite{power2018cooperation,power2018}
-
-\cite{koster2019,koster2014,koster2015,bogerhoff2015}
-
-\cite{smith2019,nolin2012}
-
 \bibliography{ref_cssa19}

### 2019-07-11 src/net/analysis.jl
Refactor isolate computation.

@@ -2,29 +2,34 @@
 using HypothesisTests
 
 # Assumption: sim.jl has been executed, and its return value saved in a
-#   variable called "r".
+#   variable called "r".                                                                               
 
-# Perform Wilcoxon rank-sum test (a.k.a. "Mann-Whitney U Test") to confirm or
-# deny the hypothesis that isolates die sooner/later than non-isolates on
-# average.
 lh = r[:life_history]
-lifespans = by(lh, [:agent, :original_isolate], lifespan = :iter => maximum)
+lifespans = by(lh, [:agent, :stage3_isolate], lifespan = :iter => maximum)
 
-lifespanp = plot(lifespans, x=:original_isolate, y=:lifespan, Geom.boxplot,
-    color=:original_isolate,
+if nrow(lifespans[lifespans[:stage3_isolate],:]) ≤ 1  ||
+    nrow(lifespans[.!lifespans[:stage3_isolate],:]) ≤ 1
+    prc("WARNING: could not perform analysis on $(filename_components).\n")
+    prc("(There were $(sum(lifespans[:stage3_isolate])) isolates and " *
+        "$(sum(.!lifespans[:stage3_isolate])) non-isolates.)\n")
+    error(1)
+end
+
+lifespanp = plot(lifespans, x=:stage3_isolate, y=:lifespan, Geom.boxplot,
+    color=:stage3_isolate,
     Scale.color_discrete_manual("navy","orange",
         levels=[false, true]),
     style(background_color=colorant"white",key_position=:none),
     Scale.y_continuous(minvalue=0))
 draw(PNG("$(tempdir())/lifespanComparison.png"), lifespanp)
 
-ihistogramp = plot(lifespans[lifespans[:original_isolate],:],
+ihistogramp = plot(lifespans[lifespans[:stage3_isolate],:],
     x=:lifespan, Geom.histogram(bincount=30, density=true), Coord.cartesian(xmax=maximum(lifespans[:lifespan])+10),
     style(background_color=colorant"white", default_color=colorant"orange"),
     Guide.xlabel("Lifespan of isolates"),
     Scale.x_continuous(minvalue=0, maxvalue=maximum(lifespans[:lifespan])))
 
-nhistogramp = plot(lifespans[.!lifespans[:original_isolate],:],
+nhistogramp = plot(lifespans[.!lifespans[:stage3_isolate],:],
[…]

### 2019-07-11 src/net/sim.jl

@@ -191,7 +191,7 @@ function specnet(;additional_params...)
         push!(nums_protos, length(arr_protos))
         for ag ∈  keys(AN)   # if a.a.alive ?
             push!(life_history, (iter, ag.a.agent_id, ag.a.sugar_level,
-                compute_effective_wealth(arr_protos, ag), 
+                compute_effective_wealth(arr_protos, ag),
                 ag.a.proto_id, length(neighbors(graph, AN[ag]))))
         end
         for pr ∈  arr_protos
@@ -336,6 +336,12 @@ function specnet(;additional_params...)
         terminated_early = true
     end
 
+
+    # Add in isolate information to life_history.
+    life_history[:stage3_isolate] =
+        [a ∈  keys(stage3_isolates) ? stage3_isolates[a] : true
+                                        for a ∈  life_history[:agent]]
+
     # Collect results in DataFrame.
     iter_results = DataFrame(
         iter = 1:length(stages),
@@ -358,7 +364,7 @@ function specnet(;additional_params...)
         plot_gini_livingfrac_over_time(iter_results,
             [:proto_threshold, :salary, :white_noise_intensity])
         #plot_final_wealth_hist(SimState(graph, AN, arr_protos))
-        plot_history(life_history, proto_history, stages, stage3_isolates)
+        plot_history(life_history, proto_history, stages)
     end
 
     if params[:make_anims]
@@ -678,17 +684,14 @@ function plot_iteration_graphs(iter)
 end
 
 
-function plot_history(life_history, proto_history, stages, stage3_isolates)
+function plot_history(life_history, proto_history, stages)
     stage_starts = [findfirst(x->x==n, stages) for n ∈  1:3]
     stage_starts = [isnothing(ss) ? 1 : ss for ss ∈  stage_starts]
 
-    life_history[:original_isolate] = 
-        [a ∈  keys(stage3_isolates) ? stage3_isolates[a] : true
-                                            for a ∈  life_history[:agent]]
     effective_historyp = plot(life_history,
         # Plotting effective wealth, not just agent wealth
         group=:agent, x=:iter, y=:resources, Geom.line,
-        color=:original_isolate,
+        color=:stage3_isolate,
         Scale.color_discrete_manual("navy","orange", levels=[false, true]),
         xintercept=stage_starts,
         Geom.vline(style=[:dash], color=["blue","green","red"]),
[…]

### 2019-07-11 src/net/analysis.jl
(Tweak plot annotation.)

@@ -2,7 +2,7 @@
 using HypothesisTests
 
 # Assumption: sim.jl has been executed, and its return value saved in a
-#   variable called "r".                                                                               
+#   variable called "r".
 
 lh = r[:life_history]
 lifespans = by(lh, [:agent, :stage3_isolate], lifespan = :iter => maximum)

### 2019-07-11 src/net/sim.jl

@@ -727,6 +727,8 @@ function plot_history(life_history, proto_history, stages)
         Guide.ylabel("Agent wealth", orientation=:vertical))
     to_plot = life_historyp
 
+    stage_text_tweak = 150  # tweak this higher to make the "Stage 1/2/3"
+                            #   text labels shift lower.
     if nrow(proto_history) > 0
         proto_historyp = plot(proto_history,
             group=:proto_id, x=:iter, y=:balance, Geom.line,
@@ -734,10 +736,12 @@ function plot_history(life_history, proto_history, stages)
             Geom.vline(style=[:dash], color=["blue","green","red"]),
             Guide.annotation(compose(context(),
                 Compose.text(stage_starts,
-                    fill(maximum(proto_history[:balance])-15,3),
-                    ["Stage 1", "Stage 2", "Stage 3"], fill(hleft,3), fill(vtop,3),
+                    fill(maximum(proto_history[:balance])-stage_text_tweak,3),
+                    ["Stage 1", "Stage 2", "Stage 3"],
+                    fill(hleft,3), fill(vtop,3),
                     [Rotation(-π/2, stage_starts[k],
-                        maximum(proto_history[:balance])-15) for k ∈  1:3]))),
+                        maximum(proto_history[:balance])-stage_text_tweak)
+                                                            for k ∈  1:3]))),
             Theme(default_color=Colors.RGBA(.5,0,.5,.5),
                 background_color=colorant"white", key_position=:bottom),
             Coord.cartesian(xmin=1, xmax=length(stages)),

### 2019-07-11 src/net/analysis.jl
Add code to compare isolate/non- lifespans.

@@ -1,57 +1,68 @@
 
 using HypothesisTests
 
-# Assumption: sim.jl has been executed, and its return value saved in a
-#   variable called "r".
+# This function returns either the result of a Mann-Whitney test comparing
+#   lifespan of isolates with non-isolates, or "nothing" if no such comparison
+#   could be made (for example, if there weren't sufficient numbers of both
+#   isolates and non-isolates.) As a side effect, produces a number of plots in
+#   /tmp comparing the two.
+# The "results" argument should be the return value from specnet().
+#   "id_string" is an arbitrary string used in plot filenames and titles.
+function perform_analysis(results, id_string="")
 
-lh = r[:life_history]
-lifespans = by(lh, [:agent, :stage3_isolate], lifespan = :iter => maximum)
+    lh = results[:life_history]
+    lifespans = by(lh, [:agent, :stage3_isolate], lifespan = :iter => maximum)
 
-if nrow(lifespans[lifespans[:stage3_isolate],:]) ≤ 1  ||
-    nrow(lifespans[.!lifespans[:stage3_isolate],:]) ≤ 1
-    prc("WARNING: could not perform analysis on $(filename_components).\n")
-    prc("(There were $(sum(lifespans[:stage3_isolate])) isolates and " *
-        "$(sum(.!lifespans[:stage3_isolate])) non-isolates.)\n")
-    error(1)
-end
+    if nrow(lifespans[lifespans[:stage3_isolate],:]) ≤ 1  ||
+        nrow(lifespans[.!lifespans[:stage3_isolate],:]) ≤ 1
+        prc("WARNING: could not perform analysis on $(id_string).\n")
+        prc("(There were $(sum(lifespans[:stage3_isolate])) isolates and " *
+            "$(sum(.!lifespans[:stage3_isolate])) non-isolates.)\n")
+        return
+    end
 
-lifespanp = plot(lifespans, x=:stage3_isolate, y=:lifespan, Geom.boxplot,
-    color=:stage3_isolate,
-    Scale.color_discrete_manual("navy","orange",
-        levels=[false, true]),
-    style(background_color=colorant"white",key_position=:none),
-    Scale.y_continuous(minvalue=0))
-draw(PNG("$(tempdir())/lifespanComparison.png"), lifespanp)
[…]

### 2019-07-11 src/net/param_sweep.jl
Agents in protos plot

@@ -20,7 +20,7 @@ original_seed=params[:random_seed]
 repeat_param=:N
 repeat_start_value=10
 repeat_end_value=15
-run_repeat_sweep=true
+run_repeat_sweep=false
 
 components=[[],[]]
 global social_connectivity_df=DataFrame(
@@ -343,6 +343,16 @@ function param_sweeper(; additional_params...)
         ),
         y_label="Protos",
         )
+
+    numagentspp = draw_plot(plot_df, param_to_sweep,
+        Dict("num_agents_in_proto" => "green"),
+            
+        Dict("num_agents_in_proto"=> :solid
+            ),
+        y_label="Number agents in proto",
+        extra=[Guide.annotation(compose(context(), Compose.text(minimum(plot_df[param_to_sweep]), params[:N], "N=$(params[:N])", hleft, vtop))),
+         Coord.Cartesian(ymin=0, ymax=params[:N]),
+         layer(yintercept=[params[:N]], Geom.hline(style=:dot, color=colorant"navy"))[1]])
 
     numlivingp = draw_plot(plot_df, param_to_sweep,
         Dict("num_living_agents_pre" => "green",

### 2019-07-11 src/net/setup_params.jl

@@ -39,7 +39,7 @@ params = Dict{Symbol,Any}(
                                     #   - "complete"
                                     #   - "empty"
 
-    :λ => float(2),                 # ER: expected number if edges per node
+    :λ => float(0.0),                 # ER: expected number if edges per node
 
     :SF_edges => 40,                # SF: number of edges
     :SF_degree => 2,                # SF: exponent of expected power law degree

### 2019-07-12 manuscript/analysis.tex
(Add reminders.)
Add Gini history plot (figure 3).

@@
 way: instead of plotting each agent's \textit{personal} wealth (as in the top
-plot of Figure~\ref{fig:singleRun}, we show its \textbf{effective wealth},
+plot of Figure~\ref{fig:singleRun}), we show its \textbf{effective wealth},
 defined as the sum of its personal wealth and its ``share'' of its proto's
@@
 From the figure, it can be seen that isolates no longer have a systematic
-advantage (as they appeared to in Figure~\ref{fig:singleRun}.
+advantage (as they appeared to in Figure~\ref{fig:singleRun}.)
 
@@
 rate hastens extinction; \textit{etc.}
+
+To see how wealth inequality plays out over time, we plot the Gini coefficient
+of the population in Figure~\ref{fig:giniHistory}. (The Gini calculation is
+taken with respect to each agent's \textit{effective} wealth, not merely its
+personal wealth.) In stage 2, we see inequality decrease as agents join one
+another in protos and contribute their ``excess'' wealth to a shared pool. When
+the stage 3 starvation period commences, inequality rises as the poorer agents
+drop to zero and begin to deplete proto balances.
+
+\begin{figure}[hb]
+\centering
+\includegraphics[width=\columnwidth]{figures/giniHistory.png}
+\caption{The simulated society's wealth inequality over time. (The same
+simulation parameters were used as in Figures~\ref{fig:singleRun} and
+\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.)}
+\label{fig:giniHistory}
+\end{figure}
+
+% Note that the empty graph can't really be shown because stages 2 and 3 have
+% no well-defined meaning in that case.
+
+% Show Gini plot, null hypothesis, "this is why it doesn't matter"
 

### 2019-07-12 src/net/sim.jl
Plot Gini vs time alone (figure 3).

@@ -361,8 +361,8 @@ function specnet(;additional_params...)
     end
 
     if params[:make_sim_plots]
-        plot_gini_livingfrac_over_time(iter_results,
-            [:proto_threshold, :salary, :white_noise_intensity])
+        plot_gini_livingfrac_over_time(iter_results)
+        #   [:proto_threshold, :salary, :white_noise_intensity])
         #plot_final_wealth_hist(SimState(graph, AN, arr_protos))
         plot_history(life_history, proto_history, stages)
     end
@@ -544,7 +544,7 @@ end
 # Plot the Gini coefficient, and the fraction of agents still alive, over time.
 # The callouts parameter should be a list of symbols which should appear in the
 # title's plot.
-function plot_gini_livingfrac_over_time(iter_results, callouts)
+function plot_gini_livingfrac_over_time(iter_results, callouts=[])
 
     # Remove rows with NaNs.
     for col in names(iter_results)
@@ -606,8 +606,9 @@ function plot_gini_livingfrac_over_time(iter_results, callouts)
 #            ["black","brown"]),
         style(background_color=colorant"white",key_position=:bottom))
 
+    draw(PNG("$(tempdir())/GiniPlot.png"), giniPlot)
     tall = vstack(giniPlot, livingPlot)
-    draw(PNG("$(tempdir())/GiniPlot.png", 4inch, 6inch), tall)
+    draw(PNG("$(tempdir())/GiniLivingPlot.png", 4inch, 6inch), tall)
 end
 
 function plot_iteration_graphs(iter)

### 2019-07-12 manuscript/draftcssa19.tex

@@
 
-More specifically, from statistical physics, we borrow the dynamics: diffusion models and associated first-passage time techniques; from network science, we borrow the structural aspects: Erd\H{o}s-R\'{e}nyi network models; and from non-equlibrium statistical physics, CSS and ACE, we borrow a form of cooperation: the concept of coalescence, institution and coordination.
+More specifically, from statistical physics, we borrow the dynamics: diffusion models and associated first-passage time techniques; from network science, we borrow the structural aspects: Erd\H{o}s-R\'{e}nyi network (ER) models; and from non-equlibrium statistical physics, CSS and ACE, we borrow a form of cooperation: the concept of coalescence, institution and coordination.
 
@@
 The particle evolves according to an one dimensional diffusion process with constant drift and is driven by a Brownian noise with boundary condition at the origin corresponding to particle absorption.
-After crossing a pre-determined threshold in state space.
+After crossing a pre-determined threshold in state space, particles above the threshold follow a protocol and coalesce together.
+In an ensemble of otherwise identical particles, a given particle may coalesce with a subset of other particles.
+This mixing characteristic is encoded via a graph.
+Both the conjoined particles and individual particles die upon crossing the origin.
+This model of interacting diffusing particles can be provided with substantive semantics as follows.
 
-In this section, we introduce the model used for our simulation study.
+%Might be nice to put a nice table here 
+The one dimensional state space of the particle is identified with the wealth of an social actor (agent).
+We consider a homogeneous population where all agents are required burn their wealth at a constant specified rate in order to survive.
+In addition, the agents all gain wealth at a constant rate.
+The resource draining rate and the resource gaining rate are additive and constitute the drift of the diffusion process.
+The environmental contingency is modeled by a Brownian noise of a specified intensity.
+Upon crossing a specific wealth threshold, agents can coalesce to form a cooperative unit deciding to pool their resources and their environmental contingencies into a single unit which we call a \textit{proto-institution} (proto).
+The mixing characteristic of this ensemble is the social network (here ER model).
 

### 2019-07-12 src/net/param_sweep.jl
Add lifespan comparison plots.

@@ -33,6 +33,8 @@ global social_connectivity_df=DataFrame(
     num_living_agents_post=Float64[],
     num_protos_pre=Float64[],
     num_protos_post=Float64[],
+    avg_lifespan_isos=Float64[],
+    avg_lifespan_nonisos=Float64[],
     sim_tag=Int[])
 
 
@@ -97,6 +99,7 @@ function param_sweeper(; additional_params...)
             iter_results = results[:iter_results]
             overall_results = results[:overall_results]
             starvation_results = results[:starvation_results]
+            avg_lifespans = results[:avg_lifespans]
 
             push!(social_connectivity_df,
                 (overall_results[:size_largest_comp],
@@ -108,6 +111,8 @@ function param_sweeper(; additional_params...)
                  starvation_results[:num_living_agents],  # shouldn't be here
                  overall_results[:num_protos],     # shouldn't be here
                  starvation_results[:num_protos],  # shouldn't be here
+                 avg_lifespans[1],     # shouldn't be here
+                 avg_lifespans[2],     # shouldn't be here
 
                  (i*trials_per_value+j)))
 
@@ -183,6 +188,12 @@ function param_sweeper(; additional_params...)
         num_protos_post=Float64[],
         num_protos_post_lowCI=Float64[],
         num_protos_post_highCI=Float64[],
+        avg_lifespan_isos=Float64[],
+        avg_lifespan_isos_lowCI=Float64[],
+        avg_lifespan_isos_highCI=Float64[],
+        avg_lifespan_nonisos=Float64[],
+        avg_lifespan_nonisos_lowCI=Float64[],
+        avg_lifespan_nonisos_highCI=Float64[],
     )
     names!(plot_df, prepend!(names(plot_df)[2:end], [param_to_sweep]))
 
@@ -210,6 +221,8 @@ function param_sweeper(; additional_params...)
         curr_num_living_agents_post=[]
         curr_num_protos_pre=[]
         curr_num_protos_post=[]
+        curr_avg_lifespan_isos=[]
+        curr_avg_lifespan_nonisos=[]
         for i=1:trials_per_value
 
             sim_tag=(j*trials_per_value+i)
@@ -233,6 +246,8 @@ function param_sweeper(; additional_params...)
[…]

### 2019-07-12 src/net/sim.jl

@@ -381,6 +381,7 @@ function specnet(;additional_params...)
         :starvation_results => starvation_results,
         :life_history => life_history,
         :proto_history => proto_history,
+        :avg_lifespans => compute_avg_lifespan(life_history),
         :terminated_early => terminated_early)
 end
 
@@ -825,4 +826,18 @@ function compute_effective_wealth(arr_protos::Array{Proto,1}, agent::NetAgent)
             length([a for a ∈  keys(AN) if a.a.proto_id==agent.a.proto_id]) +
             agent.a.sugar_level
     end
+end
+
+# Return an array of two numbers: the average lifespan of isolates, and
+# non-isolates, in this simulation run.
+function compute_avg_lifespan(life_history)
+    isol_ids = unique(life_history[life_history[:stage3_isolate],:agent])
+    nonisol_ids = unique(life_history[.!life_history[:stage3_isolate],:agent])
+    isol_lifespans = [maximum(life_history[life_history[:agent].==aid,:iter])
+        for aid ∈  isol_ids]
+    nonisol_lifespans = [maximum(life_history[life_history[:agent].==aid,:iter])
+        for aid ∈  nonisol_ids]
+    prd("isol lifespans are $(isol_lifespans)")
+    prd("non-isol lifespans are $(nonisol_lifespans)")
+    return [ mean(isol_lifespans), mean(nonisol_lifespans) ]
 end

### 2019-07-12 manuscript/draftcssa19.tex
Begin implementation section.

@@
 \subsection{Implementation}
-%Stephen thinks that a subsection of the Model section should be about the
-%simulation code. It won't be long; just enough to explain how the mathematical
-%model just described is represented and executed in Julia, including some
-%answers to non-obvious questions that arise when considering implementation.
+
+The model is realized in a discrete-time Julia simulation program, in which each particle (agent) is represented as a mutable struct that maintains that agent's state over time.
+Each agent's state includes its current amount of wealth and which proto (if any) it is a member of.
+Additionally, using the LightGraphs package~\cite{LightGraphs-2017}, each agent is associated with a node of a randomly generated ER graph.
+Protos are also represented as mutable structs, each of which contains a list of member agent IDs and a current wealth balance.
+
+% cite Bootstrap?
+We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).
+Additionally, Julia easily allows the programmer to invoke code from R packages when necessary, as we did for Gini coefficient calculation with the R package DescTools~\cite{DescTools-2019}.
 

### 2019-07-12 manuscript/analysis.tex
Complete implementation section.

@@
 \caption{A single run of the simulation, with $\lambda$=2. Each of 50 nodes is
-given an initial wealth of 50 units, a regular income distributed as
-$\sim\mathcal{N}(20,5)$, a metabolic rate of 5, and a proto threshold of 65.}
-\label{fig:singleRun}
+given an initial wealth of $\sim\mathcal{U}(0,50)$ units, a regular income
+distributed as $\sim\mathcal{N}(20,5)$, a metabolic rate of 5, and a proto
+threshold of 65.} \label{fig:singleRun}
 \end{figure}

### 2019-07-12 src/net/param_sweep.jl
update

@@ -13,7 +13,7 @@ param_to_sweep=:λ   #parameter to iterate over *any parameter*
                      #for graph sweep param_to_sweep should not be exclusive to one graph type e.g. SF_prob
 start_value=0.0     #value to begin sweep
 end_value=6         #value to end sweep
-num_values=10        #number of distinct values to run
+num_values=100        #number of distinct values to run
 trials_per_value=14   #for each distinct value, number of independent sims to run
 graph_sweep=false    #run the sweep once for each graph type
 original_seed=params[:random_seed]

### 2019-07-12 src/net/setup_params.jl

@@ -1,25 +1,25 @@
 
 ## Input parameters
 params = Dict{Symbol,Any}(
-    :N => 30,                       # number of agents
-    :max_iters => 50,               # maximum number of iterations the simulation
+    :N => 500,                       # number of agents
+    :max_iters => 150,               # maximum number of iterations the simulation
                                     #   runs before termination (will terminate
                                     #   earlier if stopping condition reached)
-    :starvation_period => 20,       # the number of iterations to starve all agents
+    :starvation_period => 80,       # the number of iterations to starve all agents
                                     #   after the simulation has reached stage 3
                                     #   (all live non-isolate agents in protos)
     :openness => float(0.0),        # 0 <=> openness <=> 1
                                     #   (0: always choose from neighbor,
                                     #    1: always choose from entire city)
-    :init_sg_lvl => 100,            # each agent starts with wealth
+    :init_sg_lvl => 50,            # each agent starts with wealth
                                     #   ~U(1, init_sg_lvl)
     :metabolic_rate => 5,           # each iteration, each agent consumes exactly
                                     #   this much sugar
     :salary => 20,                   # each iteration, each agent receives exactly
                                     #   this much sugar
     :white_noise_intensity =>       # each iteration, an agent receives (or loses)
-        float(1.0),                 #   ~N(0, white_noise_intensity) extra sugar
-    :proto_threshold => 50,         # each agent in an encounter must have
+        float(5.0),                 #   ~N(0, white_noise_intensity) extra sugar
+    :proto_threshold => 65,         # each agent in an encounter must have
                                     #   > wealth than this to form a proto
     :make_anims => true,           # create animations of results?
     :make_sim_plots => true,        # create plots (for individual simulations)?
@@ -39,7 +39,7 @@ params = Dict{Symbol,Any}(
                                     #   - "complete"
                                     #   - "empty"
 
-    :λ => float(0.0),                 # ER: expected number if edges per node
+    :λ => float(2.0),                 # ER: expected number if edges per node
 
     :SF_edges => 40,                # SF: number of edges
     :SF_degree => 2,                # SF: exponent of expected power law degree

### 2019-07-12 manuscript/analysis.tex

@@
 
-To see how wealth inequality plays out over time, we plot the Gini coefficient
-of the population in Figure~\ref{fig:giniHistory}. (The Gini calculation is
-taken with respect to each agent's \textit{effective} wealth, not merely its
-personal wealth.) In stage 2, we see inequality decrease as agents join one
-another in protos and contribute their ``excess'' wealth to a shared pool. When
-the stage 3 starvation period commences, inequality rises as the poorer agents
-drop to zero and begin to deplete proto balances.
+% Will's paragraph goes here, references Figure~\ref{fig:giniHistory}.
 

### 2019-07-12 manuscript/draftcssa19.tex

@@
 
-The model is realized in a discrete-time Julia simulation program, in which each particle (agent) is represented as a mutable struct that maintains that agent's state over time.
-Each agent's state includes its current amount of wealth and which proto (if any) it is a member of.
+The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state.
+An agent's state includes its current amount of wealth and which proto (if any) it is a member of.
 Additionally, using the LightGraphs package~\cite{LightGraphs-2017}, each agent is associated with a node of a randomly generated ER graph.
 Protos are also represented as mutable structs, each of which contains a list of member agent IDs and a current wealth balance.
+
+The simulation proceeds as follows. For configurable parameters
+$N > 0$,
+$\texttt{init\_max} > 0$,
+$\texttt{salary} > 0$,
+$m > 0$ (metabolic rate),
+$t_p > 0$ (the ``proto threshold''),
+$\sigma^2 \ge 0$ and
+$0 \le \lambda \le 1$:
+
+\begin{enumerate}
+\itemsep.1em
+\item Create $N$ agents, each with a random initial wealth (uniformly distributed from 0 to \texttt{init\_max}), and related to one another as per a random ER network with parameter $\lambda$.
+\item \textbf{Stages 1 and 2\footnote{We define ``Stage 1'' as the period \textit{before} the first proto is formed, ``Stage 2'' as the period \textit{during} which protos are being formed}:} Repeat until all non-isolate agents\footnote{An \textbf{isolate} agent is one with no graph neighbors.} are members of a proto:
+    \begin{enumerate}
+    \itemsep.1em
+    \item Each agent $A$ whose current wealth $\ge t_p$, and who is not currently a member of a proto, chooses at random one of its graph neighbors (call it $B$) whose wealth \textit{also} exceeds $t_p$.
+(If there are no such neighbors, proceed to the next agent.) If $B$ is already in a proto, have $A$ join $B$'s proto.
+If not, have $A$ and $B$ form a new proto.
+    \item Each agent gains an amount of wealth equal to $(\texttt{salary} - m + \epsilon)$, where $\epsilon \sim \mathcal{N}(0,\sigma^2)$ (white noise).\footnote{Note that this ``gain'' could be negative, in which case the agent, and possibly its proto, may be subject to death exactly as in step (3).}
+    \item Each agent \textit{that is in a proto} donates all its wealth in excess of $t_p$ to that proto's balance. (Agents not in a proto maintain their current wealth.)
+    \end{enumerate}
+    \item \textbf{Stage 3 (starvation):} Repeat until all agents are dead:
+        \begin{enumerate}
+        \itemsep.1em
+        \item Each agent \textit{loses} an amount of wealth equal to $(m + \epsilon), \epsilon \sim \mathcal{N}(0,\sigma^2)$.
+        \item If an agent's wealth would drop below zero as a result of this loss, and if it is not a member of a proto, it dies and is removed from the simulation.
+If it \textit{is} a member of a proto, it withdraws the necessary amount from its proto's balance to remain at zero wealth.
+If the proto does not have sufficient funds to cover the loss, both the agent and the proto die and are removed from the simulation.
+        \end{enumerate}
+\end{enumerate}
+
+Various statistical counters are updated as the program executes so that its behavior can be analyzed post mortem.
+The main simulation loop can also be invoked from a ``parameter sweep'' program which executes it multiple times over a range of parameter values, in order to determine how the model's behavior changes in response to key parameters.
 

### 2019-07-12 manuscript/analysis.tex
Refactor 1st part of "analysis" to "verification."

@@
-% (Separate analysis.tex file, so all images are in a separate file.)
+\subsection{Gini coefficient}
 
-First, we verify that the simulation's output matches obviously expected
-results. Then, we investigate aspects of its behavior which are not computable
-analytically in order to discover important consequences of the model.
+% Will's text and plot showing Gini coefficient (pre-stage-3) decreases with λ
 
-\subsection{Verification}
+\subsection{Life expectancy}
 
-\subsubsection{Single simulation runs}
-
-For a sensible range of parameter settings, the life history of a single
-simulation run follows an expected pattern. Assuming a positive growth rate
-(\textit{i.e.}, salary > metabolic rate), each agent's wealth rises unsteadily
-during stage 1, until eventually the first pair of neighboring agents who each
-reach the threshold form a proto-institution. Throughout stage 2, these agents
-contribute all wealth in excess of the threshold to that proto, and so their
-proto's balance rises unsteadily while their personal wealth remains at the
-constant threshold. Meanwhile, the other agents also reach the threshold at
-various points in time, and also form or join protos, until every non-isolate
-(that is, every node with at least one neighbor) is a member of a proto. Stage
-3 (the starvation period) then commences, with isolates drawing on a greater
-personal wealth than the non-isolates. When an isolate reaches zero wealth, it
-dies; when a non-isolate reaches zero, it draws from its (shared) proto balance
-until that too, reaches zero, and it dies.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=\columnwidth]{figures/sampleLifeHistory.png}
-\caption{A single run of the simulation, with $\lambda$=2. Each of 50 nodes is
-given an initial wealth of $\sim\mathcal{U}(0,50)$ units, a regular income
-distributed as $\sim\mathcal{N}(20,5)$, a metabolic rate of 5, and a proto
-threshold of 65.} \label{fig:singleRun}
-\end{figure}
-
-This history can be seen in Figure~\ref{fig:singleRun}. The top plot depicts
-agent wealth at every iteration, and the bottom plot shows the balances of the
-protos at the same points in time. (No protos exist until stage 2, by
-definition.) Note that the isolates (orange lines) never form protos, and
-therefore begin the starvation stage with a higher personal wealth to draw
-from.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=\columnwidth]{figures/sampleEffectiveHistory.png}
-\caption{The same simulation run as Figure~\ref{fig:singleRun}, but this time
-depicting each agent's \textit{effective} wealth (its personal wealth plus its
-share of its proto's wealth, if any).}
-\label{fig:effectiveWealthSingleRun}
-\end{figure}
-
-Figure~\ref{fig:effectiveWealthSingleRun} shows the same information in another
-way: instead of plotting each agent's \textit{personal} wealth (as in the top
-plot of Figure~\ref{fig:singleRun}), we show its \textbf{effective wealth},
-defined as the sum of its personal wealth and its ``share'' of its proto's
-wealth (if any). After all, contributions that a proto's members make to its
-balance are available to those members in times of need; therefore, a fair
-comparison between isolates and non-isolates should take this into account.
-From the figure, it can be seen that isolates no longer have a systematic
-advantage (as they appeared to in Figure~\ref{fig:singleRun}.)
-
-We verified that changes to basic parameters all have the expected effect:
-lowering the initial wealth delays the onset of stage 2; a higher $\sigma^2$
-for the income distribution makes the lines less jagged; a higher metabolic
-rate hastens extinction; \textit{etc.}
-
-% Will's paragraph goes here, references Figure~\ref{fig:giniHistory}.
-
-\begin{figure}[hb]
-\centering
-\includegraphics[width=\columnwidth]{figures/giniHistory.png}
-\caption{The simulated society's wealth inequality over time. (The same
-simulation parameters were used as in Figures~\ref{fig:singleRun} and
-\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.)}
-\label{fig:giniHistory}
-\end{figure}
-
-% Note that the empty graph can't really be shown because stages 2 and 3 have
-% no well-defined meaning in that case.
-
-% Show Gini plot, null hypothesis, "this is why it doesn't matter"
-
-% Show different levels of white noise intensity relative to growth rate
-%     (salary - metabolic rate)
-
-\subsubsection{Parameter sweeps}
-
-% Gini coefficient (pre-stage-3) decreases with λ
-
-\subsection{Findings}
+% Plots from 7/12 showing you best get in a proto if lambda and white noise 
+%   are high
 
 % Wealth histogram is steady ?
-
-% Which is better strategy: to form protos when possible, or not?

### 2019-07-12 manuscript/verification.tex

We first verify that the simulation's output matches obviously expected
results. Then, in the following section, we investigate aspects of its behavior
which are not computable analytically in order to discover important
consequences of the model.

\subsection{Agent and proto life history}

For a sensible range of parameter settings, the life history of a single
simulation run follows an expected pattern. Assuming a positive growth rate
(\textit{i.e.}, salary > metabolic rate), each agent's wealth rises unsteadily
during stage 1, until eventually the first pair of neighboring agents who each
reach the threshold form a proto-institution. Throughout stage 2, these agents
contribute all wealth in excess of the threshold to that proto, and so their
proto's balance rises unsteadily while their personal wealth remains at the
constant threshold. Meanwhile, the other agents also reach the threshold at
various points in time, and also form or join protos, until every non-isolate
(that is, every node with at least one neighbor) is a member of a proto. Stage
3 (the starvation period) then commences, with isolates drawing on a greater
personal wealth than the non-isolates. When an isolate reaches zero wealth, it
dies; when a non-isolate reaches zero, it draws from its (shared) proto balance
until that too, reaches zero, and it dies.

\begin{figure}[ht]
\centering
\includegraphics[width=\columnwidth]{figures/sampleLifeHistory.png}
\caption{A single run of the simulation, with $\lambda$=2. Each of 50 nodes is
given an initial wealth of $\sim\mathcal{U}(0,50)$ units, a regular income
distributed as $\sim\mathcal{N}(20,5)$, a metabolic rate of 5, and a proto
threshold of 65.} \label{fig:singleRun}
\end{figure}

This history can be seen in Figure~\ref{fig:singleRun}. The top plot depicts
agent wealth at every iteration, and the bottom plot shows the balances of the
protos at the same points in time. (No protos exist until stage 2, by
definition.) Note that the isolates (orange lines) never form protos, and
therefore begin the starvation stage with a higher personal wealth to draw
from.

\begin{figure}[ht]
\centering
\includegraphics[width=\columnwidth]{figures/sampleEffectiveHistory.png}
\caption{The same simulation run as Figure~\ref{fig:singleRun}, but this time
depicting each agent's \textit{effective} wealth (its personal wealth plus its
share of its proto's wealth, if any).}
\label{fig:effectiveWealthSingleRun}
\end{figure}

Figure~\ref{fig:effectiveWealthSingleRun} shows the same information in another
way: instead of plotting each agent's \textit{personal} wealth (as in the top
plot of Figure~\ref{fig:singleRun}), we show its \textbf{effective wealth},
defined as the sum of its personal wealth and its ``share'' of its proto's
wealth (if any). After all, contributions that a proto's members make to its
balance are available to those members in times of need; therefore, a fair
comparison between isolates and non-isolates should take this into account.
From the figure, it can be seen that isolates no longer have a systematic
advantage (as they appeared to in Figure~\ref{fig:singleRun}.)

We verified that changes to basic parameters all have the expected effect:
lowering the initial wealth delays the onset of stage 2; a higher $\sigma^2$
for the income distribution makes the lines less jagged; a higher metabolic
rate hastens extinction; \textit{etc.}

\subsection{Gini coefficient history}

% Will's paragraph goes here, references Figure~\ref{fig:giniHistory}.

\begin{figure}[hb]
\centering
\includegraphics[width=\columnwidth]{figures/giniHistory.png}
\caption{The simulated society's wealth inequality over time. (The same
simulation parameters were used as in Figures~\ref{fig:singleRun} and
\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.)}
\label{fig:giniHistory}
\end{figure}

### 2019-07-12 manuscript/analysis.tex
Add spot for Will's Gini param sweep plot.

@@
 \subsection{Gini coefficient}
+
+As mentioned in Section~\ref{giniKindaSucks}, the Gini coefficient is not the
+ideal measure of inequality for our apocalyptic model. Nonetheless, it is
+illustrative to see how it varies with respect to the ER $\lambda$ parameter.
+Figure~\ref{fig:giniVsLambda} depicts the Gini computed \textit{at the onset
+of stage 3} (before starvation) versus $\lambda$, and confirms that...
+% Will, finish this paragraph.
+
+\begin{figure}[hb]
+\centering
+\includegraphics[width=\columnwidth]{figures/giniVsLambda.png}
+\caption{The average Gini coefficient, computed before the onset of starvation,
+for various values of the ER $\lambda$ connectivity parameter.}
+\label{fig:giniVsLambda}
+\end{figure}
 

### 2019-07-12 manuscript/analysis.tex
Add life expectancy section.

@@
 \caption{The average Gini coefficient, computed before the onset of starvation,
-for various values of the ER $\lambda$ connectivity parameter.}
+for various values of the ER $\lambda$ connectivity parameter. The color band
+represents a bootstrapped 95\% confidence interval.}
 \label{fig:giniVsLambda}
@@
 
-% Plots from 7/12 showing you best get in a proto if lambda and white noise 
-%   are high
+Rather than absolute wealth, which the Gini coefficient measures, an alternate
+measure of well-being is the ability to survive an economic downturn. This,
+after all, is the chief benefit an agent should be able to expect from joining
+a proto: it serves as a kind of insurance policy against future poverty. It is
+therefore interesting to compare the life expectancy of agents who join protos
+with those who do not.
+
+There are many factors at play here, one of which is the level of white noise
+($\sigma^2$) in the agents' income. Figure~\ref{fig:avgLifespanLambda} depicts
+how the life expectancy of isolates and non-isolates depends on $\sigma^2$ for
+two different values of $\lambda$. The top plot shows that for relatively
+stable agent income levels, there is not much difference between the two lines
+-- and hence, not much advantage (or disadvantage) to an agent's joining a
+proto. Interestingly, however, the more volatile the income stream becomes, the
+more benefit there is to pooling resources. The effect is even more pronounced
+with more densely connected graphs, as in the bottom plot: here, when income is
+more noisy, agents who join protos live nearly twice as long as those who
+don't.
+
+% Insert Rajesh's fascinating speculations about why this should be the case.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\columnwidth]{figures/avgLifespanLambda_025.png}
+\includegraphics[width=\columnwidth]{figures/avgLifespanLambda2.png}
+\caption{Life expectancy comparison between isolates (non-proto members) and
+non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
+The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
+constant agent income to a scenario when the noise is as high as the average.}
+\label{fig:avgLifespanLambda}
+\end{figure}
 

### 2019-07-12 manuscript/draftcssa19.tex
Add spot for Will's Gini param sweep plot.
Add life expectancy section.

@@
 
+\label{giniKindaSucks}
 % SD: In light of recent discussions, we may want to downplay Gini and up-play the robustness of agents to exogenous shocks.
@@
 $\texttt{salary} > 0$,
-$m > 0$ (metabolic rate),
-$t_p > 0$ (the ``proto threshold''),
-$\sigma^2 \ge 0$ and
+$0 \le m \le salary$ (metabolic rate),
+$\sigma^2 \ge 0$,
+$t_p > 0$ (the ``proto threshold''), and
 $0 \le \lambda \le 1$:
@@
 
+Importantly, take note that in this simple model, every non-isolate agent (\textit{viz.}, every agent with at least one graph neighbor) will eventually join a proto.
+This is important in the analysis that follows, as we will compare isolates with non-isolates in an attempt to measure the benefits of proto membership.
+
 Various statistical counters are updated as the program executes so that its behavior can be analyzed post mortem.
@@
 
+\section{Verification}
+\input{verification}
+
 \section{Analysis}
-%\input{analysis}
+\input{analysis}
 

### 2019-07-12 manuscript/draftcssa19.tex
this version has bib issues on stephen's entries

--- 2019-07-12 manuscript/draftcssa19.tex
@@
 
-The model is realized in a discrete-time Julia simulation program, in which each particle (agent) is represented as a mutable struct that maintains that agent's state over time.
-Each agent's state includes its current amount of wealth and which proto (if any) it is a member of.
+%The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state.
+An agent's state includes its current amount of wealth and which proto (if any) it is a member of.
 Additionally, using the LightGraphs package~\cite{LightGraphs-2017}, each agent is associated with a node of a randomly generated ER graph.
 Protos are also represented as mutable structs, each of which contains a list of member agent IDs and a current wealth balance.
+%
+%The simulation proceeds as follows. For configurable parameters
+%$N > 0$,
+%$\texttt{init\_max} > 0$,
+%$\texttt{salary} > 0$,
+%$m > 0$ (metabolic rate),
+%$t_p > 0$ (the ``proto threshold''),
+%$\sigma^2 \ge 0$ and
+%$0 \le \lambda \le 1$:
+%
+%\begin{enumerate}
+%\itemsep.1em
+%\item Create $N$ agents, each with a random initial wealth (uniformly distributed from 0 to \texttt{init\_max}), and related to one another as per a random ER network with parameter $\lambda$.
+%\item \textbf{Stages 1 and 2\footnote{We define ``Stage 1'' as the period \textit{before} the first proto is formed, ``Stage 2'' as the period \textit{during} which protos are being formed}:} Repeat until all non-isolate agents\footnote{An \textbf{isolate} agent is one with no graph neighbors.} are members of a proto:
+%    \begin{enumerate}
+%    \itemsep.1em
+%    \item Each agent $A$ whose current wealth $\ge t_p$, and who is not currently a member of a proto, chooses at random one of its graph neighbors (call it $B$) whose wealth \textit{also} exceeds $t_p$.
+(If there are no such neighbors, proceed to the next agent.) If $B$ is already in a proto, have $A$ join $B$'s proto.
+If not, have $A$ and $B$ form a new proto.
+%    \item Each agent gains an amount of wealth equal to $(\texttt{salary} - m + \epsilon)$, where $\epsilon \sim \mathcal{N}(0,\sigma^2)$ (white noise).\footnote{Note that this ``gain'' could be negative, in which case the agent, and possibly its proto, may be subject to death exactly as in step (3).}
+%    \item Each agent \textit{that is in a proto} donates all its wealth in excess of $t_p$ to that proto's balance. (Agents not in a proto maintain their current wealth.)
+%    \end{enumerate}
+%    \item \textbf{Stage 3 (starvation):} Repeat until all agents are dead:
+%        \begin{enumerate}
+%        \itemsep.1em
+%        \item Each agent \textit{loses} an amount of wealth equal to $(m + \epsilon), \epsilon \sim \mathcal{N}(0,\sigma^2)$.
+%        \item If an agent's wealth would drop below zero as a result of this loss, and if it is not a member of a proto, it dies and is removed from the simulation.
+If it \textit{is} a member of a proto, it withdraws the necessary amount from its proto's balance to remain at zero wealth.
+If the proto does not have sufficient funds to cover the loss, both the agent and the proto die and are removed from the simulation.
+%        \end{enumerate}
+%\end{enumerate}
+%
+%Various statistical counters are updated as the program executes so that its behavior can be analyzed post mortem.
+The main simulation loop can also be invoked from a ``parameter sweep'' program which executes it multiple times over a range of parameter values, in order to determine how the model's behavior changes in response to key parameters.
 
-% cite Bootstrap?
-We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).
+%% cite Bootstrap?
+%We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).
 Additionally, Julia easily allows the programmer to invoke code from R packages when necessary, as we did for Gini coefficient calculation with the R package DescTools~\cite{DescTools-2019}.
 
+\section{Verification}
+\input{verification}
+
 \section{Analysis}
-%\input{analysis}
+\input{analysis}
 

### 2019-07-13 manuscript/analysis.tex
gini analysis

--- 2019-07-12 manuscript/analysis.tex
@@
+Figure~\ref{fig:giniHistory}
+
 \subsection{Gini coefficient}
 
-% Will's text and plot showing Gini coefficient (pre-stage-3) decreases with λ
+    The Gini coefficient  of the agent population as seen in the top plot is influenced by two distinct dynamics: loss/accumulation of wealth and the formation/death of proto-institutions.
+Over the course of Stage 1 and the beginning of Stage 3, this change in agent wealth is exclusively responsible for changes in the Gini coefficient .
+As agents accumulate wealth over Stage 1 and 2, the size of wealth differentials shrinks relative to absolute agent wealth, leading to the declining Gini coefficient .
+The opposite effect occurs during Stage 3 as agent starvation leads to the relative growth of these wealth differentials.
+The variability in starvation rates further contributes to the increasing Gini coefficient .
 
+    In addition, the proto-institution formation and proto-institution death respectively, indicated by the bottom plot, influence the Gini coefficient  during Stage 2 and the end of Stage 3.
+As expected, the formation of proto-institutions during Stage 2 contributes to declining Gini coefficient  as the constituent agents of each proto-institution have equivalent wealth values and represent coalitions of perfect economic equality.
+Accordingly, the death of proto-institutions, beginning around Iteration 20, contributes to increase the Gini coefficient by removing the proto-institution’s diminishing effect on the system’s inequality.
+
+Note: As the population size decreases over the starvation period the Gini coefficient  becomes increasingly unstable and susceptible to fluctuations in agent wealth.
 \subsection{Life expectancy}

### 2019-07-13 manuscript/verification.tex
Gini analysis and verification

@@
 simulation parameters were used as in Figures~\ref{fig:singleRun} and
-\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.)}
+\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.) The light
+blue band represents a bootstrapped 95\% confidence interval.}
 \label{fig:giniHistory}
 \end{figure}
+The Gini index of the agent population as seen in the top graph is influenced by two distinct dynamics: loss/accumulation of wealth and the formation/death of proto-institutions.
+Over the course of Stage 1 and the beginning of Stage 3, this change in agent wealth is exclusively responsible for changes in the Gini index.
+As agents accumulate wealth over Stage 1 and 2, the size of wealth differentials shrinks relative to absolute agent wealth, leading to the declining Gini index.
+The opposite effect occurs during Stage 3 as agent starvation leads to the relative growth of these wealth differentials.
+The variability in starvation rates further contributes to the increasing Gini index.
+In addition, the proto-institution formation and proto-institution death respectively, indicated by the bottom graph, influence the Gini index during Stage 2 and the end of Stage 3.
+As expected, the formation of proto-institutions during Stage 2 contributes to declining Gini index as the constituent agents of each proto-institution have equivalent wealth values and represent coalitions of perfect economic equality.
+Accordingly, the death of proto-institutions, beginning around Iteration 20, contributes to increase the Gini coefficient by removing the on the system’s inequality.
+Note: As the population size decreases over the starvation period the Gini index becomes increasingly unstable and susceptible to fluctuations in agent wealth.

### 2019-07-13 manuscript/verification.tex
Gini manuscript updates

--- 2019-07-12 manuscript/verification.tex
@@
 simulation parameters were used as in Figures~\ref{fig:singleRun} and
-\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.)}
+\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.) The light
+blue band represents a bootstrapped 95\% confidence interval.}
 \label{fig:giniHistory}
 \end{figure}
+    The Gini coefficient of the agent population as seen in the 3.2(1) is influenced by two distinct dynamics: loss/accumulation of wealth and the formation/death of proto-institutions.
+Over the course of Stage 1 and the beginning of Stage 3, this change in agent wealth is exclusively responsible for changes in the Gini coefficient.
+As agents accumulate wealth over Stage 1 and 2, the size of wealth differentials shrinks relative to absolute agent wealth, leading to the declining Gini coefficient.
+The opposite effect occurs during Stage 3 as agent starvation leads to the relative growth of these wealth differentials.
+The variability in starvation rates further contributes to the increasing Gini coefficient.
+
+    In addition, the proto-institution formation and proto-institution death respectively, indicated by the 3.2(2), also influence the Gini coefficient during Stage 2 and the end of Stage 3.
+As expected, the formation of proto-institutions during Stage 2 contributes to declining Gini coefficient as the constituent agents of each proto-institution have equivalent wealth values and represent coalitions of perfect economic equality.
+Accordingly, the death of proto-institutions, beginning around Iteration 20, contributes to increase the Gini coefficient by removing the proto-institution’s effect on the system’s inequality.
+
+    Note: As the population size decreases over the starvation period the Gini coefficient becomes increasingly unstable and susceptible to fluctuations in agent wealth.

### 2019-07-13 src/net/confirm.jl
Write lifespan comparison results to file.

@@ -2,10 +2,11 @@
 # Confirm/deny the hypothesis that life expectancy (mean and stdev) of isolates
 #   and non-isolates are *not* different, across a range of parameter settings.
 
+using CSV
 include("sim.jl")
 include("analysis.jl")
 
-λs = [ .1, .5, 1.0, 2.0, 6.0 ]
+λs = [ .1, .5, 1.0, 2.0, 5.0 ]
 wn_intensities = [ 1, 10, 25 ]
 salaries = [ 10, 40 ]
 
@@ -16,6 +17,7 @@ comparison_results = DataFrame(
     p_value=Float16[],
 )
 
+params[:N] = 500
 params[:make_anims] = false
 params[:make_sim_plots] = false
 
@@ -38,3 +40,11 @@ for λ in λs
         end
     end
 end
+
+comparison_results[:sig] = comparison_results[:p_value] .<=.05
+CSV.write("$(tempdir())/isolVsNonisol.csv")
+
+for var in [ :λ, :wn_intensity, :salary ]
+    println(sort(by(comparison_results, [var, :sig], nrow), [var, order(:sig, rev=true)]))
+end
+

### 2019-07-13 src/net/param_sweep.jl
(Add breadcrumbs for param sweep.)

@@ -81,7 +81,10 @@ function param_sweeper(; additional_params...)
     params[:make_sim_plots] = false  # We would never want this true for a sweep
 
     for i = 1:num_values
+        prc("$(i) of $(num_values) values.\n")
+        prc("  $(trials_per_value) trials: ")
         for j = 1:trials_per_value
+            prc("$(j).")
             #setting the random seed and adding it to the DataFrame of the final gini of each simulation
             Random.seed!(params[:random_seed])
 
@@ -128,6 +131,7 @@ function param_sweeper(; additional_params...)
         end
         params[:random_seed]=original_seed
         counter += (end_value-start_value)/num_values
+        prc("\n")
     end
     sim_tag=0
 

### 2019-07-13 src/net/sim.jl
Don't break sim of no isos (or all isos).

@@ -839,5 +839,6 @@ function compute_avg_lifespan(life_history)
         for aid ∈  nonisol_ids]
     prd("isol lifespans are $(isol_lifespans)")
     prd("non-isol lifespans are $(nonisol_lifespans)")
-    return [ mean(isol_lifespans), mean(nonisol_lifespans) ]
+    return [ length(isol_lifespans) > 0 ? mean(isol_lifespans) : 0,
+             length(nonisol_lifespans) > 0 ? mean(nonisol_lifespans) : 0 ]
 end

### 2019-07-13 manuscript/draftcssa19.tex

--- 2019-07-12 manuscript/draftcssa19.tex
@@
 Our model achieves agent interaction by postulating a static network structure which partially mixes the agents.
+Of primary interest is whether network effects alone can generate and sustain differences in economic outcomes of otherwise homogeneous agents.
 
@@
 We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models, with no detailed empirical grounding, but with the potential to generate realistic looking inequality distributions.
-In doing so, we aspire to shed light on the \textit{true} social and economic mechanisms underlying the genesis and persistence of economic inequality.
+In doing so, we aspire to shed light on the \textit{true} social and economic mechanisms underlying the genesis and persistence of economic inequality, and network structure alone can produce large differences in economic outcomes.
 
@@
 
+Two categories of questions
+
 ~\cite{redner2001guide} ~\cite{rv}  ~\cite{wilhite} ~\cite{arthur}
@@
 \subsection{Implementation}
+
+The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state.
+An agent's state includes its current amount of wealth and which proto (if any) it is a member of.
+Additionally, using the LightGraphs package~\cite{LightGraphs-2017}, each agent is associated with a node of a randomly generated ER graph.
+Protos are also represented as mutable structs, each of which contains a list of member agent IDs and a current wealth balance.
+
+The simulation proceeds as follows. For configurable parameters
+$N > 0$,
+$\texttt{init\_max} > 0$,
+$\texttt{salary} > 0$,
+$m > 0$ (metabolic rate),
+$t_p > 0$ (the ``proto threshold''),
+$\sigma^2 \ge 0$ and
+$0 \le \lambda \le 1$:
+
+\begin{enumerate}
+\itemsep.1em
+\item Create $N$ agents, each with a random initial wealth (uniformly distributed from 0 to \texttt{init\_max}), and related to one another as per a random ER network with parameter $\lambda$.
+\item \textbf{Stages 1 and 2\footnote{We define ``Stage 1'' as the period \textit{before} the first proto is formed, ``Stage 2'' as the period \textit{during} which protos are being formed}:} Repeat until all non-isolate agents\footnote{An \textbf{isolate} agent is one with no graph neighbors.} are members of a proto:
+    \begin{enumerate}
+    \itemsep.1em
+    \item Each agent $A$ whose current wealth $\ge t_p$, and who is not currently a member of a proto, chooses at random one of its graph neighbors (call it $B$) whose wealth \textit{also} exceeds $t_p$.
+(If there are no such neighbors, proceed to the next agent.) If $B$ is already in a proto, have $A$ join $B$'s proto.
+If not, have $A$ and $B$ form a new proto.
+    \item Each agent gains an amount of wealth equal to $(\texttt{salary} - m + \epsilon)$, where $\epsilon \sim \mathcal{N}(0,\sigma^2)$ (white noise).\footnote{Note that this ``gain'' could be negative, in which case the agent, and possibly its proto, may be subject to death exactly as in step (3).}
+    \item Each agent \textit{that is in a proto} donates all its wealth in excess of $t_p$ to that proto's balance. (Agents not in a proto maintain their current wealth.)
+    \end{enumerate}
+    \item \textbf{Stage 3 (starvation):} Repeat until all agents are dead:
+        \begin{enumerate}
+        \itemsep.1em
+        \item Each agent \textit{loses} an amount of wealth equal to $(m + \epsilon), \epsilon \sim \mathcal{N}(0,\sigma^2)$.
+        \item If an agent's wealth would drop below zero as a result of this loss, and if it is not a member of a proto, it dies and is removed from the simulation.
+If it \textit{is} a member of a proto, it withdraws the necessary amount from its proto's balance to remain at zero wealth.
+If the proto does not have sufficient funds to cover the loss, both the agent and the proto die and are removed from the simulation.
+        \end{enumerate}
+\end{enumerate}
+
+Various statistical counters are updated as the program executes so that its behavior can be analyzed post mortem.
+The main simulation loop can also be invoked from a ``parameter sweep'' program which executes it multiple times over a range of parameter values, in order to determine how the model's behavior changes in response to key parameters.
+
+% cite Bootstrap?
+We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).
+Additionally, Julia easily allows the programmer to invoke code from R packages when necessary, as we did for Gini coefficient calculation with the R package DescTools~\cite{DescTools-2019}.
 

### 2019-07-13 manuscript/draftcssa19.tex
Remove duplicated section 2.1.

@@
 
-The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state.
-An agent's state includes its current amount of wealth and which proto (if any) it is a member of.
-Additionally, using the LightGraphs package~\cite{LightGraphs-2017}, each agent is associated with a node of a randomly generated ER graph.
-Protos are also represented as mutable structs, each of which contains a list of member agent IDs and a current wealth balance.
-
-The simulation proceeds as follows. For configurable parameters
-$N > 0$,
-$\texttt{init\_max} > 0$,
-$\texttt{salary} > 0$,
-$0 \le m \le salary$ (metabolic rate),
-$\sigma^2 \ge 0$,
-$t_p > 0$ (the ``proto threshold''), and
-$0 \le \lambda \le 1$:
-
-\begin{enumerate}
-\itemsep.1em
-\item Create $N$ agents, each with a random initial wealth (uniformly distributed from 0 to \texttt{init\_max}), and related to one another as per a random ER network with parameter $\lambda$.
-\item \textbf{Stages 1 and 2\footnote{We define ``Stage 1'' as the period \textit{before} the first proto is formed, ``Stage 2'' as the period \textit{during} which protos are being formed}:} Repeat until all non-isolate agents\footnote{An \textbf{isolate} agent is one with no graph neighbors.} are members of a proto:
-    \begin{enumerate}
-    \itemsep.1em
-    \item Each agent $A$ whose current wealth $\ge t_p$, and who is not currently a member of a proto, chooses at random one of its graph neighbors (call it $B$) whose wealth \textit{also} exceeds $t_p$.
-(If there are no such neighbors, proceed to the next agent.) If $B$ is already in a proto, have $A$ join $B$'s proto.
-If not, have $A$ and $B$ form a new proto.
-    \item Each agent gains an amount of wealth equal to $(\texttt{salary} - m + \epsilon)$, where $\epsilon \sim \mathcal{N}(0,\sigma^2)$ (white noise).\footnote{Note that this ``gain'' could be negative, in which case the agent, and possibly its proto, may be subject to death exactly as in step (3).}
-    \item Each agent \textit{that is in a proto} donates all its wealth in excess of $t_p$ to that proto's balance. (Agents not in a proto maintain their current wealth.)
-    \end{enumerate}
-    \item \textbf{Stage 3 (starvation):} Repeat until all agents are dead:
-        \begin{enumerate}
-        \itemsep.1em
-        \item Each agent \textit{loses} an amount of wealth equal to $(m + \epsilon), \epsilon \sim \mathcal{N}(0,\sigma^2)$.
-        \item If an agent's wealth would drop below zero as a result of this loss, and if it is not a member of a proto, it dies and is removed from the simulation.
-If it \textit{is} a member of a proto, it withdraws the necessary amount from its proto's balance to remain at zero wealth.
-If the proto does not have sufficient funds to cover the loss, both the agent and the proto die and are removed from the simulation.
-        \end{enumerate}
-\end{enumerate}
-
-Importantly, take note that in this simple model, every non-isolate agent (\textit{viz.}, every agent with at least one graph neighbor) will eventually join a proto.
-This is important in the analysis that follows, as we will compare isolates with non-isolates in an attempt to measure the benefits of proto membership.
-
-Various statistical counters are updated as the program executes so that its behavior can be analyzed post mortem.
-The main simulation loop can also be invoked from a ``parameter sweep'' program which executes it multiple times over a range of parameter values, in order to determine how the model's behavior changes in response to key parameters.
-
-% cite Bootstrap?
-We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).
-Additionally, Julia easily allows the programmer to invoke code from R packages when necessary, as we did for Gini coefficient calculation with the R package DescTools~\cite{DescTools-2019}.
-
 \section{Verification}

### 2019-07-13 manuscript/verification.tex
Add Figure references; wordsmith.

--- 2019-07-12 manuscript/verification.tex
@@
 simulation parameters were used as in Figures~\ref{fig:singleRun} and
-\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.)}
+\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.) The light
+blue band represents a bootstrapped 95\% confidence interval.}
 \label{fig:giniHistory}
 \end{figure}
+
+    The Gini coefficient of the agent population as seen in the top plot of Figure~\ref{fig:giniHistory} is influenced by two distinct dynamics: loss/accumulation of wealth and the formation/death of proto-institutions.
+Over the course of Stage 1 and the beginning of Stage 3, this change in agent wealth is exclusively responsible for changes in the Gini coefficient.
+As agents accumulate wealth over Stage 1 and 2, the size of wealth differentials shrinks relative to absolute agent wealth, leading to the declining Gini coefficient.
+The opposite effect occurs during Stage 3 as agent starvation leads to the relative growth of these wealth differentials.
+The variability in starvation rates further contributes to the increasing Gini coefficient.
+
+    In addition, as indicated in the bottom plot, the proto formation and proto death also influence the Gini coefficient during Stage 2 and the end of Stage 3, respectively.
+As expected, the formation of protos during Stage 2 contributes to declining Gini coefficient as the constituent agents of each proto have equivalent wealth values and represent coalitions of perfect economic equality.
+Accordingly, the death of protos, beginning around Iteration 20, contributes to increase the Gini coefficient by removing the protos' effect on the system's inequality.
+
+    (Note: As the population size decreases over the starvation period, the Gini coefficient becomes increasingly unstable and susceptible to small fluctuations in agent wealth; hence the erratic nature of the red line at the extreme right of Figure~\ref{fig:giniHistory}.)
+
+% vim:textwidth=99999

### 2019-07-14 manuscript/draftcssa19.tex
section 2 completed

@@
 The current work originated in our attempts to incorporate and tease out the effects of social structures in simple models of wealth dynamics in the presence of environmental stochasticity, and a simple form of resource pooling.
+Specifically, we are interested in studying how structure and dynamics interact to produce and sustain inequality, and influence robustness to scarcity shocks.
+We answer the former question using Gini coefficients; the latter question is answered using survival time type analysis.
+As we discuss in section 3, while Gini was found to be of limited value, survival time analysis produced more insights on both questions of inequality and robustness.
+
 These models were inspired by our search for analogs of the grid world agent-based models (ABMs) of Friesen and Mudigonda~\cite{srimil} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
@@
 % SD: In light of recent discussions, we may want to downplay Gini and up-play the robustness of agents to exogenous shocks.
-The phenomenon under scrutiny is the emergence and evolution of economic inequality in societies with non-trivial social structures.
+The phenomenon under scrutiny is the emergence and evolution of economic inequality in societies with non-trivial social structures that enable economic interactions and cooperation mechanisms.
 The model we use to answer questions surrounding this phenomenon must possess a dynamic model of wealth accumulation, a model of social structure, and a suitably useful measure of inequality.
 The dynamics are modeled as Brownian noise driven linear dynamical systems, here constant growth rate; the structure is modeled by networks, here random graphs; the measures of inequality used are Gini coefficients, and survival time distributions of agents in response to lack of resources.
-Although both the dynamical system and the network model are quite well understood, the precise interplay of structure and dynamics produces interesting emergent wealth distributions.
+Although both the dynamical system and the network model are quite well understood, the precise interplay of structure and dynamics produces interesting emergent wealth distributions and robustness to scarcity.
 To the best of our knowledge, this specific combination of network structure and social dynamics has not been discussed in the computational social science (CSS) or mathematical sociology literature, and we consider this the primary contribution of this work.
@@
 
-Two categories of questions
+The questions of interest to us, emergence and persistence of inequality and robustness to scarcity, in the presence of social structure and uncertain environmental conditions, map onto questions about the stochastic dynamical system (SDS).
+Inequality can be quantified using Gini coefficients of the particle ensemble's state space.
+Robustness to scarcity can be measured using survival time analysis for the particles to reach the absorbing boundary at the origin, by turning off the appropriate drift terms in the dynamics.
 
-~\cite{redner2001guide} ~\cite{rv}  ~\cite{wilhite} ~\cite{arthur}
+\subsection{Mathematical formulation}
+The discussion of SDS closely follows ~\cite{redner2001guide}\footnote{The use of such analysis for studying wealth dynamics was presented by one of the authors at CSSA18 ~\cite{rv}.
+Unlike the finite interval dynamics used there, the dynamics here take place on a semi-infinite line.}
+
+The SDS can be defined through a stochastic differential equation of the form
+
+\begin{equation}\label{ddm}
+dx(t) = vdt + \sqrt{2D} dw
+\end{equation}
+
+\noindent where $v$ is the wealth growth rate (the difference of the income and metabolic rate of the agent) and $D$ is the intensity of the Brownian process (white noise process) $w$.
+$x(t)$ is the state of the particle (wealth) at time $t$.
+The dynamics can be started at a any initial point $x_0 > 0$.
+
+While equation (\ref{ddm}), in its discretized form, is the basis for simulations, other formulations are used~\cite{redner2001guide,rv}\footnote{These formulations make use measure theoretical probability to convert SDEs to partial differential equations known as Fokker-Planck equations.
+The provide numerical and closed form estimates of probability density, survival time probabilities and other quantities of importance.}.
+
+\noindent For a single particle, the probability of survival $S(t)$ and the expected probability of reaching the origin can be calculated and are functions of $x_0$, $v$ and $D$.
+For example, the expected probability of a particle reaching the origin ($\mathcal{E}(x_0)$), when starting at $x_0$ is given by
+
+\begin{equation}\label{e}
+\mathcal{E}(x_0) = \begin{cases}
+e^{-v x_0/D} \text{, } & \text{ for } v > 0 \\
+1 \text{, } & \text{ for } v \leq 0 \\
+\end{cases}
+\end{equation}
+
+\noindent That is, there is always a non-zero probability of reaching the particle, even when there is a constant positive drift away from the origin; and, the return to origin is certain for negative or zero drift.
+Similarly, survival probability, $\mathcal{S}(t)$ is given by
+
+\begin{equation}\label{s}
+\mathcal{S}(t) = \begin{cases}
+1 - e^{-v x_0/D}\text{, } & \text{ } v >0 \\
+\sqrt{\frac{4D}{\pi v^2 t} e^{-v^2 t/4 D}}\text{, } & \text{ } v \leq 0 \\
+\end{cases}
+\end{equation}
+
+Since the particles are independent, they are independent dynamical systems; proto formation is a higher level construct imposed on this system and is a constraint on what states are considered viable and what are not.
+Consider two particles $x_1$ and  $x_2$ that have crossed the threshold for coalescence $x_{thresh}$.
+After the coalescence event, the state (wealth) of individual particles $x_1(t)$ and  $x_2(t)$ is not important; only the aggregate wealth of the coalescent (proto) is important.
+As long as $x_1(t) + x_2(t) >0$, both particles survive.
+Effectively, the proto is a two-dimensional SDS.
+Since the wealth of the proto ($p_{12}$)is additive, the aggregate wealth $p_{12} = x_1(t) + x_2(t) $.
+The dynamical variable satisfies an SDE\footnote{The result follows from the additivity properties of white noise.}
+
+\begin{equation}\label{pddm}
+dx(t) = 2vdt + \sqrt{2*2D} dw
+\end{equation}
+
+As one can see, only the coefficient of drift and diffusion in equations (\ref{ddm}) and (\ref{pddm}) are different.
+So, the corresponding expressions for $\mathcal{E}(x_0)$ and $\mathcal{S}(t)$ are suitably scaled.
+This has implications for both Gini coefficient calculations and survival analysis calculations.
+
+For such ensemble of particles, the primary driver of difference in paths (life histories) and wealth is the Brownian noise intensity $D$; greater the $D$.
+greater the diversity (and hence Gini).
+However, Gini is a measure that is dependent on absolute magnitude.
+So,  if the drift ($v$) is large, then the variation generated by
+$D$ gets washed out by $v$\footnote{Preliminary investigations suggest that for simple non-network ensembles, Gini either stays close to $0$ or $1$.
+We suspect that this is because of the constant wealth growth rate used in our models, Gini is a partially useful measure.
+This is unlike in macroeconomic models where exponential growth rate gives rise a appearance of non-trivial Gini coefficients}.
+On the other hand, the mathematical form of expressions for $\mathcal{S}(t)$ suggest a clear and non-trivial dependence of the $D$ and clear separation between the population of particles that are isolates and the population of particles that are in a proto.
+
+As the equations (\ref{e}) and (\ref{s}) show, all agents, irrespective of their starting intial condition and luck have a non-zero probability of dying.
+The paper that inspired this work ~\cite{srimil} emphasized studied inequality dynamics in the context of extreme scarcity in their foraging world.
+One can mimic this scarcity by simply turning of the income, leaving the agents to all inevitably die.
+The differential rate of death of the isolates and the non-isolates then become an important quantity.
+
+In the simulation experiments that we discuss next discusses various stages and stopping conditions.
+All these stages and transition times between them make sense in terms of the underlying dynamics of the particle ensemble.
+In each of the stages, the effective dynamics are different from each other but the form of the equations remain the same.
+
+To break the homogeneity of this particle ensemble, we propose to let the particles interact with only  a random subset of other populations.
+In other words, we embed the particles on a network (graph); particles interact (form proto) with only their neighbors.
+In this work, we focus on the simplest \textit{textbook} example of network: Erd\H{o}s-R\'{e}nyi network model~\cite{newman2018networks}.
+ER models has only one parameter $\lambda$, a Poisson parameter that determines the density of connections in the network, and in this setting, determines the number of particles available for a particle to coalesce and form protos.
+Commonsense reasoning suggests that a larger $\lambda$ parameter may help increase the average lifetimes of individual agents through by enabling greater likelihood of contact with other particles.
+
+Just as equations (\ref{e}) and (\ref{s}) offers insight about the role of dynamics, the key feature of ER models is the the formation of giant component at $\lambda=1$, allowing a finite fraction of the population to be connected, have cliques of very high order, and other useful properties guarantee proto formation in large fraction of the population.
+
+As its network properties are well-understood, wealth dynamics on such network allows us to understand more thoroughly, the interaction between dynamics and structure, and its role in global behavior.
+Still, a full analysis of this model remains to be completed and is part of a forthcoming work involving other more expressive network models.
+As we note subsequently, even this simple setting offers interesting insights,
 
@@
 
-The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state.
+%The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state.
 An agent's state includes its current amount of wealth and which proto (if any) it is a member of.
@@
 % cite Bootstrap?
-We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).
+%We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).
 Additionally, Julia easily allows the programmer to invoke code from R packages when necessary, as we did for Gini coefficient calculation with the R package DescTools~\cite{DescTools-2019}.

### 2019-07-14 manuscript/draftcssa19.tex
section 2 completed

@@
 
-%The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state.
+The model is realized in a discrete-time Julia simulation program, in which each agent is represented as a mutable struct (a dedicated area of memory whose contents change over time) that maintains its state.
 An agent's state includes its current amount of wealth and which proto (if any) it is a member of.
@@
 % cite Bootstrap?
-%We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).
+We chose Julia for its flexible type system, its speed of execution, its ease of programming, and the availability of useful packages, such as LightGraphs, Gadfly~\cite{Gadfly-2018} (plotting), and Bootstrap (confidence intervals).
 Additionally, Julia easily allows the programmer to invoke code from R packages when necessary, as we did for Gini coefficient calculation with the R package DescTools~\cite{DescTools-2019}.

### 2019-07-14 manuscript/analysis.tex
Upgrade figure 4 to 500 agents.

--- 2019-07-12 manuscript/analysis.tex
@@
 
-As mentioned in Section~\ref{giniKindaSucks}, the Gini coefficient is not the
-ideal measure of inequality for our apocalyptic model. Nonetheless, it is
-illustrative to see how it varies with respect to the ER $\lambda$ parameter.
-Figure~\ref{fig:giniVsLambda} depicts the Gini computed \textit{at the onset
-of stage 3} (before starvation) versus $\lambda$, and confirms that...
-% Will, finish this paragraph.
+As mentioned in Section~\ref{giniKindaSucks}, the Gini coefficient is not the ideal measure of inequality for our apocalyptic model.
+Nonetheless, it is illustrative to see how it varies with respect to the ER $\lambda$ parameter.
+Figure~\ref{fig:giniVsLambda} depicts the Gini computed \textit{at the onset of stage 3} (before starvation) versus $\lambda$, and confirms that increasing $\lambda$ leads to a decreasing Gini coefficient.
+Increasing $\lambda$ fosters wealth uniformity through the increased formation of and growth in size of protos.
+Firstly, a higher percentage of agents join a proto as greater $\lambda$ values lead to fewer isolate agents in the ER network.
+As more agents join protos, differences in agent wealth are eliminated as each proto establishes perfect equality amongst its constituent agents, thereby lowering system's overall inequality.
+Secondly, higher $\lambda$ values lead to larger average proto sizes, as more densely-connected networks increase the likelihood that an agent will join an existing proto rather than form a new one.
+In much the same way, as smaller protos coalesce into larger ones, the standard inequality between the fragmented protos is eliminated in favor of perfect equality across the larger proto, resulting in a corresponding decrease in the Gini coefficient.
 
@@
 \caption{The average Gini coefficient, computed before the onset of starvation,
-for various values of the ER $\lambda$ connectivity parameter. The color band
-represents a bootstrapped 95\% confidence interval.}
+for various values of the ER $\lambda$ connectivity parameter. 500 agents were
+used in each simulation. The color band represents a bootstrapped 95\% confidence
+interval.}
 \label{fig:giniVsLambda}
 \end{figure}
-
-% Will's text and plot showing Gini coefficient (pre-stage-3) decreases with λ
 
@@
 % Wealth histogram is steady ?
+% vim:textwidth=99999

### 2019-07-14 src/net/param_sweep.jl
Add a second white noise value to Gini vs λ plot.

@@ -355,7 +355,7 @@ function param_sweeper(; additional_params...)
                                     (params[repeat_param]-repeat_start_value)/2*(repeat_end_value-repeat_start_value)) ))
 
     ginip = draw_plot(plot_df, param_to_sweep, Dict("gini"=>"navy"),
-        y_label="Gini")
+        y_label="Gini", extra=[Guide.title("σ²=$(params[:white_noise_intensity])")])
 
     compp = draw_plot(plot_df, param_to_sweep,
         Dict("number_components"=>"green", "size_largest_component" => "red"),

### 2019-07-15 manuscript/analysis.tex

@@
 \includegraphics[width=\columnwidth]{figures/giniVsLambda.png}
-\caption{The average Gini coefficient, computed before the onset of starvation,
-for various values of the ER $\lambda$ connectivity parameter. 500 agents were
-used in each simulation. The color band represents a bootstrapped 95\% confidence
-interval.}
+\caption{The average Gini coefficient of effective wealth (computed pre-stage 3) for various values of the ER $\lambda$ connectivity parameter, and with both low-noise and high-noise income.
+500 agents were used in each simulation.
+The color band represents a bootstrapped 95\% confidence interval.}
 \label{fig:giniVsLambda}

### 2019-07-17 src/net/param_sweep.jl
Write plot_df file to disk.

@@ -355,7 +355,8 @@ function param_sweeper(; additional_params...)
                                     (params[repeat_param]-repeat_start_value)/2*(repeat_end_value-repeat_start_value)) ))
 
     ginip = draw_plot(plot_df, param_to_sweep, Dict("gini"=>"navy"),
-        y_label="Gini", extra=[Guide.title("σ²=$(params[:white_noise_intensity])")])
+        y_label="Gini", extra=[Guide.title(
+            "White noise (σ²)=$(params[:white_noise_intensity])")])
 
     compp = draw_plot(plot_df, param_to_sweep,
         Dict("number_components"=>"green", "size_largest_component" => "red"),
@@ -422,6 +423,7 @@ function param_sweeper(; additional_params...)
         Guide.xlabel("Agent Wealth"))
     draw(PNG("$(tempdir())/wealth_heatmap.png"), wealth_heatmap)
 
+    CSV.write("$(tempdir())/plot_df.csv",plot_df)
     return Dict(:agent_line_df => agent_line_df,
         :trial_line_df => trial_line_df,
         :plot_df => plot_df)

### 2019-07-17 manuscript/draftcssa19.tex
minor comments in section 5

@@
 \input{analysis}
+%%%%% need to add some speculations and motivate further simulation experiments .... especially what insights were gained by the current simulation model
+\section{Conclusion and Future Work}
+Being one of the first in an ongoing project, the next directions are too many to mention here.
+Still, we mention a few next steps that adheres to the spirit of our project.
+These directions all alleviate some of the obvious limitations of the current work.
 
-\section{Conclusion and Future Work}
+While both the stochastic models and ER models are well understood, proto formation dynamics, as coagulation processes in continuous-time, remain to be better understood, mathematically.
+Also, while the mathematical analysis of dynamics of discrete-time stochastic models on networks are well studied, diffusion processes on networks seem under explored in the literature.
 
+Even with only a few parameters, the simulation results are hard to visualize and interpret.
+As the number of parameters increase, as expected in future models, ideas from design and analysis of (computer) experiments may be required.
+Also, our exploration of the time to death distirbutions of the population show non-trivial stucture.
+More careful statisitcal tests that go beyond the mean analysis presented here are required to tease out the necessary and sufficient conditions for proto population to consistenty out-perform isolate population.
+
+The models used for our simulation are at best \textit{stylized} models of real world social and economic systems, especially in anthropology~\cite{white2011kinship} and historical and urban sociology~\cite{sampson2012great,katz2013people}.
+Research in economic anthropology~\cite{koster2019,koster2014,koster2015,bogerhoff2015,smith2019,nolin2012,power2018cooperation,power2018} suggest complex food aand economic resource sharing rituals among members of various communities.
+Such resource sharing social networks do not look like any of the \textit{textbook} models.
+Extending our analysis to more expressive network models like exponential random graph models, stochastic block models and latent space models is an important research direction.
+This alongside the use of empirically observed cooperation and coordination protocols have potential in making our models better callibrated with real world systems.
+
+Despite their simplicitly, models like the ones constructed here have several advantages.
+As ACE models, they offer insights about economic systems in which majority of the assumptions of neo-classical economics like perfectly mixed agents~\cite{wilhite} and presence of equilibrium~\cite{arthur} do not hold.
+As AS models~\cite{hedstrom2011oxford}, they offer an approach that adds models of social mechanisms to CSS models in a graded manner.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Need to understand the physics of the proto formation better
+%%% Say something about how this work is continues the work original started by Sri Mil
+% SriMil model introduced protos but the mathematical reformulation of proto is insightful not only for our model but also for the rginal SriMil model
+
+%%%Idea for final section as of today 06/13
+
+%%%% Simulations cleary show systematic variations in both inequality and death time as both white noise and network parameter changes....
+the precise interpretation and understanding of the phenomena at a more basic level is underwya..
+more precise statistical tests are required...
+
+%%% Discuss how there are too many things to do along several fronts as this is at the interface of mathematics, simulation, economics and sociogy
+
+% Discuss the importance of simple stylized models for use in computational economics .....
+cite the papers of Testatsion, Wihtle and Arthur...
+tell how simple model provides insight into the economic systems...
+discuss the importance of not having equilibrium assumptions.....
+
+%%% link to the use of these models to tease out actual social mechanisms as is warranted by analytical sociology
+
+%%%% Still, these models, at least the ones planned for the future are ideal for studying economic systems of small scale societies... cite the anthropology work....
+
+%%% cite RV work where the idea of market forces start opearting only after a certain threshold....
+and if everythin is below that threahold, there is no reason to expect that macroeconomic models are useful in any way shape or form
+
+%%%%  Economics of poverty is totally difference and is expected to involve completely different set of models... maybe use ideas from notes below
+
+%%% End with connections to the big SPECSTAR project 
+%%% Major strengths ACE (cite Arthur, Tesfatsion and Wilhite papers), AS (mechanisms fuss) 
+%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%% DO NOT DELETE.... EXPECTED TO BE PART OF THE LARGER JOURNAL MANUSCRIPT 
 %%%Things that could be discussed here but is redundant if we are running out of words 
@@
 %%%%% Use anthropology references to motivate more expressive models
-\cite{power2018cooperation,power2018}
-
-\cite{koster2019,koster2014,koster2015,bogerhoff2015}
-
-\cite{smith2019,nolin2012}
 

### 2019-07-18 manuscript/draftcssa19.tex
Minor edits & grammer fixes

@@
 We study wealth accumulation dynamics in a population of heterogeneously mixed agents with a capacity for a certain primitive form of cooperation enabled by static network structures.
-Despite their simplicity, the stochastic dynamics generate inequalities in wealth reminiscent of real world social systems even in a fully mixed population.
-A simple form of cooperation is introduced and is shown to enhance the viability of agents By embedding such dynamics in a network, the impact of social structures on the origins and persistence of inequality can be teased out easily.
+Despite their simplicity, the stochastic dynamics generate inequalities in wealth reminiscent of real-world social systems even in a fully mixed population.
+A simple form of cooperation is introduced and is shown to enhance the viability of agents by embedding such dynamics in a network; the impact of social structures on the origins and persistence of inequality can be teased out easily.
 The models developed here complement traditional modeling approaches based on grid worlds.
@@
 \section{Introduction}
-In recent years, concerns and debates surrounding wealth inequality and socioeconomic mobility have been one of the few unifying issues dominating the extremely polarized public spheres of the Global North.
-While economic and political inequality used to be discussed in not so mainstream heterodox economics circles, the contentious discussions on the topic within mainstream economics since the publication of Piketty's book~\cite{piketty2017capital} suggests a lack of consensus about very basic foundational questions like the origins and persistence of economic inequality.
+In recent years, the concern and debate regarding wealth inequality and socioeconomic mobility have been one of the few unifying issues dominating the extremely polarized public spheres of the Global North.
+While economic and political inequality used to be discussed in heterodox economics circles, the contentious discussions on the topic within mainstream economics since the publication of Piketty's book~\cite{piketty2017capital} suggest a lack of consensus about basic foundational questions like the origins and persistence of economic inequality.
 Not surprisingly, traditional theories and tools of macro and micro economics are now being diagnosed for their limitations.
-Simultaneously, insights from related disciplines, along with novel scientific inquiry models not usually associated with traditional econometrics, are being taken more seriously.
-The work presented here shares this spirit by integrating substantive ideas from anthropology, economic sociology~\cite{granovetter2017society} and urban sociology~\cite{sampson2012great} and using modeling approaches from computational social science~\cite{hedstrom2018}, computational economics~\cite{tesfatsion} and analytical sociology~\cite{hedstrom2011oxford} to understand the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
+Simultaneously, insights from related disciplines, along with novel models for scientific inquiry not usually associated with traditional econometrics, are being taken more seriously.
+The work presented here shares this spirit by integrating substantive ideas from anthropology, economic sociology~\cite{granovetter2017society} and urban sociology~\cite{sampson2012great} and using modeling approaches from computational social science~\cite{hedstrom2018}, computational economics~\cite{tesfatsion} and analytical sociology~\cite{hedstrom2011oxford} to explore the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
 % SD: citation for "anthropology," the first element of the last sentence's list? Grief and/or White?
@@
 The current work originated in our attempts to incorporate and tease out the effects of social structures in simple models of wealth dynamics in the presence of environmental stochasticity, and a simple form of resource pooling.
-Specifically, we are interested in studying how structure and dynamics interact to produce and sustain inequality, and influence robustness to scarcity shocks.
-We answer the former question using Gini coefficients; the latter question is answered using survival time type analysis.
+Specifically, we are interested in studying how structure and dynamics interact to produce and sustain inequality and to influence robustness to scarcity shocks.
+We answer the former question using Gini coefficients and the latter using survival time type analysis.
 As we discuss in section 3, while Gini was found to be of limited value, survival time analysis produced more insights on both questions of inequality and robustness.
@@
 These models were inspired by our search for analogs of the grid world agent-based models (ABMs) of Friesen and Mudigonda~\cite{srimil} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
-The original model used foraging to mix the population and create opportunities for interaction, and, when certain conditions were met, allowed resource sharing.
+The original model used foraging to mix the population and create opportunities for interaction, and, when certain conditions were met, resource sharing.
 Our model achieves agent interaction by postulating a static network structure which partially mixes the agents.
@@
 The original model drew its inspiration from historical sociology, in Katz's influential study of middle of 19th century Hamilton, Canada~\cite{katz2013people}.
-Retaining this original motivation, we draw additional inspiration from economic sociology, in the work of Granovetter~\cite{granovetter2005}; urban sociology, in the work of Sampson~\cite{sampson2002} and others; and in anthropology, in the work on cooperation in small to medium scale societies~\cite{avner1994,white2011kinship}.
-The geographic and economic scale of the systems, the nature of social actors and time period of interest are all very different from the ones used to develop models of representative agents in macroeconomics~\cite{benhabib2018}, making the similarity between macroeconomic wealth dynamics models and our models not comparable without further justification.
+Retaining this original motivation, we draw additional inspiration from economic sociology in the work of Granovetter~\cite{granovetter2005}; urban sociology, in the work of Sampson~\cite{sampson2002} and others; and in anthropology, in the work on cooperation in small to medium scale societies~\cite{avner1994,white2011kinship}, and others.
+The geographic and economic scale of the systems and the nature of social actors and time period of interest are all very different from the ones used to develop models of representative agents in macroeconomics~\cite{benhabib2018}, making the similarity between macroeconomic wealth dynamics models and our models not comparable without further justification.
 Elaborating on the interplay of conceptual and methodological ideas among these disciplines is beyond the scope of this article.
@@
 
-The important role played by social structures or non-economic structures in determining economic outcomes of individuals in a society is not in doubt~\cite{granovetter2005,jackson_rev2017}.
+The important role played by social structures or non-economic structures in determining economic outcomes of individuals in a society is not in doubt~\cite{granovetter2005, jackson_rev2017}.
 Still, in the absence of a unifying foundation for sociology and economics, the full impact of this two-way interpenetration of economic and social structures is demonstrated only on a case-by-case basis.
@@
 Analytical sociology~\cite{ch1as_hdbk}, with its emphasis on explanation of collective emergent phenomena using mathematically formulated social mechanisms~\cite{ch2as_hdbk,ch11as_hdbk} anchored at the individual level, is an ideal candidate for this purpose.
-It is particularly powerful when combined with computational simulation, because when mathematically-formulated models reach even a modest level of complexity, they often become analytically intractable.
+It is particularly powerful when combined with computational simulation, because when mathematically formulated models reach even a modest level of complexity, they often become analytically intractable.
 Simulation \textit{in silico} can yield approximate results for these more complex scenarios, which supplement the exact results reached by traditional methods.
@@
 The model we use to answer questions surrounding this phenomenon must possess a dynamic model of wealth accumulation, a model of social structure, and a suitably useful measure of inequality.
-The dynamics are modeled as Brownian noise driven linear dynamical systems, here constant growth rate; the structure is modeled by networks, here random graphs; the measures of inequality used are Gini coefficients, and survival time distributions of agents in response to lack of resources.
+The dynamics are modeled as Brownian-noise-driven linear dynamical systems, here with constant growth rate; the structure is modeled by networks, here with random graphs; the measures of inequality used are Gini coefficients, and survival time distributions of agents in response to lack of resources.
 Although both the dynamical system and the network model are quite well understood, the precise interplay of structure and dynamics produces interesting emergent wealth distributions and robustness to scarcity.
@@
 In the next section, we discuss the mathematical formulation of the model.
-In section 3, we present the analysis of our simulation experiments, summarize key findings and discuss why we chose the \texttt{julia} programming language~\cite{Julia-2017} for our implementation.
-In section 4, we discuss the limitations of our simple models, extensions to dynamics and networks more expressive than the ones presented here, and planned future work.
+In section 3, we present the analysis of our simulation experiments, summarize key findings, and discuss why we chose the \texttt{julia} programming language~\cite{Julia-2017} for our implementation.
+In section 4, we discuss the limitations of our simple models, extensions to dynamics and networks more expressive than the ones presented here and planned future work.
 
-Before discussing our model in greater mathematical detail, we discuss the model qualitatively, contrasting them with more familiar modeling approaches.
-The model presented here has much in common with models used in social reality inspired models in statistical physics~\cite{redner2001guide}, dynamic process models in network science~\cite{newman2018networks}, and computational social science and agent-based models~\cite{abm_review}; however, our modeling philosophy is somewhere at the interface of agent-based computational economics (ACE)~\cite{tesfatsion} and analytical sociology (AS)~\cite{ch1as_hdbk,ch2as_hdbk}.
+Before discussing our model in greater mathematical detail, we discuss the model qualitatively, contrasting it with more familiar modeling approaches.
+The model presented here has much in common with models used in social-reality-inspired models in statistical physics~\cite{redner2001guide}, dynamic process models in network science~\cite{newman2018networks}, and computational social science and agent-based models~\cite{abm_review}; however, our modeling philosophy is somewhere at the interface of agent-based computational economics (ACE)~\cite{tesfatsion} and analytical sociology (AS)~\cite{ch1as_hdbk,ch2as_hdbk}.
 In ACE, we acknowledge its aspiration to develop bottom-up models of economic systems at all scales but restrain from its enthusiastic use of complex but well-calibrated detailed models of markets and agents~\cite{tesfatsion2017}.
@@
 
-More specifically, from statistical physics, we borrow the dynamics: diffusion models and associated first-passage time techniques; from network science, we borrow the structural aspects: Erd\H{o}s-R\'{e}nyi network (ER) models; and from non-equlibrium statistical physics, CSS and ACE, we borrow a form of cooperation: the concept of coalescence, institution and coordination.
+More specifically, from statistical physics, we borrow the dynamics: diffusion models and associated first-passage time techniques; from network science, we borrow the structural aspects: Erd\H{o}s-R\'{e}nyi network (ER) models; and from non-equilibrium statistical physics, CSS and ACE, we borrow a form of cooperation: the concept of coalescence, institution and coordination.
 
@@
 The model of cooperative wealth accumulation constructed here is best thought of as a stochastic interacting particle system infused with economic sociological semantics.
-The particle evolves according to an one dimensional diffusion process with constant drift and is driven by a Brownian noise with boundary condition at the origin corresponding to particle absorption.
+The particle evolves according to a one dimensional diffusion process with constant drift and is driven by a Brownian noise with a boundary condition at the origin corresponding to particle absorption.
 After crossing a pre-determined threshold in state space, particles above the threshold follow a protocol and coalesce together.
@@
 %Might be nice to put a nice table here 
-The one dimensional state space of the particle is identified with the wealth of an social actor (agent).
+The one-dimensional state space of the particle is identified with the wealth of a social actor (agent).
 We consider a homogeneous population where all agents are required burn their wealth at a constant specified rate in order to survive.
@@
 Inequality can be quantified using Gini coefficients of the particle ensemble's state space.
-Robustness to scarcity can be measured using survival time analysis for the particles to reach the absorbing boundary at the origin, by turning off the appropriate drift terms in the dynamics.
+Robustness to scarcity can be measured using survival time analysis for the particles to reach the absorbing boundary at the origin by turning off the appropriate drift terms in the dynamics.
 
@@
 $x(t)$ is the state of the particle (wealth) at time $t$.
-The dynamics can be started at a any initial point $x_0 > 0$.
+The dynamics can be started at any initial point $x_0 > 0$.
 
@@
 
-Since the particles are independent, they are independent dynamical systems; proto formation is a higher level construct imposed on this system and is a constraint on what states are considered viable and what are not.
+Since the particles are independent, they are independent dynamical systems; proto formation is a higher-level construct imposed on this system and is a constraint on what states are considered viable and which are not.
 Consider two particles $x_1$ and  $x_2$ that have crossed the threshold for coalescence $x_{thresh}$.
@@
 Effectively, the proto is a two-dimensional SDS.
-Since the wealth of the proto ($p_{12}$)is additive, the aggregate wealth $p_{12} = x_1(t) + x_2(t) $.
+Since the wealth of the proto ($p_{12}$) is additive, the aggregate wealth $p_{12} = x_1(t) + x_2(t) $.
 The dynamical variable satisfies an SDE\footnote{The result follows from the additivity properties of white noise.}
@@
 
-For such ensemble of particles, the primary driver of difference in paths (life histories) and wealth is the Brownian noise intensity $D$; greater the $D$.
-greater the diversity (and hence Gini).
+For such ensemble of particles, the primary driver of difference in paths (life histories) and wealth is the Brownian noise intensity $D$; greater $D$ leads to greater diversity (and hence Gini).
 However, Gini is a measure that is dependent on absolute magnitude.
@@
 We suspect that this is because of the constant wealth growth rate used in our models, Gini is a partially useful measure.
-This is unlike in macroeconomic models where exponential growth rate gives rise a appearance of non-trivial Gini coefficients}.
+This is unlike in macroeconomic models where exponential growth rate gives rise an appearance of non-trivial Gini coefficients}.
 On the other hand, the mathematical form of expressions for $\mathcal{S}(t)$ suggest a clear and non-trivial dependence of the $D$ and clear separation between the population of particles that are isolates and the population of particles that are in a proto.
 
-As the equations (\ref{e}) and (\ref{s}) show, all agents, irrespective of their starting intial condition and luck have a non-zero probability of dying.
-The paper that inspired this work ~\cite{srimil} emphasized studied inequality dynamics in the context of extreme scarcity in their foraging world.
-One can mimic this scarcity by simply turning of the income, leaving the agents to all inevitably die.
-The differential rate of death of the isolates and the non-isolates then become an important quantity.
+As the equations (\ref{e}) and (\ref{s}) show, all agents, irrespective of their starting initial condition and luck, have a non-zero probability of dying.
+The paper that inspired this work ~\cite{srimil} studied inequality dynamics in the context of extreme scarcity in their foraging world.
+One can mimic this scarcity by simply turning off the income, leaving the agents to all inevitably die.
+The differential rate of death of the isolates and the non-isolates then becomes an important quantity.
 
@@
 All these stages and transition times between them make sense in terms of the underlying dynamics of the particle ensemble.
-In each of the stages, the effective dynamics are different from each other but the form of the equations remain the same.
+In each of the stages, the effective dynamics are different from each other, but the form of the equations remains the same.
 
@@
 In this work, we focus on the simplest \textit{textbook} example of network: Erd\H{o}s-R\'{e}nyi network model~\cite{newman2018networks}.
-ER models has only one parameter $\lambda$, a Poisson parameter that determines the density of connections in the network, and in this setting, determines the number of particles available for a particle to coalesce and form protos.
-Commonsense reasoning suggests that a larger $\lambda$ parameter may help increase the average lifetimes of individual agents through by enabling greater likelihood of contact with other particles.
+ER models have only one parameter $\lambda$, a Poisson parameter that determines the density of connections in the network, and which in this setting
+determines the expected number of particles available for a particle to
+coalesce with and form a proto.
+Commonsense reasoning suggests that a larger $\lambda$ parameter may help increase the average lifetimes of individual agents by enabling greater likelihood of contact with other particles.
 
-Just as equations (\ref{e}) and (\ref{s}) offers insight about the role of dynamics, the key feature of ER models is the the formation of giant component at $\lambda=1$, allowing a finite fraction of the population to be connected, have cliques of very high order, and other useful properties guarantee proto formation in large fraction of the population.
+Just as equations (\ref{e}) and (\ref{s}) offer insight into the role of dynamics, the key feature of ER models is the formation of giant component at $\lambda>=1$, allowing a finite fraction of the population to be connected, have cliques of very high order, and other useful properties guarantee proto formation in large fraction of the population.
 
-As its network properties are well-understood, wealth dynamics on such network allows us to understand more thoroughly, the interaction between dynamics and structure, and its role in global behavior.
+As its network properties are well-understood, the network’s wealth dynamics allow us to understand more thoroughly the interaction between dynamics and structure, and its role in global behavior.
 Still, a full analysis of this model remains to be completed and is part of a forthcoming work involving other more expressive network models.
@@
 
-Various statistical counters are updated as the program executes so that its behavior can be analyzed post mortem.
+Various statistical counters are updated as the program executes so that its behavior can be analyzed postmortem.
 The main simulation loop can also be invoked from a ``parameter sweep'' program which executes it multiple times over a range of parameter values, in order to determine how the model's behavior changes in response to key parameters.
@@
 \section{Conclusion and Future Work}
-Being one of the first in an ongoing project, the next directions are too many to mention here.
-Still, we mention a few next steps that adheres to the spirit of our project.
+This is one of the first in an ongoing project and the next directions are too many to mention here.
+Still, we mention a few next steps that adhere to the spirit of our project.
 These directions all alleviate some of the obvious limitations of the current work.
 
-While both the stochastic models and ER models are well understood, proto formation dynamics, as coagulation processes in continuous-time, remain to be better understood, mathematically.
-Also, while the mathematical analysis of dynamics of discrete-time stochastic models on networks are well studied, diffusion processes on networks seem under explored in the literature.
+While both the stochastic models and ER models are well understood, proto formation dynamics, as coagulation processes in continuous time, remain to be better understood, mathematically.
+Also, while the mathematical analysis of dynamics of discrete-time stochastic models on networks is well studied, diffusion processes on networks seem under explored in the literature.
 
 Even with only a few parameters, the simulation results are hard to visualize and interpret.
-As the number of parameters increase, as expected in future models, ideas from design and analysis of (computer) experiments may be required.
-Also, our exploration of the time to death distirbutions of the population show non-trivial stucture.
-More careful statisitcal tests that go beyond the mean analysis presented here are required to tease out the necessary and sufficient conditions for proto population to consistenty out-perform isolate population.
+As the number of parameters increases, as expected in future models, ideas from design and analysis of (computer) experiments may be required.
+Also, our exploration of the time to death distributions of the population show non-trivial structure.
+More careful statistical tests that go beyond the mean analysis presented here are required to tease out the necessary and sufficient conditions for
+agents in protos (non-isolates) to consistently outperform the isolates.
 
 The models used for our simulation are at best \textit{stylized} models of real world social and economic systems, especially in anthropology~\cite{white2011kinship} and historical and urban sociology~\cite{sampson2012great,katz2013people}.
-Research in economic anthropology~\cite{koster2019,koster2014,koster2015,bogerhoff2015,smith2019,nolin2012,power2018cooperation,power2018} suggest complex food aand economic resource sharing rituals among members of various communities.
+Research in economic anthropology~\cite{koster2019,koster2014,koster2015,bogerhoff2015,smith2019,nolin2012,power2018cooperation,power2018} suggests complex food and economic resource sharing rituals among members of various communities.
 Such resource sharing social networks do not look like any of the \textit{textbook} models.
 Extending our analysis to more expressive network models like exponential random graph models, stochastic block models and latent space models is an important research direction.
-This alongside the use of empirically observed cooperation and coordination protocols have potential in making our models better callibrated with real world systems.
+This alongside the use of empirically observed cooperation and coordination protocols have potential in making our models better calibrated with real world systems.
 
-Despite their simplicitly, models like the ones constructed here have several advantages.
-As ACE models, they offer insights about economic systems in which majority of the assumptions of neo-classical economics like perfectly mixed agents~\cite{wilhite} and presence of equilibrium~\cite{arthur} do not hold.
+Despite their simplicity, models like the ones constructed here have several advantages.
+As ACE models, they offer insights about economic systems in which the majority of the assumptions of neo-classical economics like perfectly mixed agents~\cite{wilhite} and presence of equilibrium~\cite{arthur} do not hold.
 As AS models~\cite{hedstrom2011oxford}, they offer an approach that adds models of social mechanisms to CSS models in a graded manner.

### 2019-07-22 manuscript/analysis.tex
Minor edits & grammer fixes
next to final manuscript

@@
 Increasing $\lambda$ fosters wealth uniformity through the increased formation of and growth in size of protos.
-Firstly, a higher percentage of agents join a proto as greater $\lambda$ values lead to fewer isolate agents in the ER network.
+Firstly, a higher percentage of agents join a proto as greater $\lambda$ values lead to fewer isolates in the ER network.
 As more agents join protos, differences in agent wealth are eliminated as each proto establishes perfect equality amongst its constituent agents, thereby lowering system's overall inequality.
@@
 
-% Insert Rajesh's fascinating speculations about why this should be the case.
-
 \begin{figure}[ht]
@@
 
+\subsection{Interpretations, Conjectures and Next Steps}
+Unraveling the interplay of structure and dynamics was is a major objective of this offshoot of the Milton and Mudigonda model.
+The necessarily preliminary analysis reported here shows interesting results in this direction.
+As the two sources of heterogeneity, both the ambient stochasticity and interaction probability seem to influence the two kinds of inequality indicators.
+
+As expected, figure~\ref{fig:giniVsLambda} shows the role of environmental noise: larger environmental noise produces larger inequality measures.
+Similarly, figure ~\ref{fig:avgLifespanLambda} shows the role of noise in amplifying differences between isolates and non-isolates: larger the noise, larger the separation between the mean lifetimes of the two populations.
+Also, as mentioned above, larger $\lambda$ leads to more egalitarian population(figure~\ref{fig:giniVsLambda}); concurrently, larger $\lambda$ leads to larger separation between mean lifetimes of the two populations.
+
+Ideally, we would like to derive these results mathematically, especially the point beyond which the average lifespan of two populations change.
+Since the SDS has only a few parameters, it would easy to decompose the contributions of the various factors response for mean differential lifetimes as it is unclear whether the differences are due to wealth stabilization induced by proto formation in stage 2, or in stage 3.
+Another interesting question is whether the population can be further stratified along proto-size dimensions.
+We conjecture that protos with larger number of agents will have larger mean lifetimes than protos with smaller numbers in the aggregate.
+We also conjecture that the time spent in a proto positively influences the mean lifetimes of agents in it.
+
+While the mathematical formulation of the model was presented for a single particle, the system consists of a large ensemble of particles.
+Many of the characteristics, the differentiation of the system into isolates and non-isolates depend on the order rank order statistics of wealth.
+Also, More careful statistical tests that go beyond the mean analysis presented here are required to tease out the necessary and sufficient conditions for agents in protos (non-isolates) to consistently outperform the isolates.
+We are currently pursuing these questions.
+
 % Wealth histogram is steady ?

### 2019-07-22 manuscript/bodycssa19.tex

--- 2019-07-18 manuscript/draftcssa19.tex
@@
-\documentclass[sigconf]{acmart}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-%\usepackage{graphics}
-%\usepackage{curves}
-%\usepackage{tikz}
-%\usetikzlibrary{backgrounds}
-%\usetikzlibrary{snakes} \documentclass{report}
-%\usepackage{amsmath}
-%\usepackage{amssymb}
-%\usepackage{amsfonts}
-%\usepackage{graphics}
-%\usepackage{curves}
-%\usepackage{tikz}
-%\usetikzlibrary{backgrounds}
-%\usetikzlibrary{snakes}
-%\usepackage{setspace}
-%\doublespacing
-%\usepackage{lscape}
-%\usepackage{booktabs}
-%\usepackage{longtable}
-\usepackage{hyperref}
-\usepackage{url}
-\usepackage{color}
-
-\author{ABMSPECSIG Group}
-\title{Wealth dynamics in the presence of network structure and primitive cooperation}
-\bibliographystyle{plain} 
-\begin{document}
-
-\maketitle
-\begin{abstract}
-We study wealth accumulation dynamics in a population of heterogeneously mixed agents with a capacity for a certain primitive form of cooperation enabled by static network structures.
-Despite their simplicity, the stochastic dynamics generate inequalities in wealth reminiscent of real-world social systems even in a fully mixed population.
-A simple form of cooperation is introduced and is shown to enhance the viability of agents by embedding such dynamics in a network; the impact of social structures on the origins and persistence of inequality can be teased out easily.
-The models developed here complement traditional modeling approaches based on grid worlds.
-
-\end{abstract}
 \section{Introduction}
-In recent years, the concern and debate regarding wealth inequality and socioeconomic mobility have been one of the few unifying issues dominating the extremely polarized public spheres of the Global North.
+In recent years, the concerns and debates regarding wealth inequality and socioeconomic mobility have been one of the few unifying issues dominating the extremely polarized public spheres of the Global North.
 While economic and political inequality used to be discussed in heterodox economics circles, the contentious discussions on the topic within mainstream economics since the publication of Piketty's book~\cite{piketty2017capital} suggest a lack of consensus about basic foundational questions like the origins and persistence of economic inequality.
@@
 The work presented here shares this spirit by integrating substantive ideas from anthropology, economic sociology~\cite{granovetter2017society} and urban sociology~\cite{sampson2012great} and using modeling approaches from computational social science~\cite{hedstrom2018}, computational economics~\cite{tesfatsion} and analytical sociology~\cite{hedstrom2011oxford} to explore the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
-% SD: citation for "anthropology," the first element of the last sentence's list? Grief and/or White?
 
@@
 
-These models were inspired by our search for analogs of the grid world agent-based models (ABMs) of Friesen and Mudigonda~\cite{srimil} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
-The original model used foraging to mix the population and create opportunities for interaction, and, when certain conditions were met, resource sharing.
+The model presented here was inspired by our search for analogs of the grid world agent-based model (ABM) of Friesen and Mudigonda~\cite{srimil} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
+This model used foraging to mix the population and create opportunities for interaction, and, when certain conditions were met, resource sharing.
 Our model achieves agent interaction by postulating a static network structure which partially mixes the agents.
@@
 
-The original model drew its inspiration from historical sociology, in Katz's influential study of middle of 19th century Hamilton, Canada~\cite{katz2013people}.
+The Friesen and Mudigonda model drew its inspiration from historical sociology, in Katz's influential study of middle of 19th century Hamilton, Canada~\cite{katz2013people}.
 Retaining this original motivation, we draw additional inspiration from economic sociology in the work of Granovetter~\cite{granovetter2005}; urban sociology, in the work of Sampson~\cite{sampson2002} and others; and in anthropology, in the work on cooperation in small to medium scale societies~\cite{avner1994,white2011kinship}, and others.
-The geographic and economic scale of the systems and the nature of social actors and time period of interest are all very different from the ones used to develop models of representative agents in macroeconomics~\cite{benhabib2018}, making the similarity between macroeconomic wealth dynamics models and our models not comparable without further justification.
+The geographic and economic scale of the systems and the nature of social actors and time scale of interest in these different disciplineary approaches are all very different from the ones used to develop models of representative agents in macroeconomics~\cite{benhabib2018}, making the similarity between macroeconomic wealth dynamics models and our models not comparable without further justification.
 Elaborating on the interplay of conceptual and methodological ideas among these disciplines is beyond the scope of this article.
@@
 
-The important role played by social structures or non-economic structures in determining economic outcomes of individuals in a society is not in doubt~\cite{granovetter2005, jackson_rev2017}.
+The important role played by social structures in determining economic outcomes of individuals in a society is not in doubt~\cite{granovetter2005, jackson_rev2017}.
 Still, in the absence of a unifying foundation for sociology and economics, the full impact of this two-way interpenetration of economic and social structures is demonstrated only on a case-by-case basis.
-The language of social and economic networks affords a first principle integration by simplifying the non-trivial concept of social and economic structure~\cite{martin_lee} to only dyadic relations.
+The language of social and economic networks affords a first principle integration by simplifying the non-trivial concept of social and economic structure~\cite{martin_lee} to only dyadic (binary) relations among actors\footnote{The concept social structures~\cite{martin_lee} is more general than the widely held belief in computational social science that social structure \textit{is} just a social network.}.
 
-As mentioned earlier, macroeconomic models are ill-suited to the study of collective phenomena at an intermediate level.
+Models of wealth accumulation dynamics in both macro and micro economics typically assume the presence of markets and equilibria.
+Hence, such models are ill-suited to the study of collective phenomena at an intermediate level.
 Hence, alternative explanations of aggregate phenomena that match the expressiveness of economic models are required.
@@
 It is particularly powerful when combined with computational simulation, because when mathematically formulated models reach even a modest level of complexity, they often become analytically intractable.
-Simulation \textit{in silico} can yield approximate results for these more complex scenarios, which supplement the exact results reached by traditional methods.
+Simulation \textit{in silico} can yield approximate results for these more complex scenarios, which supplement the exact results reached by analytically tractable models.
 
@@
 In this work, we construct simple toy models to reproduce certain aspects of non-trivial wealth inequality distributions in the presence and absence of primitive forms of cooperation, clearly delineating the role of network structure in generating wealth inequality.
-We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models, with no detailed empirical grounding, but with the potential to generate realistic looking inequality distributions.
-In doing so, we aspire to shed light on the \textit{true} social and economic mechanisms underlying the genesis and persistence of economic inequality, and network structure alone can produce large differences in economic outcomes.
+We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models, with no detailed empirical grounding, but with the potential to generate heterogeneous wealth outcomes reminiscent of ones obtained using more sophisticated models.
+In doing so, we aspire to shed light on the true social and economic mechanisms underlying the genesis and persistence of economic inequality, and network structure alone can produce large differences in economic outcomes.
 
 \label{giniKindaSucks}
-% SD: In light of recent discussions, we may want to downplay Gini and up-play the robustness of agents to exogenous shocks.
 The phenomenon under scrutiny is the emergence and evolution of economic inequality in societies with non-trivial social structures that enable economic interactions and cooperation mechanisms.
@@
 The dynamics are modeled as Brownian-noise-driven linear dynamical systems, here with constant growth rate; the structure is modeled by networks, here with random graphs; the measures of inequality used are Gini coefficients, and survival time distributions of agents in response to lack of resources.
+Just as with macroeconomic models, measures of wealth inequality like Gini coefficients are not so well suited for the non-market based wealth dynamics.
+We discuss this more in section 4.
+
 Although both the dynamical system and the network model are quite well understood, the precise interplay of structure and dynamics produces interesting emergent wealth distributions and robustness to scarcity.
@@
 The institutions can take the form of economic institutions, like banks and cooperatives; or the form of norms, like resource-sharing practices in societies.
-The original SriMil model~\cite{srimil}consists of a simple resource pooling arrangement where aggregates of agents pool their excess wealth in a common institution called ``proto-institutions,'' agreeing to provide this saved resource to individual agents in times of need.
-The model of resource pooling used in this work is identical to the SriMil model.
+The Friesen and Mudigonda model~\cite{srimil}consists of a simple resource pooling arrangement where aggregates of agents pool their excess wealth in a common institution called ``proto-institutions,'' agreeing to provide this saved resource to individual agents in times of need.
+The model of resource pooling used in this work is identical to this model.
 
@@
 In section 3, we present the analysis of our simulation experiments, summarize key findings, and discuss why we chose the \texttt{julia} programming language~\cite{Julia-2017} for our implementation.
-In section 4, we discuss the limitations of our simple models, extensions to dynamics and networks more expressive than the ones presented here and planned future work.
+In section 5, we discuss the limitations of our simple models, extensions to dynamics and networks more expressive than the ones presented here and planned future work.
 
 Before discussing our model in greater mathematical detail, we discuss the model qualitatively, contrasting it with more familiar modeling approaches.
-The model presented here has much in common with models used in social-reality-inspired models in statistical physics~\cite{redner2001guide}, dynamic process models in network science~\cite{newman2018networks}, and computational social science and agent-based models~\cite{abm_review}; however, our modeling philosophy is somewhere at the interface of agent-based computational economics (ACE)~\cite{tesfatsion} and analytical sociology (AS)~\cite{ch1as_hdbk,ch2as_hdbk}.
+The model presented here has much in common with models used in social-reality-inspired models in statistical physics~\cite{redner2001guide}, dynamic process models in network science~\cite{newman2018networks}, computational social science, and agent-based models~\cite{abm_review}; however, our modeling philosophy is somewhere at the interface of agent-based computational economics (ACE)~\cite{tesfatsion} and analytical sociology (AS)~\cite{ch1as_hdbk,ch2as_hdbk}.
 In ACE, we acknowledge its aspiration to develop bottom-up models of economic systems at all scales but restrain from its enthusiastic use of complex but well-calibrated detailed models of markets and agents~\cite{tesfatsion2017}.
@@
 In an ensemble of otherwise identical particles, a given particle may coalesce with a subset of other particles.
-This mixing characteristic is encoded via a graph.
+In grid world ABMs, agents interact with other agents by moving around this world.
+The precise movement protocol encodes how the agents interact (mix) among themselves.
+In the social network setting, this mixing characteristic is encoded via a graph.
 Both the conjoined particles and individual particles die upon crossing the origin.
@@
 
-%Might be nice to put a nice table here 
 The one-dimensional state space of the particle is identified with the wealth of a social actor (agent).
@@
 The environmental contingency is modeled by a Brownian noise of a specified intensity.
-Upon crossing a specific wealth threshold, agents can coalesce to form a cooperative unit deciding to pool their resources and their environmental contingencies into a single unit which we call a \textit{proto-institution} (proto).
+Agents can coalesce to form a cooperative unit deciding to pool their resources and their environmental contingencies into a single unit which we call a \textit{proto-institution} (proto), if they cross a specific wealth threshold.
 The mixing characteristic of this ensemble is the social network (here ER model).
@@
 The discussion of SDS closely follows ~\cite{redner2001guide}\footnote{The use of such analysis for studying wealth dynamics was presented by one of the authors at CSSA18 ~\cite{rv}.
-Unlike the finite interval dynamics used there, the dynamics here take place on a semi-infinite line.}
+Unlike the finite interval dynamics used there, the dynamics here take place on a semi-infinite line.}.
 
@@
 The dynamics can be started at any initial point $x_0 > 0$.
+Since simulations make use of discrete versions of these equations, a slightly different notation is used\footnote{The discrete time step $\Delta t=1$.
+$w$ in the discrete setting is a Gaussian distributed random variable $\mathcal{N}(0,\sigma^2) = \mathcal{N}(0,D\Delta t)$ }.
 
@@
 
-\noindent For a single particle, the probability of survival $S(t)$ and the expected probability of reaching the origin can be calculated and are functions of $x_0$, $v$ and $D$.
+For a single particle, the probability of survival $S(t)$ up to time $t$ and the probability of reaching the origin can be calculated and are functions of $x_0$, $v$ and $D$.
 For example, the expected probability of a particle reaching the origin ($\mathcal{E}(x_0)$), when starting at $x_0$ is given by
@@
 
-\noindent That is, there is always a non-zero probability of reaching the particle, even when there is a constant positive drift away from the origin; and, the return to origin is certain for negative or zero drift.
+\noindent That is, there is always a non-zero probability of reaching the origin, even when there is a constant positive drift away from the origin; and, the return to origin is certain for negative or zero drift.
 Similarly, survival probability, $\mathcal{S}(t)$ is given by
@@
 Since the particles are independent, they are independent dynamical systems; proto formation is a higher-level construct imposed on this system and is a constraint on what states are considered viable and which are not.
-Consider two particles $x_1$ and  $x_2$ that have crossed the threshold for coalescence $x_{thresh}$.
-After the coalescence event, the state (wealth) of individual particles $x_1(t)$ and  $x_2(t)$ is not important; only the aggregate wealth of the coalescent (proto) is important.
+Consider two particles $x_1$ and  $x_2$ that have crossed the threshold for coalescence $x_{thresh}$ ($t_p$ in the next section).
+After the coalescence event, the state (wealth) of individual particles $x_1(t)$ and  $x_2(t)$ is not relevant for survivability; only the aggregate wealth of the coalescent (proto) determines whether the particles in the coalescent survive.
 As long as $x_1(t) + x_2(t) >0$, both particles survive.
 Effectively, the proto is a two-dimensional SDS.
-Since the wealth of the proto ($p_{12}$) is additive, the aggregate wealth $p_{12} = x_1(t) + x_2(t) $.
-The dynamical variable satisfies an SDE\footnote{The result follows from the additivity properties of white noise.}
+Since the wealth of the proto ($p_{12}$) is additive, the aggregate wealth $p_{12}(t) = x_1(t) + x_2(t) $.
+The aggregate dynamical variable satisfies a SDE\footnote{The result follows from the additivity properties of white noise.}\footnote{The two pictures: the particle perspective and the proto perspective, are equivalent.
+While it is easier to mathematically analyze the system in the proto perspective, the individual wealth of the particles carries meaning; it is just not useful for studying survival of the proto or the particles within it.}.
 
 \begin{equation}\label{pddm}
-dx(t) = 2vdt + \sqrt{2*2D} dw
+dx(t) = 2vdt + \sqrt{2(2D)} dw
 \end{equation}
@@
 
-For such ensemble of particles, the primary driver of difference in paths (life histories) and wealth is the Brownian noise intensity $D$; greater $D$ leads to greater diversity (and hence Gini).
+For such ensemble of particles, the primary driver of difference in paths (life histories) and wealth is the Brownian noise intensity $D$; greater the $D$ leads greater the diversity (and hence Gini).
 However, Gini is a measure that is dependent on absolute magnitude.
@@
 This is unlike in macroeconomic models where exponential growth rate gives rise an appearance of non-trivial Gini coefficients}.
-On the other hand, the mathematical form of expressions for $\mathcal{S}(t)$ suggest a clear and non-trivial dependence of the $D$ and clear separation between the population of particles that are isolates and the population of particles that are in a proto.
+On the other hand, the mathematical form of expressions for $\mathcal{S}(t)$ suggest a clear dependence on $D$ which separates the population of particles that are not in a coalescent and the population of particles that are in one.
+Particles reaches the absorbing state (death of the agent) without being part of a coalescent are called isolates; the non-isolates, the particles that are in a coalescent when they reach the absorbing state are called protos.
 
@@
 The paper that inspired this work ~\cite{srimil} studied inequality dynamics in the context of extreme scarcity in their foraging world.
-One can mimic this scarcity by simply turning off the income, leaving the agents to all inevitably die.
-The differential rate of death of the isolates and the non-isolates then becomes an important quantity.
+One can mimic this scarcity by simply turning off the income, starving the agents, and leaving the agents to all inevitably die.
+The differential rate of death between the isolates and the non-isolates then becomes an important quantity.
+In the absence of tractable mathematical solutions, simulations experiments which probe this expected differential survival rates help illuminating the role of protos.
 
-In the simulation experiments that we discuss next discusses various stages and stopping conditions.
-All these stages and transition times between them make sense in terms of the underlying dynamics of the particle ensemble.
+We first evolve the system under favorable environmental conditions with steady salary, and identify phases before and after proto formation take place (Stage 1 and 2).
+After making sure that all surviving agents possess  wealth above the proto formation threshold $x_{thresh}$, we cut off the salary for all agents, starving the agents, leaving them susceptible to the white noise process (Stage 3).
 In each of the stages, the effective dynamics are different from each other, but the form of the equations remains the same.
@@
 To break the homogeneity of this particle ensemble, we propose to let the particles interact with only a random subset of other populations.
-In other words, we embed the particles on a network (graph); particles interact (form proto) with only their neighbors.
+In other words, we embed the particles on a network (graph); particles interact (form protos) with only their neighbors.
 In this work, we focus on the simplest \textit{textbook} example of network: Erd\H{o}s-R\'{e}nyi network model~\cite{newman2018networks}.
-ER models have only one parameter $\lambda$, a Poisson parameter that determines the density of connections in the network, and which in this setting
-determines the expected number of particles available for a particle to
-coalesce with and form a proto.
+ER models have only one parameter $\lambda$, a parameter that is the average expected degree of any given node that determines the density of connections in the network, and which in this setting determines the expected number of particles available for a particle to coalesce with and form a proto.
 Commonsense reasoning suggests that a larger $\lambda$ parameter may help increase the average lifetimes of individual agents by enabling greater likelihood of contact with other particles.
 
-Just as equations (\ref{e}) and (\ref{s}) offer insight into the role of dynamics, the key feature of ER models is the formation of giant component at $\lambda>=1$, allowing a finite fraction of the population to be connected, have cliques of very high order, and other useful properties guarantee proto formation in large fraction of the population.
+Just as equations (\ref{e}) and (\ref{s}) offer insight into the role of dynamics, the key feature of ER models is high probability of formation of giant component at $\lambda>=1$, in which a finite fraction of the population to be connected, have cliques of very high order, and other useful properties guarantee proto formation in large fraction of the population.
 
-As its network properties are well-understood, the network’s wealth dynamics allow us to understand more thoroughly the interaction between dynamics and structure, and its role in global behavior.
+As its network properties are well-understood, the network's wealth dynamics allow us to understand more thoroughly the interaction between dynamics and structure, and its role in global behavior.
 Still, a full analysis of this model remains to be completed and is part of a forthcoming work involving other more expressive network models.
-As we note subsequently, even this simple setting offers interesting insights,
+As we note subsequently, even this simple setting offers interesting insights regarding the role of network structure in determining important outcomes for the agent.
 
@@
 
-The simulation proceeds as follows. For configurable parameters
+The simulation~\footnote{All code for this work is available at https://github.com/WheezePuppet/specstar} proceeds as follows. For configurable parameters
 $N > 0$,
@@
 \input{analysis}
-%%%%% need to add some speculations and motivate further simulation experiments .... especially what insights were gained by the current simulation model
 \section{Conclusion and Future Work}
@@
 While both the stochastic models and ER models are well understood, proto formation dynamics, as coagulation processes in continuous time, remain to be better understood, mathematically.
-Also, while the mathematical analysis of dynamics of discrete-time stochastic models on networks is well studied, diffusion processes on networks seem under explored in the literature.
+Also, while the mathematical analysis of dynamics of discrete-time stochastic models on networks is well studied, diffusion processes on networks seem underexplored in the literature.
 
@@
 Also, our exploration of the time to death distributions of the population show non-trivial structure.
-More careful statistical tests that go beyond the mean analysis presented here are required to tease out the necessary and sufficient conditions for
-agents in protos (non-isolates) to consistently outperform the isolates.
+More careful statistical tests that go beyond the mean analysis presented here are required to tease out the necessary and sufficient conditions for agents in protos (non-isolates) to consistently outperform the isolates.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Need to understand the physics of the proto formation better
-%%% Say something about how this work is continues the work original started by Sri Mil
-% SriMil model introduced protos but the mathematical reformulation of proto is insightful not only for our model but also for the rginal SriMil model
+\begin{acks}
+We thank Milton Friesen and Srikanth Mudigonda, the authors of ~\cite{srimil} for providing the code for resource pooling.
+This work is part of a larger project undertaken by ABMSPECSIG\footnote{https://github.com/WheezePuppet/specstar} team.
+We thank everyone in the team for help in various stages of this work.
+The authors wish to thank their respective home institutions where this work was done.
+\end{acks}
 
-%%%Idea for final section as of today 06/13
-
-%%%% Simulations cleary show systematic variations in both inequality and death time as both white noise and network parameter changes....
-the precise interpretation and understanding of the phenomena at a more basic level is underwya..
-more precise statistical tests are required...
-
-%%% Discuss how there are too many things to do along several fronts as this is at the interface of mathematics, simulation, economics and sociogy
-
-% Discuss the importance of simple stylized models for use in computational economics .....
-cite the papers of Testatsion, Wihtle and Arthur...
-tell how simple model provides insight into the economic systems...
-discuss the importance of not having equilibrium assumptions.....
-
-%%% link to the use of these models to tease out actual social mechanisms as is warranted by analytical sociology
-
-%%%% Still, these models, at least the ones planned for the future are ideal for studying economic systems of small scale societies... cite the anthropology work....
-
-%%% cite RV work where the idea of market forces start opearting only after a certain threshold....
-and if everythin is below that threahold, there is no reason to expect that macroeconomic models are useful in any way shape or form
-
-%%%%  Economics of poverty is totally difference and is expected to involve completely different set of models... maybe use ideas from notes below
-
-%%% End with connections to the big SPECSTAR project 
-%%% Major strengths ACE (cite Arthur, Tesfatsion and Wilhite papers), AS (mechanisms fuss) 
-%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% DO NOT DELETE.... EXPECTED TO BE PART OF THE LARGER JOURNAL MANUSCRIPT 
-%%%Things that could be discussed here but is redundant if we are running out of words 
-%The general idea is to discuss how/why social networks matter wealth accumulation dynamics.
-We have references from anthropology.
-We have references in economic sociology(jackson).Sampson's work and Venkatesh's work can be used when talking about urban poverty and urban sociology.
-Discuss how in economics, wealth accumulation dynamics are mostly discussed at the macroeconomic level.
-In this sense, this work (and the work presented last year) are novel in this regard.
-
-%% Sampson's work seem to be crucial for making the claim that social structures and neighborhood effects are important determinants of economic outcomes.
-
-% Wealth accumulation models all start from fancy macroeconomic models and may not be well suited for studying wealth accumulation processes under poverty where high level of stochasticity seem to matter.
-
-%While we are interested in more sophisticated models, we are more interested in extracting the effects of social network structure in simple models of cooperative wealth accumulation.
-The proto-institution is definitely borrowed from SriMil.
-In order to study more elaborate and economically rigorous wealth dynamics, we need to be able sort of the effects of network structure in simple stylized network models.
-The work on ER models is expected to be first of our analysis.
-Eventually, we plan to get to more realistic wealth accumulation models of interest to economists but for now this is all we have.
-
-%In Katz's book, the differing life histories of individuals in Hamilton, Canada suggest that luck played a role in deterministic life outcomes.
-Katz argues that social mobility makes sense only in the context of social structure
-
-%Katz's chapter 2.
-His main argument there is that the structure of inequality represent in Hamilton, Canada is representative of inequality present in all other north American cities of that era.
-The persistence of inequality can be see in the persistence of four kinds of social structures.
-1) occupational structure, 2) division of wealth and proportion of the wealthy, 3) social and demographic identity of different economic ranks, and 4) distance between people of different socio-economic ranks or social stratification.
-He talks about persistence of networks of wealth and power.
-Points out strong interconnection between property, political power and social status.
-Argues that economic stratification and its crystallization leads to crystallization of social and other subjective stratifications.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%% This one is really important and top priority for use as a zoomed out conclusion 
-%what kinds of real world systems are we talking about?This section should write itself. Just a brief discussion of phase 2+ and integration with spescape should suffice 
-%%%% ERGM, SBM and LNM are good next steps 
-%%%%% Use anthropology references to motivate more expressive models
-
-%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%I am actually confused about whether such a purely preliminary work can say antyhing about the real world.
-Do we really want to say anything at all about the real world.
-What can ER graphs say about the real world?
-
-%We conclude by discussing features of social processes and mechanisms argued for by both Sampson and Katz that are currently not present in the model but important and part of the vision for where our model is headed.
-
-%We also include the goal of seamlessly going from a model with no geography to a model with geography.
-
-% I am moving the discussion of connections to anthropology to this section
-
-\bibliography{ref_cssa19}
-\end{document}
 % this line is for Stephen's purposes only:

### 2019-07-22 manuscript/draftcssa19.tex

@@
 \section{Introduction}
-In recent years, the concern and debate regarding wealth inequality and socioeconomic mobility have been one of the few unifying issues dominating the extremely polarized public spheres of the Global North.
+In recent years, the concerns and debates regarding wealth inequality and socioeconomic mobility have been one of the few unifying issues dominating the extremely polarized public spheres of the Global North.
 While economic and political inequality used to be discussed in heterodox economics circles, the contentious discussions on the topic within mainstream economics since the publication of Piketty's book~\cite{piketty2017capital} suggest a lack of consensus about basic foundational questions like the origins and persistence of economic inequality.
@@
 In this work, we construct simple toy models to reproduce certain aspects of non-trivial wealth inequality distributions in the presence and absence of primitive forms of cooperation, clearly delineating the role of network structure in generating wealth inequality.
-We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models, with no detailed empirical grounding, but with the potential to generate realistic looking inequality distributions.
-In doing so, we aspire to shed light on the \textit{true} social and economic mechanisms underlying the genesis and persistence of economic inequality, and network structure alone can produce large differences in economic outcomes.
+We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models, with no detailed empirical grounding, but with the potential to generate heterogeneous wealth outcomes reminiscent of ones obtained using more sophisticated models.
+In doing so, we aspire to shed light on the true social and economic mechanisms underlying the genesis and persistence of economic inequality, and network structure alone can produce large differences in economic outcomes.
 
@@
 The institutions can take the form of economic institutions, like banks and cooperatives; or the form of norms, like resource-sharing practices in societies.
-The original SriMil model~\cite{srimil}consists of a simple resource pooling arrangement where aggregates of agents pool their excess wealth in a common institution called ``proto-institutions,'' agreeing to provide this saved resource to individual agents in times of need.
-The model of resource pooling used in this work is identical to the SriMil model.
-
+The Friesen and Mudigonda model~\cite{srimil}consists of a simple resource pooling arrangement where aggregates of agents pool their excess wealth in a common institution called ``proto-institutions,'' agreeing to provide this saved resource to individual agents in times of need.
+The model of resource pooling used in this work is identical to this model.
+%% Add this in the acknowledgement section
 The analysis to be presented in later sections focuses only on homogeneous agents with simple drift-diffusion dynamics on Erd\H{o}s-R\'{e}nyi network models (ER); space constraints unfortunately prevent us from repeating the analysis on other standard \textit{textbook} networks like scale-free and small-world networks.

### 2019-07-22 manuscript/specnet_conffmt.tex

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[CSS'18]{ACM Computational Social Science conference}{July 1997}{El
  Paso, Texas USA}
\acmYear{2018}
\copyrightyear{2018}

\acmArticle{4}
\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}

\begin{document}
\title{Wealth dynamics in the presence of network structure and primitive cooperation}
%\titlenote{Produces the permission block, and
 % copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
 % \texttt{acmart.pdf} document}

\author{Stephen Davies}
\affiliation{%
  \institution{University of Mary Washington}
  \streetaddress{1301 College Avenue}
  \city{Fredericksburg}
  \state{Virginia}
  \postcode{22401}
}
\email{stephen@umw.edu}

\author{William Nehrboss}
\affiliation{%
  \institution{Lake Anna Homeschool}
  \streetaddress{2663 Moody Town RD}
  \city{Bumpass}
  \state{Virginia}
  \postcode{23024}
}
\email{Wknehrboss@gmail.com}

\author{Rajesh Venkatachalapathy}
\affiliation{%
  \institution{Systems Science Graduate Program, Portland State University}
  \streetaddress{1604 SW 10th Avenue }
  \city{Portland}
  \state{Oregon}
  \postcode{97207-0751}
}
\email{venkatr@pdx.edu}

% The default list of authors is too long for headers.
%\renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
We study wealth accumulation dynamics in a population of heterogeneously mixed agents with a capacity for a certain primitive form of cooperation enabled by static network structures. Despite their simplicity, the stochastic dynamics generate inequalities in wealth reminiscent of real-world social systems even in a fully mixed population. A simple form of cooperation is introduced and is shown to enhance the viability of agents by embedding such dynamics in a network; the impact of social structures on the origins and persistence of inequality can be teased out easily. The models developed here complement traditional modeling approaches based on grid worlds.

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

\input{bodycssa19}

\bibliographystyle{ACM-Reference-Format}
%\bibliography{sample-bibliography_test}
\bibliography{ref_cssa19}
\end{document}

### 2019-07-22 manuscript/bodycssa19.tex
Call out TJ and Olufemi in Acks.

@@
 \begin{acks}
-We thank Milton Friesen and Srikanth Mudigonda, the authors of ~\cite{srimil} for providing the code for resource pooling.
+We thank Milton Friesen and Srikanth Mudigonda, the authors of ~\cite{srimil}, for providing the code for resource pooling; Thomas Davies for contributions to the code base; and Olufemi Olaba for modeling ideas.
 This work is part of a larger project undertaken by ABMSPECSIG\footnote{https://github.com/WheezePuppet/specstar} team.
-We thank everyone in the team for help in various stages of this work.
 The authors wish to thank their respective home institutions where this work was done.

### 2019-07-23 manuscript/specnet_conffmt.tex
Change author order.
Update conference header.

@@
 %Conference
-\acmConference[CSS'18]{ACM Computational Social Science conference}{July 1997}{El
-  Paso, Texas USA}
-\acmYear{2018}
-\copyrightyear{2018}
+\acmConference[CSS'19]{CSSSA's Annual Conference on Computational Social
+Science}{October 24--27, 2019}{Santa Fe, NM, USA}
+\acmYear{2019}
+
+\copyrightyear{2019}
 
@@
 \begin{document}
-\title{Wealth dynamics in the presence of network structure and primitive cooperation}
+\title{Wealth dynamics in the presence of\\network structure and primitive cooperation}
 %\titlenote{Produces the permission block, and
@@
 
+\author{Rajesh Venkatachalapathy}
+\affiliation{%
+  \institution{Systems Science Graduate Program, Portland State University}
+  \streetaddress{1604 SW 10th Avenue }
+  \city{Portland}
+  \state{Oregon}
+  \postcode{97207-0751}
+}
+\email{venkatr@pdx.edu}
+
 \author{Stephen Davies}
 \affiliation{%
-  \institution{University of Mary Washington}
+  \institution{University of Mary Washington\\Department of Computer Science}
   \streetaddress{1301 College Avenue}
@@
 \email{Wknehrboss@gmail.com}
-
-\author{Rajesh Venkatachalapathy}
-\affiliation{%
-  \institution{Systems Science Graduate Program, Portland State University}
-  \streetaddress{1604 SW 10th Avenue }
-  \city{Portland}
-  \state{Oregon}
-  \postcode{97207-0751}
-}
-\email{venkatr@pdx.edu}
 

### 2019-07-23 manuscript/specnet_conffmt.tex
Update keywords.

@@
 <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+<concept_id>10010147.10010341</concept_id>
+<concept_desc>Computing methodologies~Modeling and simulation</concept_desc>
 <concept_significance>500</concept_significance>
@@
 <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
+<concept_id>10010147.10010341.10010349.10010355</concept_id>
+<concept_desc>Computing methodologies~Agent / discrete models</concept_desc>
+<concept_significance>500</concept_significance>
 </concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Computing methodologies~Modeling and simulation}
+\ccsdesc[500]{Computing methodologies~Agent / discrete models}
 
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\keywords{economic inequality, dynamical systems, social networks}
 

### 2019-07-23 manuscript/analysis.tex
Stephen's final wordsmithing.

@@
 Nonetheless, it is illustrative to see how it varies with respect to the ER $\lambda$ parameter.
-Figure~\ref{fig:giniVsLambda} depicts the Gini computed \textit{at the onset of stage 3} (before starvation) versus $\lambda$, and confirms that increasing $\lambda$ leads to a decreasing Gini coefficient.
+Figure~\ref{fig:giniVsLambda} depicts the Gini computed \textit{at the onset of Stage 3} (before starvation) versus $\lambda$, and confirms that increasing $\lambda$ leads to a decreasing Gini coefficient.
 Increasing $\lambda$ fosters wealth uniformity through the increased formation of and growth in size of protos.
@@
 \includegraphics[width=\columnwidth]{figures/giniVsLambda.png}
-\caption{The average Gini coefficient of effective wealth (computed pre-stage 3) for various values of the ER $\lambda$ connectivity parameter, and with both low-noise and high-noise income.
+\caption{The average Gini coefficient of effective wealth (computed pre-Stage 3) for various values of the ER $\lambda$ connectivity parameter, and with both low-noise and high-noise income.
 500 agents were used in each simulation.
@@
 \subsection{Interpretations, Conjectures and Next Steps}
-Unraveling the interplay of structure and dynamics was is a major objective of this offshoot of the Milton and Mudigonda model.
+Unraveling the interplay of structure and dynamics is a major objective of this offshoot of the Milton and Mudigonda model.
 The necessarily preliminary analysis reported here shows interesting results in this direction.
@@
 
-As expected, figure~\ref{fig:giniVsLambda} shows the role of environmental noise: larger environmental noise produces larger inequality measures.
-Similarly, figure ~\ref{fig:avgLifespanLambda} shows the role of noise in amplifying differences between isolates and non-isolates: larger the noise, larger the separation between the mean lifetimes of the two populations.
-Also, as mentioned above, larger $\lambda$ leads to more egalitarian population(figure~\ref{fig:giniVsLambda}); concurrently, larger $\lambda$ leads to larger separation between mean lifetimes of the two populations.
+As expected, Figure~\ref{fig:giniVsLambda} shows the role of environmental noise: larger environmental noise produces larger inequality measures.
+Similarly, Figure~\ref{fig:avgLifespanLambda} shows the role of noise in amplifying differences between isolates and non-isolates: the larger the noise, the larger the separation between the mean lifetimes of the two populations.
+Also, as mentioned above, larger $\lambda$ leads to a more egalitarian population (Figure~\ref{fig:giniVsLambda}); concurrently, larger $\lambda$ leads to larger separation between mean lifetimes of the two populations (Figure~\ref{fig:avgLifespanLambda}).
 
 Ideally, we would like to derive these results mathematically, especially the point beyond which the average lifespan of two populations change.
-Since the SDS has only a few parameters, it would easy to decompose the contributions of the various factors response for mean differential lifetimes as it is unclear whether the differences are due to wealth stabilization induced by proto formation in stage 2, or in stage 3.
+Since the SDS has only a few parameters, it would easy to decompose the contributions of the various factors response for mean differential lifetimes as it is unclear whether the differences are due to wealth stabilization induced by proto formation in Stage 2, or in Stage 3.
 Another interesting question is whether the population can be further stratified along proto-size dimensions.
@@
 Many of the characteristics, the differentiation of the system into isolates and non-isolates depend on the order rank order statistics of wealth.
-Also, More careful statistical tests that go beyond the mean analysis presented here are required to tease out the necessary and sufficient conditions for agents in protos (non-isolates) to consistently outperform the isolates.
+Also, a more nuanced statistical analysis that goes beyond the mean analysis presented here is required to tease out the necessary and sufficient conditions for agents in protos (non-isolates) to consistently outperform the isolates.
 We are currently pursuing these questions.

### 2019-07-23 manuscript/bodycssa19.tex
Stephen's final wordsmithing.

@@
 
-The model presented here was inspired by our search for analogs of the grid world agent-based model (ABM) of Friesen and Mudigonda~\cite{srimil} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
+The model presented here was inspired by our search for analogs of the grid world agent-based model (ABM) of Friesen and Mudi\-gonda~\cite{srimil} where foraging agents that pool their resources were shown to on-average outperform non-pooling agents.
 This model used foraging to mix the population and create opportunities for interaction, and, when certain conditions were met, resource sharing.
@@
 Still, in the absence of a unifying foundation for sociology and economics, the full impact of this two-way interpenetration of economic and social structures is demonstrated only on a case-by-case basis.
-The language of social and economic networks affords a first principle integration by simplifying the non-trivial concept of social and economic structure~\cite{martin_lee} to only dyadic (binary) relations among actors\footnote{The concept social structures~\cite{martin_lee} is more general than the widely held belief in computational social science that social structure \textit{is} just a social network.}.
+The language of social and economic networks affords a first principle integration by simplifying the non-trivial concept of social and economic structure~\cite{martin_lee} to only dyadic (binary) relations among actors.\footnote{The ``social structure'' concept~\cite{martin_lee} is more general than the social network specifically, despite the widely held belief in computational social science that they are synonyms.}
 
@@
 Hence, such models are ill-suited to the study of collective phenomena at an intermediate level.
-Hence, alternative explanations of aggregate phenomena that match the expressiveness of economic models are required.
+Alternative explanations of aggregate phenomena that match the expressiveness of economic models are required.
 Analytical sociology~\cite{ch1as_hdbk}, with its emphasis on explanation of collective emergent phenomena using mathematically formulated social mechanisms~\cite{ch2as_hdbk,ch11as_hdbk} anchored at the individual level, is an ideal candidate for this purpose.
@@
 The model we use to answer questions surrounding this phenomenon must possess a dynamic model of wealth accumulation, a model of social structure, and a suitably useful measure of inequality.
-The dynamics are modeled as Brownian-noise-driven linear dynamical systems, here with constant growth rate; the structure is modeled by networks, here with random graphs; the measures of inequality used are Gini coefficients, and survival time distributions of agents in response to lack of resources.
+The dynamics are modeled as Brownian-noise-driven linear dynamical systems, here with constant growth rate; the structure is modeled by networks, here with random graphs\footnote{In this paper (as elsewhere) the terms \textbf{graph} and \textbf{network} are exact synonyms.}; the measures of inequality used are Gini coefficients, and survival time distributions of agents in response to lack of resources.
 Just as with macroeconomic models, measures of wealth inequality like Gini coefficients are not so well suited for the non-market based wealth dynamics.
@@
 The institutions can take the form of economic institutions, like banks and cooperatives; or the form of norms, like resource-sharing practices in societies.
-The Friesen and Mudigonda model~\cite{srimil}consists of a simple resource pooling arrangement where aggregates of agents pool their excess wealth in a common institution called ``proto-institutions,'' agreeing to provide this saved resource to individual agents in times of need.
+The Friesen and Mudigonda model~\cite{srimil} consists of a simple resource pooling arrangement where aggregates of agents pool their excess wealth in a common institution called a ``proto-institution'' (henceforth, ``\textbf{proto}'') agreeing to provide this saved resource to individual agents in times of need.
 The model of resource pooling used in this work is identical to this model.
@@
 In the next section, we discuss the mathematical formulation of the model.
-In section 3, we present the analysis of our simulation experiments, summarize key findings, and discuss why we chose the \texttt{julia} programming language~\cite{Julia-2017} for our implementation.
+In section 3, we present the analysis of our simulation experiments, summarize key findings, and discuss why we chose the Julia programming language~\cite{Julia-2017} for our implementation.
 In section 5, we discuss the limitations of our simple models, extensions to dynamics and networks more expressive than the ones presented here and planned future work.
@@
 The model presented here has much in common with models used in social-reality-inspired models in statistical physics~\cite{redner2001guide}, dynamic process models in network science~\cite{newman2018networks}, computational social science, and agent-based models~\cite{abm_review}; however, our modeling philosophy is somewhere at the interface of agent-based computational economics (ACE)~\cite{tesfatsion} and analytical sociology (AS)~\cite{ch1as_hdbk,ch2as_hdbk}.
-In ACE, we acknowledge its aspiration to develop bottom-up models of economic systems at all scales but restrain from its enthusiastic use of complex but well-calibrated detailed models of markets and agents~\cite{tesfatsion2017}.
-In AS, we assent its focus on social mechanisms in explaining social phenomena, but instead rely on simplified mechanisms with few parameters~\cite{ch11as_hdbk} with the specific goal of extracting insights from \textit{stylized} models.
+We acknowledge ACE's aspiration to develop bottom-up models of economic systems at all scales, but restrain from its enthusiastic use of complex but well-calibrated detailed models of markets and agents~\cite{tesfatsion2017}.
+We adhere to AS's focus on social mechanisms in explaining social phenomena, but instead rely on simplified mechanisms with few parameters~\cite{ch11as_hdbk} with the specific goal of extracting insights from \textit{stylized} models.
 
@@
 The model of cooperative wealth accumulation constructed here is best thought of as a stochastic interacting particle system infused with economic sociological semantics.
-The particle evolves according to a one dimensional diffusion process with constant drift and is driven by a Brownian noise with a boundary condition at the origin corresponding to particle absorption.
+The particle evolves according to a one-dimensional diffusion process with constant drift and is driven by Brownian noise with a boundary condition at the origin corresponding to particle absorption.
 After crossing a pre-determined threshold in state space, particles above the threshold follow a protocol and coalesce together.
@@
 The environmental contingency is modeled by a Brownian noise of a specified intensity.
-Agents can coalesce to form a cooperative unit deciding to pool their resources and their environmental contingencies into a single unit which we call a \textit{proto-institution} (proto), if they cross a specific wealth threshold.
+Agents can coalesce to form a cooperative unit deciding to pool their resources and their environmental contingencies into a single unit which we call a proto-institution (proto), if they cross a specific wealth threshold.
 The mixing characteristic of this ensemble is the social network (here ER model).
@@
 Since simulations make use of discrete versions of these equations, a slightly different notation is used\footnote{The discrete time step $\Delta t=1$.
-$w$ in the discrete setting is a Gaussian distributed random variable $\mathcal{N}(0,\sigma^2) = \mathcal{N}(0,D\Delta t)$ }.
+$w$ in the discrete setting is a Gaussian distributed random variable $\mathcal{N}(0,\sigma^2) = \mathcal{N}(0,D\Delta t)$.}.
 
@@
 Since the particles are independent, they are independent dynamical systems; proto formation is a higher-level construct imposed on this system and is a constraint on what states are considered viable and which are not.
-Consider two particles $x_1$ and  $x_2$ that have crossed the threshold for coalescence $x_{thresh}$ ($t_p$ in the next section).
+Consider two particles $x_1$ and  $x_2$ that have crossed $x_{\textrm{thresh}}$, the threshold for coalescence.
 After the coalescence event, the state (wealth) of individual particles $x_1(t)$ and  $x_2(t)$ is not relevant for survivability; only the aggregate wealth of the coalescent (proto) determines whether the particles in the coalescent survive.
@@
 The paper that inspired this work ~\cite{srimil} studied inequality dynamics in the context of extreme scarcity in their foraging world.
-One can mimic this scarcity by simply turning off the income, starving the agents, and leaving the agents to all inevitably die.
+One can mimic this scarcity by simply ``turning off'' the income at some point, starving the agents, and leaving the agents to all inevitably die.
 The differential rate of death between the isolates and the non-isolates then becomes an important quantity.
-In the absence of tractable mathematical solutions, simulations experiments which probe this expected differential survival rates help illuminating the role of protos.
+In the absence of tractable mathematical solutions, simulation experiments which probe this expected difference in survival rates help illuminate the role of protos.
 
-We first evolve the system under favorable environmental conditions with steady salary, and identify phases before and after proto formation take place (Stage 1 and 2).
-After making sure that all surviving agents possess  wealth above the proto formation threshold $x_{thresh}$, we cut off the salary for all agents, starving the agents, leaving them susceptible to the white noise process (Stage 3).
-In each of the stages, the effective dynamics are different from each other, but the form of the equations remains the same.
+We first evolve the system under favorable environmental conditions with steady salary, during what we define as ``Stages 1 and 2.'' \textbf{Stage 1} is the phase of the dynamic model \textit{before} which any agents have formed protos (since their wealth has not yet reached $x_{\textrm{thresh}}$), and \textbf{Stage 2} is the phase \textit{during which} agents are forming protos.
+Once all non-isolate agents have joined a proto, \textbf{Stage 3} commences, at which point we cut off the salary for all agents, starving them and leaving them susceptible to the white noise process.
+The effective dynamics are different in each stage, but the form of the equations remains the same.
 
@@
 In this work, we focus on the simplest \textit{textbook} example of network: Erd\H{o}s-R\'{e}nyi network model~\cite{newman2018networks}.
-ER models have only one parameter $\lambda$, a parameter that is the average expected degree of any given node that determines the density of connections in the network, and which in this setting determines the expected number of particles available for a particle to coalesce with and form a proto.
+ER models have only one parameter ($\lambda$), which is the \textit{average expected degree} of any given node.
+This determines the density of connections in the network, and in this setting determines the expected number of particles available for a particle to coalesce with and form a proto.
 Commonsense reasoning suggests that a larger $\lambda$ parameter may help increase the average lifetimes of individual agents by enabling greater likelihood of contact with other particles.
 
-Just as equations (\ref{e}) and (\ref{s}) offer insight into the role of dynamics, the key feature of ER models is high probability of formation of giant component at $\lambda>=1$, in which a finite fraction of the population to be connected, have cliques of very high order, and other useful properties guarantee proto formation in large fraction of the population.
+Just as equations (\ref{e}) and (\ref{s}) offer insight into the role of dynamics, the key feature of ER models is the high probability of the formation of a ``giant component'' at $\lambda \ge 1$.
+When a giant component exists, a finite fraction of the population is connected.
+Networks with this property also tend to have cliques of very high order, and other useful properties that bear upon proto formation.
 
-As its network properties are well-understood, the network's wealth dynamics allow us to understand more thoroughly the interaction between dynamics and structure, and its role in global behavior.
+As its network properties are well-understood, the network's wealth dynamics allow us to understand more thoroughly the interaction between dynamics and structure, and their role in global behavior.
 Still, a full analysis of this model remains to be completed and is part of a forthcoming work involving other more expressive network models.
@@
 
-The simulation~\footnote{All code for this work is available at https://github.com/WheezePuppet/specstar} proceeds as follows. For configurable parameters
+The simulation\footnote{All code for this work is available at \texttt{https://github.com/WheezePuppet/specstar}.} proceeds as follows. For configurable parameters
 $N > 0$,
@@
 $m > 0$ (metabolic rate),
-$t_p > 0$ (the ``proto threshold''),
+$x_{\textrm{thresh}} > 0$ (the ``proto threshold''),
 $\sigma^2 \ge 0$ and
@@
 \item Create $N$ agents, each with a random initial wealth (uniformly distributed from 0 to \texttt{init\_max}), and related to one another as per a random ER network with parameter $\lambda$.
-\item \textbf{Stages 1 and 2\footnote{We define ``Stage 1'' as the period \textit{before} the first proto is formed, ``Stage 2'' as the period \textit{during} which protos are being formed}:} Repeat until all non-isolate agents\footnote{An \textbf{isolate} agent is one with no graph neighbors.} are members of a proto:
+\item \textbf{Stages 1 and 2:} Repeat until all non-isolate agents\footnote{An \textbf{isolate} agent is one with no graph neighbors.} are members of a proto:
     \begin{enumerate}
     \itemsep.1em
-    \item Each agent $A$ whose current wealth $\ge t_p$, and who is not currently a member of a proto, chooses at random one of its graph neighbors (call it $B$) whose wealth \textit{also} exceeds $t_p$.
+    \item Each agent $A$ whose current wealth $\ge x_{\textrm{thresh}}$, and who is not currently a member of a proto, chooses at random one of its graph neighbors (call it $B$) whose wealth \textit{also} exceeds $x_{\textrm{thresh}}$.
 (If there are no such neighbors, proceed to the next agent.) If $B$ is already in a proto, have $A$ join $B$'s proto.
@@
     \item Each agent gains an amount of wealth equal to $(\texttt{salary} - m + \epsilon)$, where $\epsilon \sim \mathcal{N}(0,\sigma^2)$ (white noise).\footnote{Note that this ``gain'' could be negative, in which case the agent, and possibly its proto, may be subject to death exactly as in step (3).}
-    \item Each agent \textit{that is in a proto} donates all its wealth in excess of $t_p$ to that proto's balance. (Agents not in a proto maintain their current wealth.)
+    \item Each agent \textit{that is in a proto} donates all its wealth in excess of $x_{\textrm{thresh}}$ to that proto's balance. (Agents not in a proto maintain their current wealth.)
     \end{enumerate}
@@
 \section{Conclusion and Future Work}
-This is one of the first in an ongoing project and the next directions are too many to mention here.
+This is one of the first phases of an ongoing project, and the next directions are too many to enumerate here.
 Still, we mention a few next steps that adhere to the spirit of our project.
@@
 
-Even with only a few parameters, the simulation results are hard to visualize and interpret.
+Even with only a few parameters, the simulation results are challenging to visualize and interpret.
 As the number of parameters increases, as expected in future models, ideas from design and analysis of (computer) experiments may be required.

### 2019-07-23 manuscript/verification.tex
Stephen's final wordsmithing.

@@
 (\textit{i.e.}, salary > metabolic rate), each agent's wealth rises unsteadily
-during stage 1, until eventually the first pair of neighboring agents who each
-reach the threshold form a proto-institution. Throughout stage 2, these agents
+during Stage 1, until eventually the first pair of neighboring agents who each
+reach the threshold form a proto-institution. Throughout Stage 2, these agents
 contribute all wealth in excess of the threshold to that proto, and so their
@@
 agent wealth at every iteration, and the bottom plot shows the balances of the
-protos at the same points in time. (No protos exist until stage 2, by
+protos at the same points in time. (No protos exist until Stage 2, by
 definition.) Note that the isolates (orange lines) never form protos, and
@@
 We verified that changes to basic parameters all have the expected effect:
-lowering the initial wealth delays the onset of stage 2; a higher $\sigma^2$
+lowering the initial wealth delays the onset of Stage 2; a higher $\sigma^2$
 for the income distribution makes the lines less jagged; a higher metabolic
@@
 The opposite effect occurs during Stage 3 as agent starvation leads to the relative growth of these wealth differentials.
-The variability in starvation rates further contributes to the increasing Gini coefficient.
+The variability in starvation rates further stimulates the increasing Gini coefficient.
 

### 2019-07-23 manuscript/bodycssa19.tex
minor changes, Will's comments addressed

@@
 Simultaneously, insights from related disciplines, along with novel models for scientific inquiry not usually associated with traditional econometrics, are being taken more seriously.
-The work presented here shares this spirit by integrating substantive ideas from anthropology, economic sociology~\cite{granovetter2017society} and urban sociology~\cite{sampson2012great} and using modeling approaches from computational social science~\cite{hedstrom2018}, computational economics~\cite{tesfatsion} and analytical sociology~\cite{hedstrom2011oxford} to explore the origins of inequality in a simple model of wealth dynamics in the presence of social structures.
+This work contributes to this effort by integrating substantive ideas from anthropology, economic sociology~\cite{granovetter2017society} and urban sociology~\cite{sampson2012great} and using modeling approaches from computational social science~\cite{hedstrom2018}, computational economics~\cite{tesfatsion} and analytical sociology~\cite{hedstrom2011oxford} to explore the origins of inequality in a simple model of wealth dynamics, with social structures and a primitive form of cooperation .
 
-The current work originated in our attempts to incorporate and tease out the effects of social structures in simple models of wealth dynamics in the presence of environmental stochasticity, and a simple form of resource pooling.
-Specifically, we are interested in studying how structure and dynamics interact to produce and sustain inequality and to influence robustness to scarcity shocks.
+The current work originated in our attempts to incorporate and tease out the effects of social structures in simple models of wealth dynamics in the presence of environmental stochasticity and a simple form of resource pooling.
+We are interested in the interaction between structure and dynamics, their role in the production and persistence of inequality, and how they influence the system's robustness to scarcity shocks.
 We answer the former question using Gini coefficients and the latter using survival time type analysis.
@@
 We make no suggestions that these models \textit{explain} the phenomena of interest; we are only interested in constructing the simplest possible models, with no detailed empirical grounding, but with the potential to generate heterogeneous wealth outcomes reminiscent of ones obtained using more sophisticated models.
-In doing so, we aspire to shed light on the true social and economic mechanisms underlying the genesis and persistence of economic inequality, and network structure alone can produce large differences in economic outcomes.
+As we discuss later, these simple mechanisms are limited in their ability to stabilize wealth and inequality.
+Despite this, the model still sheds light on the true social and economic mechanisms underlying the genesis and persistence of economic inequality, and network structure alone can produce large differences in economic outcomes.
 
@@
 We suspect that this is because of the constant wealth growth rate used in our models, Gini is a partially useful measure.
-This is unlike in macroeconomic models where exponential growth rate gives rise an appearance of non-trivial Gini coefficients}.
+This is unlike in macroeconomic models where exponential growth rate gives rise to stable non-trivial Gini coefficients}.
 On the other hand, the mathematical form of expressions for $\mathcal{S}(t)$ suggest a clear dependence on $D$ which separates the population of particles that are not in a coalescent and the population of particles that are in one.
-Particles reaches the absorbing state (death of the agent) without being part of a coalescent are called isolates; the non-isolates, the particles that are in a coalescent when they reach the absorbing state are called protos.
+Particles reaching the absorbing state (death of the agent) without being part of a coalescent are called isolates\footnote{In the context of a system with non-trivial network structure, an \textbf{isolate} agent is one with no graph neighbors.}; the non-isolates, the particles that are in a coalescent when they reach the absorbing state are called protos.
 
@@
 This determines the density of connections in the network, and in this setting determines the expected number of particles available for a particle to coalesce with and form a proto.
-Commonsense reasoning suggests that a larger $\lambda$ parameter may help increase the average lifetimes of individual agents by enabling greater likelihood of contact with other particles.
+Commonsense reasoning suggests that a larger $\lambda$ parameter may help increase the average lifetimes of individual agents by enabling proto formation by increasing the likelihood of contact with other particles.
 
@@
 \item Create $N$ agents, each with a random initial wealth (uniformly distributed from 0 to \texttt{init\_max}), and related to one another as per a random ER network with parameter $\lambda$.
-\item \textbf{Stages 1 and 2:} Repeat until all non-isolate agents\footnote{An \textbf{isolate} agent is one with no graph neighbors.} are members of a proto:
+\item \textbf{Stages 1 and 2:} Repeat until all non-isolate agents are members of a proto:
     \begin{enumerate}
@@
 
+An obvious and important limitation of the current model is the lack of stability in wealth inequality in the population; neither the ER graph structure nor the Brownian noise stabilizes procured wealth.
+Therefore, Additional mechanisms are required to maintain the inequality.
+
 While both the stochastic models and ER models are well understood, proto formation dynamics, as coagulation processes in continuous time, remain to be better understood, mathematically.

### 2019-07-23 manuscript/specnet_conffmt.tex
(Remove weird title line break.)
minor changes, Will's comments addressed

@@
 \begin{document}
-\title{Wealth dynamics in the presence of\\network structure and primitive cooperation}
+\title[Wealth dynamics in the presence of network structure and primitive cooperation]{Wealth dynamics in the presence of\\network structure and primitive cooperation}
 %\titlenote{Produces the permission block, and
@@
 We study wealth accumulation dynamics in a population of heterogeneously mixed agents with a capacity for a certain primitive form of cooperation enabled by static network structures.
-Despite their simplicity, the stochastic dynamics generate inequalities in wealth reminiscent of real-world social systems even in a fully mixed population.
-A simple form of cooperation is introduced and is shown to enhance the viability of agents by embedding such dynamics in a network; the impact of social structures on the origins and persistence of inequality can be teased out easily.
+Despite their simplicity, the stochastic dynamics generate inequalities in wealth reminiscent of real-world social systems even in a population without social structure.
+A simple form of social structure and cooperation is introduced and is shown to enhance the viability of agents.
+The interaction between social structures and dynamics illuminates their role in the generation and persistence of inequality.
 The models developed here complement traditional modeling approaches based on grid worlds.

### 2019-10-19 manuscript/specnet_cssa19.tex
specnet_cssa19.tex created. ending not completed

\documentclass{beamer}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
%\usepackage{graphics}
%\usepackage{curves}
\usepackage{tikz}
%\usetikzlibrary{backgrounds}
%\usetikzlibrary{snakes} 
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amsfonts}
%\usepackage{graphics}
%\usepackage{curves}
%\usepackage{tikz}
%\usetikzlibrary{backgrounds}
%\usetikzlibrary{snakes}
%\usepackage{setspace}
%\doublespacing
%\usepackage{lscape}
%\usepackage{booktabs}
%\usepackage{longtable}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{url}
\usepackage{color}
\usepackage{bibentry}
\usepackage{graphicx}
%\nobibliography*
\bibliographystyle{plain}
\graphicspath{ {./figures/} }
\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

\beamertemplatenavigationsymbolsempty

\setbeamerfont{page number in head/foot}{size=\small}
\setbeamertemplate{footline}[frame number]

\title[Your Short Title]{Wealth dynamics in the presence of network structure and primitive cooperation}
\author[shortname]{Rajesh Venkatachalapathy \inst{1} \and Stephen Davies \inst{2} \and William Nehrboss \inst{3}}
\institute[shortinst]{\inst{1} Systems Science Graduate Program \\Portland State University \\Portland, Oregon \and \inst{2} Department of Computer Science\\University of Mary Washington\\Fredericksburg, Virginia \and \inst{3} Lake Anna Homeschool\\Bumpass, Virginia}

%\author{Rajesh Venkatachalapathy}
%\institute{Systems Science Graduate Program \\Portland State University \\Portland, Oregon}
%
%
%
%\author{Stephen Davies}
%\institute{Systems Science Graduate Program \\Portland State University \\Portland, Oregon}
%\date{Friday 15th February 2019}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}[t]
\frametitle{Outline}
\begin{itemize}
\item Motivation and questions
\item Model
\item Experiments 
\item Findings 
\item Future work 
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Motivation}
\begin{itemize}
\item Friesen-Mudigonda (FM) model 
\end{itemize}
Questions
\begin{itemize}
\item What is the social network analog of FM model?
\item What is the mathematical analog of ABM-based FM model? 
\item Do social structures mediate wealth accumulation? 
\item Does cooperation lead to more wealth?
\item Does cooperation improve chances of survival under resource scarcity?
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Model}
FM model
\begin{itemize}
\item Agent-based model 
\item Resources are distributed in a grid world 
\item Agents interact as they forage for resources in \textit{this} grid world
\item  \textit{Wealthy enough} agents decide to pool their resources  
\end{itemize}
Our model 
\begin{itemize}
\item Stochastic dynamical system 
\item Resources are provided to each individual agent in a \textit{noisy manner}
\item Agents interact with neighbors in a static social network
\item \textit{Wealthy enough} agents decide to pool their resources 
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Model}

Dynamics
\begin{equation}\label{ddm}
dx(t) = vdt + \sqrt{2D} dw
\end{equation}

\begin{itemize}
\item $v$ is the wealth growth rate (the difference of the income and metabolic rate of the agent) and $D$ is the intensity of the Brownian process (white noise process) $w$. 
\item $x(t)$ is the state of the particle (wealth) at time $t$. 
\item The dynamics can be started at any initial point $x_0 > 0$. 
\end{itemize}
Structure
\begin{itemize}
\item Erd\H{o}s-R\'{e}nyi network (ER) models
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Vocabulary}
\begin{itemize}
\item proto
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Experiments}
There are three \textbf{stages} in our experiments
\begin{itemize}
\item \textbf{Stage 1} is the phase of the dynamical model \textit{before} which any agents have formed protos
\item \textbf{Stage 2} is the phase \textit{during} which agents are formation protos.
\item \textbf{Stage 3} is the phase where all agents undergo starvation\footnote{This stage commences once all non-isiolate agents have jointed a proto.} 
\end{itemize}
\end{frame}

%\begin{frame}[t]
%\frametitle{Figures}
%\begin{figure}[hb]
%\centering
%\includegraphics[scale=.4]{figures/giniVsLambda.png}
%\caption{The average Gini coefficient of effective wealth (computed pre-Stage 3) for various values of the ER $\lambda$ connectivity parameter, and with both low-noise and high-noise income. 500 agents were used in each simulation. The color band represents a bootstrapped 95\% confidence interval.}
%\label{fig:giniVsLambda}
%\end{figure}
%\end{frame}
%
%\begin{frame}[t]
%\frametitle{Figures}
%\begin{figure}[ht]
%\centering
%\includegraphics[scale=.4]{figures/avgLifespanLambda_025.png}
%\caption{Life expectancy comparison between isolates (non-proto members) and
%non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
%The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
%constant agent income to a scenario when the noise is as high as the average.}
%\label{fig:avgLifespanLambda}
%\end{figure}
%\end{frame}
%
%\begin{frame}[t]
%\frametitle{Figures}
%\begin{figure}[ht]
%\centering
%\includegraphics[scale=.4]{figures/avgLifespanLambda2.png}
%\caption{Life expectancy comparison between isolates (non-proto members) and
%non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
%The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
%constant agent income to a scenario when the noise is as high as the average.}
%\label{fig:avgLifespanLambda}
%\end{figure}
%\end{frame}

\begin{frame}[t]
\frametitle{Results}
%% need to link the figures here 
\begin{itemize}
\item Larger environmental noise produces large inequality measures (Figure 4)
\item Larger the noise, larger the separation between the mean lifetimes of the two populations (Figure 5) 
\item Larger connectivity leads to a more egalitarian population
\item Larger connectivity leads to larger separation between the mean lifetimes of the two populations
\end{itemize}

\end{frame}

\end{document}

### 2019-10-21 manuscript/specnet_cssa19.tex
concluding slides added, comments welcome

@@
 
-%\begin{frame}[t]
-%\frametitle{Figures}
-%\begin{figure}[hb]
-%\centering
-%\includegraphics[scale=.4]{figures/giniVsLambda.png}
-%\caption{The average Gini coefficient of effective wealth (computed pre-Stage 3) for various values of the ER $\lambda$ connectivity parameter, and with both low-noise and high-noise income.
+\begin{frame}[t]
+\frametitle{Figures}
+\begin{figure}[hb]
+\centering
+\includegraphics[scale=.4]{figures/giniVsLambda.png}
+\caption{The average Gini coefficient of effective wealth (computed pre-Stage 3) for various values of the ER $\lambda$ connectivity parameter, and with both low-noise and high-noise income.
 500 agents were used in each simulation.
 The color band represents a bootstrapped 95\% confidence interval.}
-%\label{fig:giniVsLambda}
-%\end{figure}
-%\end{frame}
-%
-%\begin{frame}[t]
-%\frametitle{Figures}
-%\begin{figure}[ht]
-%\centering
-%\includegraphics[scale=.4]{figures/avgLifespanLambda_025.png}
-%\caption{Life expectancy comparison between isolates (non-proto members) and
-%non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
-%The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
-%constant agent income to a scenario when the noise is as high as the average.}
-%\label{fig:avgLifespanLambda}
-%\end{figure}
-%\end{frame}
-%
-%\begin{frame}[t]
-%\frametitle{Figures}
-%\begin{figure}[ht]
-%\centering
-%\includegraphics[scale=.4]{figures/avgLifespanLambda2.png}
-%\caption{Life expectancy comparison between isolates (non-proto members) and
-%non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
-%The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
-%constant agent income to a scenario when the noise is as high as the average.}
-%\label{fig:avgLifespanLambda}
-%\end{figure}
-%\end{frame}
+\label{fig:giniVsLambda}
+\end{figure}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Figures}
+\begin{figure}[ht]
+\centering
+\includegraphics[scale=.4]{figures/avgLifespanLambda_025.png}
+\caption{Life expectancy comparison between isolates (non-proto members) and
+non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
+The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
+constant agent income to a scenario when the noise is as high as the average.}
+\label{fig:avgLifespanLambda}
+\end{figure}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Figures}
+\begin{figure}[ht]
+\centering
+\includegraphics[scale=.4]{figures/avgLifespanLambda2.png}
+\caption{Life expectancy comparison between isolates (non-proto members) and
+non-isolates (proto members) for different values of $\lambda$ and $\sigma^2$.
+The \texttt{salary} parameter was set to 20, so the x-axis ranges from a nearly
+constant agent income to a scenario when the noise is as high as the average.}
+\label{fig:avgLifespanLambda}
+\end{figure}
+\end{frame}
 
@@
 \begin{itemize}
-\item Larger environmental noise produces large inequality measures (Figure 4)
-\item Larger the noise, larger the separation between the mean lifetimes of the two populations (Figure 5) 
+\item Larger environmental noise produces large inequality measures (Figure 1)
+\item Larger the noise, larger the separation between the mean lifetimes of the two populations (Figures 2 and 3) 
 \item Larger connectivity leads to a more egalitarian population
@@
 
+\begin{frame}[t]
+\frametitle{Questions}
+\begin{itemize}
+\item What are the underlying mechanisms underlying the gap between mean life expectancy of \textit{protos} and \textit{isolates}?
+\item Do \textit{protos} of different sizes differ in the mean life expectancy and wealth? 
+\item Can we derive the results of these simulations from the defining SDS?
+\item Do other baseline network models like \textit{scale-free} and \textit{small-world} models induce similar systematic differences between \textit{protos} and \textit{isolates}?
+\end{itemize}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Conclusion}
+\begin{itemize}
+\item These are very preliminary results 
+\item Repeating these simulations on other baseline network models might provide more clarity
+\item These models might be amenable to mean field analysis 
+\end{itemize}
+More generally
+\begin{itemize}
+\item Our models are an useful addition to the variety of dynamical system models on networks 
+\item Despite their simplicity, the exhibit interesting dynamics and are useful to study the two-way interaction between structure and dynamics.  
+\end{itemize}
+\end{frame}
+
 \end{document}

### 2019-10-22 manuscript/specnet_cssa19.tex
very minor edits

@@
 \item $x(t)$ is the state of the particle (wealth) at time $t$. 
-\item The dynamics can be started at any initial point $x_0 > 0$. 
+\item The dynamics can be started at any initial point $x_0 > 0$ (diffusion on a \textit{semi-infinite interval}. 
 \end{itemize}
@@
 \begin{itemize}
-\item proto
+\item isolates
+\item proto a.k.a proto-institutions
+\item starvation shock 
+\item lifetime 
+\item $\lambda$ parameter 
+\item \texttt{julia}
 \end{itemize}
@@
 \begin{itemize}
-\item Larger environmental noise produces large inequality measures (Figure 1)
+\item Larger environmental noise produces larger inequality measures (Figure 1)
 \item Larger the noise, larger the separation between the mean lifetimes of the two populations (Figures 2 and 3) 
@@
 \item Repeating these simulations on other baseline network models might provide more clarity
+\item Simulations with SDS models used in macroeconomics will help empirically ground the models  
 \item These models might be amenable to mean field analysis 

### 2019-10-24 manuscript/specnet_cssa19.tex
Stephen's last-minute slide changes.

--- 2019-10-21 manuscript/specnet_cssa19.tex
@@
 \usepackage{amsfonts}
+\usepackage{commath}
 %\usepackage{graphics}
@@
 \usepackage{graphicx}
+
 %\nobibliography*
@@
 \title[Your Short Title]{Wealth dynamics in the presence of network structure and primitive cooperation}
-\author[shortname]{Rajesh Venkatachalapathy \inst{1} \and Stephen Davies \inst{2} \and William Nehrboss \inst{3}}
+\author[shortname]{Rajesh Venkatachalapathy \inst{1} \and Stephen Davies
+\inst{2} \\ \and William Nehrboss \inst{3}}
 \institute[shortinst]{\inst{1} Systems Science Graduate Program \\Portland State University \\Portland, Oregon \and \inst{2} Department of Computer Science\\University of Mary Washington\\Fredericksburg, Virginia \and \inst{3} Lake Anna Homeschool\\Bumpass, Virginia}
@@
 \item Experiments 
+\item Sample simulation runs
 \item Findings 
@@
 \begin{itemize}
-\item What is the social network analog of FM model?
+\item What is the social network analog of the FM model?
 \item What is the mathematical analog of ABM-based FM model? 
 \item Do social structures mediate wealth accumulation? 
-\item Does cooperation lead to more wealth?
+\item Does cooperation lead to more wealth? (Or to less?)
 \item Does cooperation improve chances of survival under resource scarcity?
@@
 \item Agents interact as they forage for resources in \textit{this} grid world
-\item  \textit{Wealthy enough} agents decide to pool their resources  
+\item  \textit{Wealthy enough} agents who encounter one another decide to pool their resources  
 \end{itemize}
+\bigskip
 Our model 
@@
 \item Stochastic dynamical system 
-\item Resources are provided to each individual agent in a \textit{noisy manner}
+\item Resources are provided to each agent in a \textit{noisy manner}
 \item Agents interact with neighbors in a static social network
-\item \textit{Wealthy enough} agents decide to pool their resources 
+\item \textit{Wealthy enough} agents who encounter one another decide to pool their resources 
 \end{itemize}
@@
 \begin{equation}\label{ddm}
-dx(t) = vdt + \sqrt{2D} dw
+\dif x(t) = v\dif t + \sqrt{2D} \dif w
 \end{equation}
@@
 \begin{itemize}
-\item $v$ is the wealth growth rate (the difference of the income and metabolic rate of the agent) and $D$ is the intensity of the Brownian process (white noise process) $w$. 
+\item $v$ is the wealth growth rate (the difference of the income and metabolic
+rate of the agent) and $D$ is the intensity of the Brownian (white noise)
+process $w$. 
 \item $x(t)$ is the state of the particle (wealth) at time $t$. 
-\item The dynamics can be started at any initial point $x_0 > 0$. 
+\item The dynamics can be started at any initial point $x_0 > 0$ (diffusion on
+a \textit{semi-infinite interval}).
 \end{itemize}
@@
 \begin{itemize}
-\item proto
+\item an \textbf{isolate}
+\item a ``\textbf{proto}'' a.k.a proto-institution
+\item ``\textbf{starvation shock}''
+\item \textbf{lifespan}
+\item $\lambda$ parameter (for ER model)
+\item \texttt{julia}
 \end{itemize}
@@
 \frametitle{Experiments}
+\bigskip
 There are three \textbf{stages} in our experiments
+\smallskip
 \begin{itemize}
-\item \textbf{Stage 1} is the phase of the dynamical model \textit{before} which any agents have formed protos
-\item \textbf{Stage 2} is the phase \textit{during} which agents are formation protos.
-\item \textbf{Stage 3} is the phase where all agents undergo starvation\footnote{This stage commences once all non-isiolate agents have jointed a proto.} 
+\item \textbf{Stage 1} is the phase of the dynamical model \textit{before}
+which any agents have formed protos.
+\item \textbf{Stage 2} is the phase \textit{during} which agents are forming protos.
+\item \textbf{Stage 3} is the phase \textit{after} which all (non-isolate)
+agents have joined a proto. \textbf{Starvation} commences.
 \end{itemize}
@@
 \begin{frame}[t]
-\frametitle{Figures}
+\frametitle{Demo}
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\begin{center}
+\huge
+Sample simulation runs
+\end{center}
+\end{frame}
+
+\begin{frame}[t]
+\frametitle{Experimental results}
 \begin{figure}[hb]
@@
 \begin{frame}[t]
-\frametitle{Figures}
+\frametitle{Experimental results}
 \begin{figure}[ht]
@@
 constant agent income to a scenario when the noise is as high as the average.}
-\label{fig:avgLifespanLambda}
+\label{fig:avgLifespanLambda025}
 \end{figure}
@@
 constant agent income to a scenario when the noise is as high as the average.}
-\label{fig:avgLifespanLambda}
+\label{fig:avgLifespanLambda2}
 \end{figure}
@@
 \begin{frame}[t]
-\frametitle{Results}
+\frametitle{Takeaways}
 %% need to link the figures here 
 \begin{itemize}
-\item Larger environmental noise produces large inequality measures (Figure 1)
-\item Larger the noise, larger the separation between the mean lifetimes of the two populations (Figures 2 and 3) 
-\item Larger connectivity leads to a more egalitarian population
-\item Larger connectivity leads to larger separation between the mean lifetimes of the two populations
+\itemsep1em
+\item Higher environmental noise produces more inequality (Fig.~1)
+\item Denser connectivity produces \textit{less} inequality (Fig.~1)
+\item Higher environmental noise gives proto members a longer average lifespan (Figs.~2 and 3) 
+    \begin{itemize}
+    \item ...and this effect is exaggerated for more densely connected populations
+    \end{itemize}
 \end{itemize}
@@
 \begin{itemize}
-\item What are the underlying mechanisms underlying the gap between mean life expectancy of \textit{protos} and \textit{isolates}?
-\item Do \textit{protos} of different sizes differ in the mean life expectancy and wealth? 
+\item What are the mechanisms underlying the gap between mean life expectancy
+of proto members and isolates?
+\item Do protos of different sizes differ in the mean life expectancy
+and wealth? 
 \item Can we derive the results of these simulations from the defining SDS?
-\item Do other baseline network models like \textit{scale-free} and \textit{small-world} models induce similar systematic differences between \textit{protos} and \textit{isolates}?
+\item Do other baseline network models (like \textit{scale-free} and
+\textit{small-world}) induce similar systematic differences between
+proto members and isolates?
 \end{itemize}
@@
 \item Repeating these simulations on other baseline network models might provide more clarity
+\item Simulations with SDS models used in macroeconomics will help empirically ground the models  
 \item These models might be amenable to mean field analysis 
 \end{itemize}
+\bigskip
 More generally
 \begin{itemize}
-\item Our models are an useful addition to the variety of dynamical system models on networks 
-\item Despite their simplicity, the exhibit interesting dynamics and are useful to study the two-way interaction between structure and dynamics.  
+\item Our models are an useful addition to the variety of dynamical system
+models on networks.
+\item Despite their simplicity, they exhibit interesting dynamics and are useful to study the two-way interaction between structure and dynamics.  
 \end{itemize}
